### 2025-01-05 main.tex
init templates

\documentclass[12pt]{article}
\usepackage{setspace} 
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{hyperref}
\usepackage{lineno}

%\usepackage[utf8]{inputenc}
\usepackage{natbib}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\bibliographystyle{plainnat}
\setcitestyle{aysep={}}

\geometry{margin=1in}

% Enable line numbering
\linenumbers

\begin{document}

% Title
\title{An Unofficial Latext template}
\author{
    Abc\textsuperscript{a,*},
    Waa \textsuperscript{a},
    xxa \textsuperscript{a}
}
\date{}

\maketitle

% Footnotes for authors
\noindent\textsuperscript{a} Centre for Machine Vision, , United Kingdom \\
Email: \{abc, yxz,, aaa\}@yahoo.ac.uk \\
%\textsuperscript{b}Affiliation 2, Full address, Country, email2@example.com\\
%\textsuperscript{c}Affiliation 3, Full address, Country, email3@example.com\\
\textsuperscript{*}Corresponding author: abc@ yahoo.ac.uk

\begin{abstract}

\end{abstract}

\textbf{Keywords:} Computer vision

\doublespacing

\section{Introduction}

% check which citation works for you
\citep{barbole_comparative_2023}
%citet{2}

\section{Experimental}

\section{Experimental Results}

\subsection{Quantitative Analysis}

\section{Conclusion}

\section*{CRediT authorship contribution statement}
\textbf{author}: Writing – original draft, Visualization, Validation, Software, Investigation, Formal analysis, Data curation, Conceptualization.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\section*{Data availability}
Data will be made available on request.

\section*{Acknowledgment}
This work was supported by

\bibliography{references}

\end{document}

### 2025-01-05 main.tex
finish heading page

@@
 
+\newcommand\blfootnote[1]{
+    \begingroup
+    \renewcommand\thefootnote{}\footnote{#1}
+    \addtocounter{footnote}{-1}
+    \endgroup
+}
+
 \begin{document}
@@
 % Title
-\title{An Unofficial Latext template}
+\title{GrapeCPNet: A deep learning integration for grape completion and phenotyping in 3D}
 \author{
-    Abc\textsuperscript{a,*},
-    Waa \textsuperscript{a},
-    xxa \textsuperscript{a}
+    Wenli Zhang \textsuperscript{a,*},
+    Chao Zheng \textsuperscript{a},
+    Chenhuizi Wang \textsuperscript{a},
+    Pieter M. Blok \textsuperscript{b}, \\
+    Haozhou Wang \textsuperscript{b},
+    Wei Guo \textsuperscript{b}
+    \blfootnote{Corresponding author: zhangwenli@bjut.edu.cn}
+    \blfootnote{Email addresses: zhengchao97201@163.com (Chao Zheng), Wangchenhuizi@emails.bjut.edu.cn (Chenhuizi Wang), pieter.blok@fieldphenomics.com (Pieter M.
+Blok), haozhou-wang@g.ecc.u-tokyo.ac.jp (Haozhou Wang), guowei@g.ecc.u-tokyo.ac.jp (Wei Guo)}
 }
@@
 % Footnotes for authors
-\noindent\textsuperscript{a} Centre for Machine Vision, , United Kingdom \\
-Email: \{abc, yxz,, aaa\}@yahoo.ac.uk \\
-%\textsuperscript{b}Affiliation 2, Full address, Country, email2@example.com\\
-%\textsuperscript{c}Affiliation 3, Full address, Country, email3@example.com\\
-\textsuperscript{*}Corresponding author: abc@ yahoo.ac.uk
+\noindent\textsuperscript{a} Information Department, Beijing University of Technology, Beijing, China \\
+% Email: zhangwenli@bjut.edu.cn \\
+\textsuperscript{b} Graduate School of Agricultural and Life Sciences, The University of Tokyo, Tokyo, Japan\\
+% \textsuperscript{*} \\
 
 \begin{abstract}
-
+The measurement of phenotypic parameters of fresh grapes, especially at the individual berry level, is critical for yield estimation and quality control. 
+Currently, these measurements are done by humans, making it costly, labor-intensive, and often inaccurate. 
+Advances in 3D reconstruction and point cloud analysis allow extraction of detailed for grapes, yet current methods struggle with instance segmentation on incomplete point clouds due to occlusion. 
+This study presents a novel deep-learning-based phenotyping pipeline designed specifically for 3D grape point cloud data.                                                         
+First, individual berries are segmented from the grape bunch using the SoftGroup deep learning network. 
+Next, a self-supervised point cloud completion network, termed GrapeCPNet, addresses occlusions by completing missing areas.  
+Finally, morphological analyses are applied to extract berry radius and volumes. 
+Validation on a dataset of four fresh grape varieties yielded  $R^2$ values of 85.53\% for berry radius and 96.89\% for berry volume, respectively. 
+These results demonstrate the potential of the proposed method for rapid, practical acquisition of grape 3D phenotypic information in grape cultivation.
 \end{abstract}
 
-\textbf{Keywords:} Computer vision
+\textbf{Keywords:} 3D point cloud analysis, instance segmentation, shape completion
 

### 2025-01-05 main.tex
add intro and methods source

@@
 \usepackage{xcolor}
+\usepackage{indentfirst}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-\bibliographystyle{plainnat}
-\setcitestyle{aysep={}}
 
@@
 
+% footnote email
 \newcommand\blfootnote[1]{
@@
 }
+
+% reset space of equation blocks
+\usepackage{etoolbox}
+\AtBeginEnvironment{equation}{\setstretch{1}\vspace{-0\baselineskip}}
+\AtBeginEnvironment{align}{\setstretch{1}\vspace{-\baselineskip}}
 
@@
 \section{Introduction}
+Fresh grape is one of the most important agricultural products and economic crops. 
+Its global production scale and consumption is increasing year by year. 
+To better guide planting strategy and monitoring growing status, several geometric parameters like counts, length, and volume at bunch level and berry level are commonly used in actual applications.
+[1-4].
+Among them, the number and the radius of the berries are the most important phenotypic parameters [5]. 
+Traditional manual phenotyping of parameter measurements is labor-intensive and time-consuming, and often destructive. 
+To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic parameters based on computer vision has attracted extensive interest in recent years [6].
+Several simple geometry parameters can be acquired from 2D images by using computer vision algorithms like pattern recognition, machine learning, and deep learning [7]. 
+Projecting the 3D world onto a 2D image plane inevitably results in information loss. 
+The occlusion of berries often lead to incomplete representations of grape bunches. 
+Additionally, clustered berries and their shadows naturally create complex structures even under controlled lightning conditions. 
+Leaving difficulties for obtaining reliable measurements of phenotypic parameters through 2D image analysis [8,9].
 
-% check which citation works for you
-\citep{barbole_comparative_2023}
-%citet{2}
+Advances in 3D scanning and reconstruction techniques have made it possible to retain detailed spatial information about objects, enabling the acquisition of complex 3D morphological traits in grape bunches [10-11].
+Researchers have developed 3D phenotyping processes for grapes by combining feature-engineered point cloud processing algorithms[12,13]. 
+These methods primarily rely on point cloud segmentation techniques, such as edge-based segmentation, region-growing segmentation, and sphere-fitting algorithms. 
+However, traditional point cloud processing algorithms are heavily dependent on prior knowledge of the target object and require extensive manual feature design and parameter tuning to achieve optimal results in specific conditions, limiting their broader applicability.
 
-\section{Experimental}
+On the other hand, deep learning approach uses a data-driven approach to learn features from point cloud data automatically. 
+It recently shows promising adaptability and accuracy in plant 3D phenotyping [14-17]. Focusing on point cloud segmentation applications, 
+Li et al. [18] proposed MASPC\_Transform to segment the stems and leaves of rose bush point cloud data to obtain 3D phenotypic parameters. 
+Wang et al. [19] realized leaf instance segmentation by designing the PartNet for lettuce point cloud data. 
+Li et al. [20] proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. 
+Unlike previous studies focused on canopy level or individual plant level analysis, instance segmentation alone is insufficient on berry level analysis. 
+The aggregated cluster growth [21] causes the berries to squeezed against each other, leading to interior occlusion and resulting in an incomplete point cloud of berry surfaces. 
+Therefore, point cloud instance segmentation can only capture partial information rather than that of whole berries.
 
-\section{Experimental Results}
+To address the partial point cloud problem, some researchers applied deep learning-based point cloud completion [22]. 
+Point cloud completion is the task of generating a complete 3D shape given partial point cloud input [23]. 
+Utilizing deep learning methods, researchers have designed point cloud completion networks[24-28]. 
+Park et al.
+[24] introduced DeepSDF to achieve the completion of object point cloud models.
+It uses a learned continuous signed distance function to represent a class of shapes in latent space and is tolerant to noisy 3D input data.
+Magistri et al. [25] utilized a latent space of potential fruit appearances and propose an encoder-decoder network that converted a single RGB-D frame to a 3D shape of a complete fruit. 
+This network was extended and upgraded by Blok et al. [47] for high-throughput 3D shape completion of potato tubers on a commercial harvester.
+Tang et al [26] proposed a point cloud completion network Lake-net for furniture model point cloud datasets. 
+For grape berry application, the completion network is expected to infer a complete point cloud model based on a single partial berry point cloud after bunch segmentation. 
+However, existing models are mainly designed for feature extraction of objects consisting of simple geometric forms such as surfaces with fixed curvature, and absolute planes [29]. 
+The shape of the berry can roughly approach the deformation of a sphere or ellipsoid depending on the species [30], and its surface consists of multiple spherical surfaces of varying curvature, with a rich characterization of details.
+This leads to difficulties in the direct application of existing networks. 
+Therefore, there is an urgent demand to construct a network that can complete the detailed surface of an incomplete berry point cloud.
 
-\subsection{Quantitative Analysis}
+In this study, we proposed a berry-level 3D grape phenotyping pipeline that will overcome the occlusion issue. 
+The proposed pipeline includes: 
+(1) individual berry segmentation module that segment each berry from 3D point cloud of whole bunch; 
+(2) point cloud completion module that complete the missing part of segmentated berry point cloud data; 
+(3) phenotyping module that extract berry phenotypic traits such as radius and volume. 
+And at the end, the pipeline has been tested on four different fresh grape species (Red, Green, Kyoho, and Shine Muscat Grape).
+
+\section{Materials and Methods}
+
+In this section, we first introduce the four experimental grape materials and the 3D reconstruction methods for obtaining 3D point cloud data. 
+We then provide a brief overview of the SoftGroup [32] deep learning network, which was trained on our previous point cloud dataset for instance segmentation of individual berries (Fig. 1a). 
+Next, we detail the proposed self-supervised completion deep learning module, GrapeCPNet, which predicts the complete berry point cloud from segmented partial berries (Fig. 1b). 
+Subsequently, we describe the module and method for calculating phenotypic traits (Fig. 1c). 
+Finally, we introduced the evaluation method for model training and results validation.
+
+% fig.1
+
+\subsection{Plant Materials and Point Cloud Acquisition}
+
+\subsubsection{Grape species selection}
+
+To ensure the generality and applicability of the study, this paper considers the sparsity, shape, and color of the bunch, and chooses four common fresh grapes as the experimental materials, which are Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape.
+The characteristics of them are shown in Table 1 and the examples are shown in Figure 8.
+
+% table 1
+
+% fig.8 + fig.6 -> Fig.2a, 2b
+
+\subsubsection{3D reconstruction of grape}
+
+In this paper, the multi-view images acquisition and 3D reconstruction by Agisoft Metashape (Agisoft LLC, St.
+Petersburg, Russia) was used to obtain the 3D point cloud of bunch (Fig.
+9a) and single complete berry (Fig.
+9b).
+Their correspondence of the same berry was also labelled as shown in Figure 9c
+
+% fig.9
+
+For whole bunch multi-view images acquisition, the device was built as shown in Figure 9a. 
+One grape bunch was hung on the hook which was attached to propellers driven by stepping motors (Fig. 9a1) that can achieve rotation at a certain speed. 
+The entire device was placed in front of a solid-colored backdrop (Fig. 9a2 ), and multiple cameras were set up to photograph the bunch from different height angles. 
+In addition, a ruler with markers were used for scale correction. 
+For single complete berry multi-view images acquisition in batch (Fig. 9b). 
+Nine berries were fixed floating by needle disk (Fig. 9b1) on a turntable device (Fig. 9b2). 
+The background, cameras, and marker settings are similar to the previous bunch reconstruction. 
+The number of reconstructed images and the shooting parameters are selected, as shown in Table 2. 
+Examples of the point cloud of bunch, multiple berries, and single complete berries from multiple berries are shown in Figure 10.
+
+% table 2
+
+% figure 10
+
+\subsection{Berry Instance Segmentation}
+
+As Figure 1a, the single-bunch shell point cloud was represented as $P_{bunch}=\{p_i | i=1, \cdots, m\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in 3D space and $m$ denotes the total number of points in the point cloud of the bunch.
+The bunch point cloud segmentation task expects to segment $P_{bunch}$ into a combination of several individual subsets of the berries point cloud and a subset of the stem point cloud, as shown in Equation~(\ref{eq:1}).
+
+\begin{equation}
+P_{bunch} = \sum_{i=1}^{n} P_{berry_{i}} + P_{stem}
+\label{eq:1}
+\end{equation}
+
+{\raggedright where, $P_{berry_{i}}$ denotes the subset point cloud of the $i^{\text{th}}$ berry in the bunch, $n$ denotes the number of all the berries contained in the bunch, and $P_{stem}$ denotes the set of stem point cloud.
+Meanwhile, each subset $P_{berry_{i}}=\{p_j | j=1, \cdots, k\}$ consists of multiple points in 3D space, which can represent the location and morphology of the visible part of the berry within the bunch.}
+
+The task of instance berry segmentation from a bunch is complex. 
+As shown in Figure 2, it involves distinct localization features and complex boundary morphology. 
+The distinct localization feature implies that individual berry has more geometrical and morphological details compared to the overall shape of the grape bunch, particularly when the object is a small-sized point cloud [31].
+The complex boundary morphology arises from berries pressing against each other, resulting in multiple curves with varying connecting depths. 
+Therefore, accurate berry instance segmentation requires a model that can both capture detailed geometric features and identify instances at boundary point.
+
+% figure 2
+
+In this paper, SoftGroup [32] was selected for bunch point cloud segmentation by comparing different current deep learning-based point cloud instance segmentation models. 
+SoftGroup contains two aspects of design: 
+(1) the point-by-point prediction U-Net was used to capture the detailed geometric characteristics between points. 
+(2) a threshold score was used to judge the boundary of the point to avoid point category misclassification. 
+Therefore, it is suitable for use in a bunch where there is a tight connection boundary among the berries.
+
+In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in
+% todo
+Section 2.1.2 was labeled at the instance-level (Fig. 11). 
+This paper collected and labeled 8 bunches for each of the four species (total 32 bunches). 
+In the sample division, 5 grape bunches of each species (total 20) are randomly selected and used as training samples, the remaining 12 bunches are used for validation.
+
+\subsection{Self-Supervised Point Cloud Completion}
+
+The self-supervised training-based berry point cloud completion was used to predict their complete 3D model. 
+Self-supervised learning is a way of training a model without artificial annotations by using the data itself as truth value to supervise [33]. 
+This subsection introduced the self-supervised strategy to generating paired training data without manual annotation and the structure of grape completion network, GrapeCPNet. 
+The whole workflow of proposed GrapeCPNet is shown in Figure 3.
+
+% figure 3
+
+\subsubsection{Self-supervised training data generation}
+
+The point cloud completion network often requires the incomplete-complete data pairs of the same object to build a mapping relationship. 
+In this paper, the complete grapes were obtained by single berry reconstruction 
+%todo
+(Section 2.1.2) and were used as ground truth, while the incomplete grapes were cut from the complete grapes following characteristic of occlusion and were used as training inputs. 
+This data pair generation strategy saved huge amounts of data annotation. The common incomplete characteristics of the berry are shown in Figure 4.
+Based on the incomplete characteristics, we developed a cutting method for the complete berry point cloud to generate the incomplete berry point cloud.
+
+% figure 4
+
+This proposed algorithm is shown in Algorithm 1. 
+The inputs include a single complete berry point cloud and the maximum number of cutting area (5 in this paper). 
+The output is the cut incomplete berry point clouds. First, the single complete berry point cloud was normalized and centralized (Fig. 12a). 
+Second, randomly pick the integer number of cuts lower than maximum number, in this paper ranging from 1 to 5. 
+Then, for each loop of cutting, a 3D sphere model was generated in the space to collide with the berry point cloud, and the collision portion was removed to complete the cutting operation. 
+The maximum of center and radius parameters of 3D sphere model were manually set according to berry size. 
+In this paper we set maximum 0.75 for center offsets and maximum 0.25 for radius. 
+Continue the previous cut looping until meet the cut limits. The cut incomplete berry of each loop was all saved as training data (Fig. 12b).
+
+% algorithm 1
+
+% figure 12
+
+For model training, 36 complete berry are collected for each of the four species of grape (in total 144). 
+To further expand the data quantity, based on the single complete berry point cloud obtained by reconstruction, this paper uses the PointFlow [40], a point cloud generation model to generate the simulated samples (Fig.
+12c).
+Then, 500 complete berry point clouds are generated from PointFlow method. 
+Thus, a total of 644 complete samples are obtained. 
+Each complete berry point cloud has 5 incomplete berry point clouds corresponding to it, and a total of 3220 training data pairs are obtained. 
+For the training and testing of the model, this paper divides the dataset according to a ratio close to 7:3, with a total of 450 complete berry point clouds (2250 training data pairs) to train the network and 194 complete berry point clouds (970 testing data pairs) to test.
+
+For the model inference validation, among 12 testing grape bunches of the berry instance segmentation model 
+%todo
+(Section 2.2), each grape species was randomly selected one bunch (total 4 bunches). 
+For each bunch, 27 berries are randomly selected, and finally obtain a total of 108 incomplete berries as the input data for completion network inference validation. 
+By checking the labels of these berries, the corresponding single complete berry reconstruction results %todo
+(Section 2.1.2 \& Fig. 9c) were used as ground truth.
+
+\subsubsection{GrapeCPNet structure}
+
+Since the entire contour of the incomplete berry is missing, the model is required to have the ability to predict the incomplete part based on the visible part and make the prediction part fit the real berry surface and avoid detail distortion.
+This paper combines the centroid-based sparse completion structure of PoinTr [35] with the diffusion-based dense completion structure of SnowFlakeNet [36]. 
+Based on the characteristics of the berry, it has two parts: contour completion and surface completion. The network structure is shown in Figure 5.
+
+% figure 5
+
+{\raggedright\textbf{(1) Centroid-based berry contour completion}}
+
+The visible portion of the incomplete berry belongs to a part of a sphere or ellipsoid, characterized by a distinctly spherical surface. 
+In addition, the point cloud is unstructured data, unstructured and dense, resulting in features that cannot be effectively extracted. 
+Based on the above analysis, this paper utilizes the centroid set of the visible part to infer the centroid set of the invisible part. 
+Specifically, GrapeCPNet uses centroid-based feature extraction in PoinTr [35] to accomplish berry point cloud contour completion. The process is described below:
+
+Assume that the set of incomplete berry point cloud as input to the network is represented as $P_{partial}=\{p_i | i=1, \cdots, m \}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in 3D space and $m$ denotes the number of points.
+The berry point cloud completion task aims to output the complete berry point set $P_{complete}=\{p_i | i=1, \cdots, n\}$, where $n$ denotes the number of points of the output, and $n > m$, thereby it can represent the complete 3D morphology of the berry.
+
+After the incomplete berry point cloud set $P_{partial}=\{p_i |i=1,\cdots,m\}$ was fed into the network, it was firstly down-sampled to a fixed number of points $M$ ($M$ is often less than $m$, in this paper, $M$ is set to 2048) through the farthest point sampling (FPS) to obtain the center point set $P_{partial-center}=\{p_i | i=1, \cdots, M\}$ of the visible part of the berry.
+This set was used as a ``representative'' to avoid huge computational effort while characterizing the complete morphology of the visible part.
+
+Then, the 3D convolutional neural networks DGCNN [37] and MLP [38] are used to obtain the local structural features of each point $p_i$ in the center point set, as shown in Equation (\ref{eq:2}).
+
+\begin{equation}
+    F_i = F_{i}^{'} + \varphi(p_i)
+    \label{eq:2}
+\end{equation}
+
+{\raggedright where, $F_{i}^{'}$ denotes the feature around $p_i$ obtained by DGCNN, which is the local feature of the point in the point cloud; and $\varphi(p_i)$ denotes the position information of $p_i$ obtained by MLP, which is the global feature of the point.}
+
+Finally, since the $\varphi = \{ \varphi(p_i) |i=1, \cdots, M \}$ contains the relative position information of each point, it can be used as the position embedding and the serialized feature $F = \{F_i | i=1, \cdots, M \}$ was fed into the geometrically-aware Transformer [39] based encoder.
+The process is Equation (\ref{eq:3}).
+
+\begin{equation}
+    V = T_e(F)
+    \label{eq:3}
+\end{equation}
+
+{\raggedright where, $T_e$ denotes the encoder of the Transformer and $V=\{V_i |i=1, \cdots, M\}$ denotes the encoded feature. 
+Next, the predicted centroid point set of the missing part was output by the decoder, and the process as Equation (\ref{eq:4}).}
+
+\begin{equation}
+    P_{pred-center} = T_d(V)
+    \label{eq:4}
+\end{equation}
+
+{\raggedright where, $T_d$ denotes the decoder of the Transformer, $P_{pred-center}=\{p_i |i=1,\cdots,N\}$ denotes the predicted centroid point set, and $N$ denotes the number of points in the set. 
+Through the above steps, the set of center points of the complete berry can be initially obtained, which was the result of sparse contour completion.}
+
+{\raggedright\textbf{(2) Snowflake diffusion-based berry surface completion}}
+
+The results of the contour completion can determine the overall 3D morphology, however, the density of this sparse point cloud requires the model can capture the detail surface geometry changes between points to avoid distortion.
+Therefore, this paper utilizes the snowflake diffusion-based generation idea to regard each point in the contour completion as the center point of the local region. 
+It diffuses based on the centroid points and generates further at the generated location, densification by point-to-point splitting. 
+Specifically, as follows:
+
+First, GrapeCPNet sets each point $p$ of the sparse complement $P_{pred-center}=\{p_i |i=1,\cdots,N\}$ as a ``seed point''. 
+Then, $P_{pred-center}$ was fed into multiple SPD [36] connected serially of SnowFlakeNet, which are used to realize point splitting and generation. 
+On the one hand, the SPD diffuses from the center point in a tree structure around, revealing the detailed geometric structure of the local region. 
+This method effectively represents the surface geometric features composed between the points in the localized region of the berry. 
+On the other hand, the iteration of multiple point splitting steps delivers information from each one to the next one. 
+This approach effectively characterizes the curvature changes on the surface of the berry. The process is Equation (\ref{eq:5}).
+
+\begin{equation}
+    P_{i+1} = SPD(P_i)
+    \label{eq:5}
+\end{equation}
+
+{\raggedright where, $P_i$ denotes the input point cloud of the $i^{\text{th}}$ SPD, $P_{i+1}$ denotes the output point cloud of the $(i+1)^{\text{th}}$ SPD, and $P_0=P_{pred-center}$. 
+In this paper, when $i=2$ (an empirical value), the final predicted dense point cloud on the surface of the complete berry $P_3=P_{complete}$ was output and $P_{complete}=\{p_i |i=1,\cdots,n\}$.}
+
+Through the above two steps, the complete 3D point cloud model of the berry can be obtained after contour completion and surface completion of GrapeCPNet.
+
+\subsection{Phenotypic Traits Calculation and Validation}
+
+To describe the 3D morphology of berries, this paper used ellipsoidal surface fitting with three axes, for the completed berry point cloud (Fig. 7).
+
+% figure 7
+
+Suppose the point cloud of the complete berry is denoted as $P_{complete}=\{P_i | i=1, \cdots,n\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in the 3D space, and $n$ denotes the number of points. 
+In this paper, it is fitted to an ellipsoid surface with three unequal long axes by the least squares method, and the function is shown in Equation (\ref{eq:6}).
+
+\begin{equation}
+    \frac{(x-x_0)^2}{a^2} + \frac{(y-y_0)^2}{b^2} + \frac{(z-z_0)^2}{c^2} = 1
+    \label{eq:6}
+\end{equation}
+
+{\raggedright where, $(x,y,z)$ denotes a point on the ellipsoid surface, $(x_0,y_0,z_0)$ denotes the coordinates of the ellipsoid center point, and $a$, $b$, $c$ are the half-long, half-middle, and half-short axes, respectively (assuming that $a>b>c>0$).
+}
+
+Thus, the values of $a$, $b$, $c$ can represent the berry radius parameters. 
+At the same time, the volume of the berry can be calculated as shown in Equation (\ref{eq:7}).
+
+\begin{equation}
+    V=\frac{4}{3} \pi a b c
+    \label{eq:7}
+\end{equation}
+
+In order to validate the accuracy of extracted morphological traits, those 12 validation bunches in %todo
+Section 2.2 were continuously used after instance berry segmentation and berry completion. 
+The radius and volume of the 108 samples are calculated. 
+For ground truth measurement, instead of using manual measurement, which has multiple artificial errors in obtaining the true values of actual radius and volume. 
+This paper used the correspond individual complete berry as the ground truth and applied the same method for the radius and volume calculations.
+
+\subsection{Evaluation Metrics}
+
+In this paper, the evaluation metrics for the bunch segmentation, the berry completion, the effectiveness of the number of berries counting, and the calculation of radius and volume in the acquisition of 3D phenotypic parameters are as follows.
+
+\subsubsection{Berry instance segmentation}
+
+In this paper, we use the format of SoftGroup [32] that is consistent with the S3DIS dataset [41] and use the average precision AP [32] as the evaluation metric for berry instance segmentation.
+In the threshold setting, the average of the APs with selected the IoU (Intersection over Union) from 50\% to 95\% in steps of 5\% is noted as AP@50:5:95.
+
+\subsubsection{Berry self-supervised completion}
+
+In this paper, we use the format of PoinTr [35] that is consistent with the PCN dataset [42] and use the chamfer distance (CD-distance) and F-Score to measure the effect of berry completion. 
+For each sample, the chamfer distance $d_CD$ between the predicted point set $P$ and the true point set $G$ is calculated as shown in Equation (\ref{eq:8})
+
+\begin{equation}
+    d_{CD}(P, G) = \frac{1}{|P|} \sum_{p \in P} \min_{g \in G} \|p - g\|_2^2 + \frac{1}{|G|} \sum_{g \in G} \min_{p \in P} \|g - p\|_2^2
+    \label{eq:8}
+\end{equation}
+
+{\raggedright where, $|P|$ denotes the number of points of $P$, $|G|$ denotes the number of points of $G$, and $\|p - g\|$ denotes the distance between $p$ and $g$. 
+It can be seen that the chamfer distance represents the sum of the average closest distance from the point in $P$ to the point in $G$ and the average closest distance from the point in $G$ to the point in $P$.
+Where the L1 norm is used to calculate the closest distance between two points.}
+
+In addition, F-Score measures the similarity between $P$ and $G$ by the harmonic mean between Precision and Recall. 
+On the one hand, Precision counts the percentage of the number of points of the prediction within a certain distance from the truth point, which represents the accuracy of the prediction;
+on the other hand, Recall counts the percentage of the number of points of the truth point within a certain distance from the prediction point, which represents the completeness of the prediction.
+Specifically, as follows.
+
+\begin{align}
+    \text{Precision}(d) &= \frac{1}{|P|} \sum_{p \in P} \left[ \min_{g \in G} \|p - g\| < d \right] \tag{9}\\
+    \text{Recall}(d) &= \frac{1}{|G|} \sum_{g \in G} \left[ \min_{p \in P} \|g - p\| < d \right] \tag{10}\\
+    F\text{-Score}(d) &= \frac{2 \times \text{Precision}(d) \times \text{Recall}(d)}{\text{Precision}(d) + \text{Recall}(d)} \tag{11}
+\end{align}
+
+{\raggedright where, Precision$(d)$ and Recall$(d)$ in (11) denote the Precision and Recall computed under the distance threshold $d$, respectively, and $d$ is set to $0.01$ in the PCN data format. 
+From the above Equation, the higher the F-Score indicates that the two point sets are more similar.}
+
+In addition, in order to verify the efficiency of GrapeCPNet, other classical point cloud completion networks, including PoinTr, SnowFlakeNet, TopNet [43], and GRNet [44] are selected as comparison algorithms.
+
+\subsubsection{Phenotypic traits calculation}
+
+In order to evaluate the efficiency of the number of berry statistics and the calculation of berry radius and volume, the MAE (Mean Absolute Error) and the coefficient of determination $R^2$ (R-Square) are used to calculate the error between the prediction value and the true value of the sample.
+
+\begin{align}
+    \text{MAE} &= \frac{1}{m} \sum_{i=1}^{m} |y_i - \hat{y}_i| \tag{12}\\
+    R^2 &= 1 - \frac{\sum_{i} (\hat{y}_i - y_i)^2}{\sum_{i} (\bar{y}_i - y_i)^2} \tag{13}
+\end{align}
+
+{\raggedright where, $m$ is the number of samples, $y_i$ is the true value of the $i^{\text{th}}$ sample, $\hat{y}_i$ is the prediction value, and $\bar{y}_i$ represents the mean of all true values. 
+It can be seen that the lower the MAE, the closer the prediction value is to the true value, and the value of $R^2$ ranges from 0 to 1, and the closer it is to 1 means that the prediction value is better fitted.}
 
@@
 \section*{Acknowledgment}
-This work was supported by
+This work was supported by \citep{blok_highthroughput_2025}
 
+\bibliographystyle{elsarticle-harv}
+\setcitestyle{aysep={}}
 \bibliography{references}

### 2025-01-05 main.tex
update all texts

@@
 
-\section{Conclusion}
+\section{Results}
+
+In order to validate the efficiency of the method proposed in this paper, the experiments are conducted on each component separately, including the result of bunch point cloud segmentation, the result of berry point cloud completion based on self-supervised training, and the result of phenotypic parameters acquisition.
+
+\subsection{Berry Instance Segmentation Results}
+
+Bunch point cloud segmentation is mainly realized based on SoftGroup, a point cloud segmentation network. 
+This paper calculates the segmentation results for the berry instances and stem instances using the dataset introduced in 
+%todo
+Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table 3.
+
+% table 3
+
+As can be seen from Table 3, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.
+The visualization results of four fresh grapes for bunch point cloud segmentation using SoftGroup are shown in Figure 13.
+
+% figure 13
+
+\subsection{Berry Self-Supervised Completion Results}
+
+The berry point cloud completion experiments are divided into two parts according to the different phases of the network: the results of the self-supervised training experiments and the results of the practical application experiments.
+
+(1) In the training phase, the incomplete-complete pair of the point cloud of berry is obtained by the cutting method to train the network. 
+The samples are divided into the training set and the testing set.
+Therefore, in order to verify the efficiency of berry point cloud completion in the training phase, experiments are conducted as ``Test''.
+
+(2) In the application phase, the incomplete berries segmented from the bunch are complemented based on the trained berry point cloud completion model. 
+Therefore, in order to verify the efficiency of berry point cloud completion in practical applications, experiments are conducted as ``Inference''.
+
+Meanwhile, since the point cloud obtained after berry picking is used as the ground truth, the point cloud alignment is performed to calculate evaluation metrics of the predicted complete berry point cloud with the ground truth.
+The experimental results of comparing to other point cloud completion algorithms are shown in Table 4. 
+GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the other comparative algorithms. 
+The visualization of using GrapeCPNet to complement the incomplete berry segmented from the bunch in the application phase is shown in Figure 14.
+
+% table 4
+
+% figure 14
+
+In addition, the results of the ``Inference'' experiments are worse than those of the ``Test'' experiments for two main reasons.
+First, there are differences between the dataset of the training phase and the application phase of self-supervised training, resulting in a loss of accuracy in the application of the model. 
+In addition, when evaluating the actual application efficiency of the model, the true value of the reconstructed complete point cloud of a single berry and the prediction value of the complemented point cloud suffer from the loss of accuracy when they are aligned.
+Through the above results, the experiments of berry point cloud completion based on self-supervised training reflected the efficacy of GrapeCPNet, meanwhile, this paper further validated the efficacy of the 3D phenotypic parameters acquisition of grape by the proposed method.
+
+\subsection{Phenotypic Traits Calculation Results}
+
+Based on the method in this paper, the bunch point cloud is used as input, and the acquired 3D phenotypic parameters are the final output, which mainly contains two parts: the bunch-level phenotypic parameters and the berry-level phenotypic parameters.
+In this paper, experiments are conducted to calculate berry radius and volume with the dataset in the evaluation metrics in 
+%todo
+Section 2.5.3.
+The radius parameters are calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure 16.
+
+% figure 16
+
+Three lengths of the radius of the berry can be obtained by fitting the predicted point cloud of the complete berry shell to the surface of an ellipsoid. 
+Meanwhile, the point cloud data acquisition method in 
+%todo
+Section 2.1.2 can translate the scale of the point cloud space to the real world, so as to get the real radius length of the berry.
+Because of the large difference between the ratio of the long and short axis of different species, this paper conducted experiments on the calculation of the axis length of four species respectively, as shown in Figure 17.
+
+% figure 17
+
+As shown in Figure 17, each point on the subplot block represents a berry sample, the horizontal coordinate indicates the true value of the axis length, the vertical coordinate indicates the prediction value, and the $R^2$ and MAE are displayed in the figure at the same time.
+From the results, it can be seen that the proposed method achieves an average $R^2$ of 0.86 for the three axis lengths of the four species of grape. 
+The analysis based on different perspectives is as follows.
+
+(1) The different species: Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape axis lengths predicted to reach an average $R^2$ of 0.86, 0.84, 0.89, and 0.84, respectively. 
+Among them, Kyoho Grape achieves the best results due to its berries with spherical shapes that are not too densely clustered and the lower difficulty in berry completion and morphology fitting. 
+Secondly, Red Grape and Green Grape both present a typical ellipsoid shape, but the latter is less precise than the former due to its greater ratio of long axis to short axis, which provides a more complex presentation.
+In addition, Shine-Muscat Grape has the lowest precision, which is due to the fact that its berry grows tightly and squeeze each other heavily, and the completion and fitting suffer from a loss of precision.
+
+(2) The different axis: the average $R^2$ of the four species of grape are 0.89, 0.83, and 0.84 for the long, middle, and short axis, respectively. 
+It can be seen that the prediction accuracy of the long axis is significantly higher than that of the others, in which the $R^2$ of Red Grape and Kyoho Grape reach 0.90 and 0.92, respectively, realizing a high accuracy.
+This is due to the fact that in berry completion and fitting, the long axis is the easiest to determine, with less fitting error compared to the other two axes.
+
+The experimental results show that the proposed method has achieved high accuracy in the calculation of the radius of different grape species. 
+In addition, based on the radius prediction results, the volume of all 108 berry samples is calculated in this paper, and the experimental results are shown in Figure 18.
+
+% figure 18
+
+From the experimental results, it can be seen that the proposed method in the four species of berry volume phenotypic parameter calculation, $R^2$ reached 0.97, MAE is 0.3842 $cm^3$, with high precision, fully guarantee the accuracy of the prediction of the volume of different species.
+
+\section{Discussion and Conclusion}
+
+In this paper, a method for the automatic acquisition of 3D phenotypic parameters of grape is designed to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end in the current work.
+Based on the point cloud of a bunch, the combination of deep learning point cloud processing algorithms realizes the counting of the number of berries, the calculation of berry radius, and berry volume.
+Moreover, to address the problem of incomplete surface of berry point cloud caused by occlusion, GrapeCPNet, a berry point cloud completion model based on the self-supervised training method, is designed to provide effective analytical data for berry-level phenotypic analysis.
+
+At the same time, we found that GrapeCPNet is not effective in the case of complex berry appearance, such as drop-shaped. 
+We have found that some researchers [45,46] have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network. 
+We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion. 
+In addition, the noise of data is also related to the effectiveness of the method proposed in this paper. 
+How to implement the method in practical application scenarios, such as RGB-D collected point cloud data, is another issue to be considered in the future.
+
+Through the method proposed in this paper, the automated acquisition of 3D phenotypic parameters of grape can be realized, which is of great significance in the field of agricultural production and scientific research.
+First, there are large differences in berry morphology among different species of grape, and accurate reconstruction and analysis at the berry-level can help researchers analyze character differences more accurately.
+This plays an important role in breed improvement, cultivation management, and yield prediction. 
+Secondly, the point cloud data analysis technology based on 3D reconstruction has a wide application prospect in the growth environment of field crops. 
+Through the designed data acquisition method and related technologies, combined with the actual field crop growing environment, the growth process can be monitored and analyzed in real-time. 
+Further, it can understand the phenotypic change law of crops under a natural growing environment better, provide a scientific basis for agricultural production, and optimize the production process and quality control.
 
 \section*{CRediT authorship contribution statement}
-\textbf{author}: Writing – original draft, Visualization, Validation, Software, Investigation, Formal analysis, Data curation, Conceptualization.
+\textbf{Wenli Zhang}: conceptualisation, methodology, supervision, funding acquisition, project administration, writing - review; \textbf{Chao Zheng}: methodology, software, data curation, writing - original draft \& editing; \textbf{Chenhuizi Wang}: data curation, software; \textbf{Pieter M.
+Blok}: methodology, supervision, writing - review \& editing; \textbf{Haozhou Wang}: methodology, writing - review \& editing; \textbf{Wei Guo}: conceptualisation, methodology, funding acquisition, supervision, writing - review \& editing.
 
@@
 \section*{Data availability}
-Data will be made available on request.
+The dataset, model weight and code will be made available on request.
 
-\section*{Acknowledgment}
-This work was supported by \citep{blok_highthroughput_2025}
+\section*{Funding}
+This study is partially funded by the ...
+
+\section*{Acknowledgements}
+We would like to thank ... \citep{blok_highthroughput_2025}
+
+{\clearpage}
 

### 2025-01-05 main.tex
add all fig tbl alg

@@
 \usepackage{cite}
+\usepackage[ruled]{algorithm2e}
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
 \usepackage{graphicx}
@@
 % fig.1
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure1.pdf}
+    \caption{Proposed pipeline for grape bunch 3D phenotyping.
+Taking the bunch point cloud data as input, it is realized through three steps: (1) berry instance segmentation by SoftGroup[32], (2) berry point cloud completion by proposed GrapeCPNet, and (3) phenotypic traits calculation.}
+    \label{fig:raw1}
+\end{figure}
 
@@
 % table 1
+\begin{table}[h]
+    \centering
+    \caption{Comparison of the characteristics of the four species of fresh grape}
+    \begin{tabular}{cccc}
+        \hline
+        \textbf{Grape Species} & \textbf{Color} & \textbf{Sparsity} & \textbf{Shape} \\
+        \hline
+        Red & Purple-red & Sparser & Ellipsoid \\
+        Green & Green & Sparse & Ellipsoid \\
+        Kyoho & Dark-purple & Dense & Sphere \\
+        Shine-Muscat & Green & Very dense & Sphere \\
+        \hline
+    \label{tlb:1}
+    \end{tabular}
+\end{table}
 
-% fig.8 + fig.6 -> Fig.2a, 2b
+% fig.8 + fig.6 -> Fig.2
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure2.pdf}
+    \caption{Examples of four fresh grape bunches and their berries}
+    \label{fig:raw86}
+\end{figure}
 
@@
 % fig.9
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure3.pdf}
+    \caption{Methods for obtaining multi-view images of bunch reconstruction and berry reconstruction, and the example of berry labeling}
+    \label{fig:raw9}
+\end{figure}
 
@@
 % table 2
+\begin{table}[h]
+    \centering
+    \caption{Comparison of the characteristics of the four species of fresh grape}
+    \begin{tabular}{cccc}
+        \hline
+        \textbf{Object} & \textbf{Shooting distance} & \textbf{Shooting angle} & \textbf{Number of images} \\
+        \hline
+        Bunch        & 25-60cm & $0^{\circ}$, $\pm 25^{\circ}$, $\pm 45^{\circ}$ & $5 \times 50$ \\
+        Single berry & 20-40cm & $-15^{\circ}$, $0^{\circ}$, $25^{\circ}$, $45^{\circ}$ & $4 \times 50$ \\
+        \hline
+    \label{tlb:2}
+    \end{tabular}
+\end{table}
 
 % figure 10
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure4.pdf}
+    \caption{Example of point cloud obtained based on multi-view images reconstruction}
+    \label{fig:raw10}
+\end{figure}
 
@@
 
-As Figure 1a, the single-bunch shell point cloud was represented as $P_{bunch}=\{p_i | i=1, \cdots, m\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in 3D space and $m$ denotes the total number of points in the point cloud of the bunch.
+As Figure 1a, the single-bunch shell point cloud was represented as $P_{bunch}=\{p_i \mid i=1, \cdots, m\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in 3D space and $m$ denotes the total number of points in the point cloud of the bunch.
 The bunch point cloud segmentation task expects to segment $P_{bunch}$ into a combination of several individual subsets of the berries point cloud and a subset of the stem point cloud, as shown in Equation~(\ref{eq:1}).
@@
 {\raggedright where, $P_{berry_{i}}$ denotes the subset point cloud of the $i^{\text{th}}$ berry in the bunch, $n$ denotes the number of all the berries contained in the bunch, and $P_{stem}$ denotes the set of stem point cloud.
-Meanwhile, each subset $P_{berry_{i}}=\{p_j | j=1, \cdots, k\}$ consists of multiple points in 3D space, which can represent the location and morphology of the visible part of the berry within the bunch.}
+Meanwhile, each subset $P_{berry_{i}}=\{p_j \mid j=1, \cdots, k\}$ consists of multiple points in 3D space, which can represent the location and morphology of the visible part of the berry within the bunch.}
 
@@
 % figure 2
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure5.pdf}
+    \caption{Example of berry connection in a bunch (in the case of Red Grape). The red line in the figure shows the characteristics: multiple curves of different depths intersect each other}
+    \label{fig:raw2}
+\end{figure}
 
@@
 
+% figure 11
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure6.pdf}
+    \caption{Example of instance-level labeling of a bunch point cloud: each berry has a unique instance label, as shown by different colors of point sets}
+    \label{fig:raw11}
+\end{figure}
+
 \subsection{Self-Supervised Point Cloud Completion}
@@
 % figure 3
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure7.pdf}
+    \caption{Flowchart of the self-supervised berry point cloud completion, including model training and model inferencing (application) phases.
+In the training phase, the paired incomplete training data was generated from the complete single berry point cloud, then train GrapeCPNet self-supervisely without manual annotation.
+In the application phase, the incomplete berry point cloud is input into the trained model to obtain a complete prediction berry.}
+    \label{fig:raw3}
+\end{figure}
 
@@
 % figure 4
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure8.pdf}
+    \caption{Example of different perspectives of an incomplete berry point cloud segmented from the bunch.
+The edge of the absence shows multiple segments connected by circular curves, as shown by the red arrows}
+    \label{fig:raw4}
+\end{figure}
 
@@
 % algorithm 1
+\begin{algorithm}
+    \caption{The cutting method for generating incomplete training data}
+    \label{alg:1}
+    \KwData{$P_C = \{p_i \mid i = 1, \cdots, t\}$ \tcp{One complete berry pointcloud}}
+    \KwData{$n$ \tcp{Number of incomplete berries to be generated}}
+    \KwResult{$P_{\text{output}} = \{P_{o_i} \mid i = 1, \cdots, n\}$ \tcp{incomplete berry point cloud sets} }
+
+    $\hat{P_C} \gets Normalize(Translate(P_C))$ \tcp{center to $(0,0,0)$, range to $[-0.5, 0.5]$}
+    \For{$i = 0 \to n$}{
+        set $m = \text{random}\{1,2,3,4,5\}$ \tcp{cut incomplete single berry $m$ times}
+        $P_{o_i} \gets copy(\hat{P_C})$ \tcp{initialize one output}
+        \For{$j = 0 \to m$}{
+            set $O = \{(x_o, y_o, z_o) \mid x, y, z \in \text{random}[-0.75, 0.75]\}$ \tcp{center variable} 
+            set $R = \text{random}[0.25, 0.75]$ \tcp{radius variable}
+            set $M_S \gets sphere(O, R)$ \tcp{genreate sphere cut model}
+            $P_{o_i} = P_{o_i} - P_{o_i} \cap M_S$ \tcp{remove overlap with cut shpere model}
+        }
+        $P_{o_i} \in P_{\text{output}}$ \tcp{add to output set}
+    }
+\end{algorithm}
 
 % figure 12
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure9.pdf}
+    \caption{Example of dataset composition for the self-supervised training-based method of the berry point cloud completion network.}
+    \label{fig:raw12}
+\end{figure}
 
@@
 % figure 5
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure10.pdf}
+    \caption{GrapeCPNet structure.
+(a) Centroid-based completion and (b) Transformer network for contour completion of incomplete berry, using sparse point cloud to determine the entire shape; (c) Snowflake diffusion-based completion for dense surface completion to obtain final prediction.}
+    \label{fig:raw5}
+\end{figure}
 
@@
 
-Assume that the set of incomplete berry point cloud as input to the network is represented as $P_{partial}=\{p_i | i=1, \cdots, m \}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in 3D space and $m$ denotes the number of points.
-The berry point cloud completion task aims to output the complete berry point set $P_{complete}=\{p_i | i=1, \cdots, n\}$, where $n$ denotes the number of points of the output, and $n > m$, thereby it can represent the complete 3D morphology of the berry.
+Assume that the set of incomplete berry point cloud as input to the network is represented as $P_{partial}=\{p_i \mid i=1, \cdots, m \}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in 3D space and $m$ denotes the number of points.
+The berry point cloud completion task aims to output the complete berry point set $P_{complete}=\{p_i \mid i=1, \cdots, n\}$, where $n$ denotes the number of points of the output, and $n > m$, thereby it can represent the complete 3D morphology of the berry.
 
-After the incomplete berry point cloud set $P_{partial}=\{p_i |i=1,\cdots,m\}$ was fed into the network, it was firstly down-sampled to a fixed number of points $M$ ($M$ is often less than $m$, in this paper, $M$ is set to 2048) through the farthest point sampling (FPS) to obtain the center point set $P_{partial-center}=\{p_i | i=1, \cdots, M\}$ of the visible part of the berry.
+After the incomplete berry point cloud set $P_{partial}=\{p_i \mid i=1,\cdots,m\}$ was fed into the network, it was firstly down-sampled to a fixed number of points $M$ ($M$ is often less than $m$, in this paper, $M$ is set to 2048) through the farthest point sampling (FPS) to obtain the center point set $P_{partial-center}=\{p_i \mid i=1, \cdots, M\}$ of the visible part of the berry.
 This set was used as a ``representative'' to avoid huge computational effort while characterizing the complete morphology of the visible part.
@@
 
-Finally, since the $\varphi = \{ \varphi(p_i) |i=1, \cdots, M \}$ contains the relative position information of each point, it can be used as the position embedding and the serialized feature $F = \{F_i | i=1, \cdots, M \}$ was fed into the geometrically-aware Transformer [39] based encoder.
+Finally, since the $\varphi = \{ \varphi(p_i) \mid i=1, \cdots, M \}$ contains the relative position information of each point, it can be used as the position embedding and the serialized feature $F = \{F_i \mid i=1, \cdots, M \}$ was fed into the geometrically-aware Transformer [39] based encoder.
 The process is Equation (\ref{eq:3}).
@@
 
-{\raggedright where, $T_d$ denotes the decoder of the Transformer, $P_{pred-center}=\{p_i |i=1,\cdots,N\}$ denotes the predicted centroid point set, and $N$ denotes the number of points in the set. 
+{\raggedright where, $T_d$ denotes the decoder of the Transformer, $P_{pred-center}=\{p_i \mid i=1,\cdots,N\}$ denotes the predicted centroid point set, and $N$ denotes the number of points in the set.
 Through the above steps, the set of center points of the complete berry can be initially obtained, which was the result of sparse contour completion.}
@@
 
-First, GrapeCPNet sets each point $p$ of the sparse complement $P_{pred-center}=\{p_i |i=1,\cdots,N\}$ as a ``seed point''. 
+First, GrapeCPNet sets each point $p$ of the sparse complement $P_{pred-center}=\{p_i \mid i=1,\cdots,N\}$ as a ``seed point''. 
 Then, $P_{pred-center}$ was fed into multiple SPD [36] connected serially of SnowFlakeNet, which are used to realize point splitting and generation. 
@@
 {\raggedright where, $P_i$ denotes the input point cloud of the $i^{\text{th}}$ SPD, $P_{i+1}$ denotes the output point cloud of the $(i+1)^{\text{th}}$ SPD, and $P_0=P_{pred-center}$. 
-In this paper, when $i=2$ (an empirical value), the final predicted dense point cloud on the surface of the complete berry $P_3=P_{complete}$ was output and $P_{complete}=\{p_i |i=1,\cdots,n\}$.}
+In this paper, when $i=2$ (an empirical value), the final predicted dense point cloud on the surface of the complete berry $P_3=P_{complete}$ was output and $P_{complete}=\{p_i \mid i=1,\cdots,n\}$.}
 
@@
 
-% figure 7
+% figure 7 -> removed
 
-Suppose the point cloud of the complete berry is denoted as $P_{complete}=\{P_i | i=1, \cdots,n\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in the 3D space, and $n$ denotes the number of points. 
+Suppose the point cloud of the complete berry is denoted as $P_{complete}=\{P_i \mid i=1, \cdots,n\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in the 3D space, and $n$ denotes the number of points. 
 In this paper, it is fitted to an ellipsoid surface with three unequal long axes by the least squares method, and the function is shown in Equation (\ref{eq:6}).
@@
 % table 3
+\begin{table}[h]
+    \centering
+    \caption{Instance berry segmentation results from whole bunch}
+    \begin{tabular}{ccc}
+        \hline
+        \textbf{Model} & \textbf{Class} & \textbf{AP@50:5:95} \\
+        \hline
+        \multirow{2}{*}{SoftGroup \citep{vu_softgroup_2022}} & Berry & 0.995 \\
+        \cline{2-3}
+        & Stem & 0.941 \\
+        \hline
+    \end{tabular}
+\end{table}
 
@@
 % figure 13
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure11.pdf}
+    \caption{Segmentation results of the bunch of four species of fresh grape, the stems point cloud and the noise point cloud are set to black, and the different color point sets indicate the point clouds of different berry instances obtained.}
+    \label{fig:raw13}
+\end{figure}
 
@@
 % table 4
+\begin{table}[h]
+    \centering
+    \caption{Experimental results of different completion networks based on self-supervised training for berry point cloud}
+    \begin{tabular}{cccccc}
+        \hline
+        \textbf{Model} & \textbf{DataSet} & \textbf{CD-distance $\downarrow$} & \textbf{Precision $\uparrow$} & \textbf{Recall $\uparrow$} & \textbf{F-score $\uparrow$} \\
+        \hline
+        \multirow{2}{*}{PoinTr} & Test & 9.036 & 0.721 & 0.705 & 0.713 \\
+        \cline{2-6}
+        & Inference & 10.542 & 0.623 & 0.601 & 0.612 \\
+        \hline
+        \multirow{2}{*}{SnowFlakeNet} & Test & 11.235 & 0.512 & 0.534 & 0.521 \\
+        \cline{2-6}
+        & Inference & 12.384 & 0.415 & 0.423 & 0.419 \\
+        \hline
+        \multirow{2}{*}{TopNet} & Test & 23.019 & 0.201 & 0.200 & 0.201 \\
+        \cline{2-6}
+        & Inference & 31.88 & 0.155 & 0.154 & 0.154 \\
+        \hline
+        \multirow{2}{*}{GRNet} & Test & 19.24 & 0.402 & 0.392 & 0.397 \\
+        \cline{2-6}
+        & Inference & 21.25 & 0.365 & 0.363 & 0.364 \\
+        \hline
+        \multirow{2}{*}{GrapeCPNet (\textbf{Ours})} & Test & \textbf{8.315} & \textbf{0.729} & \textbf{0.772} & \textbf{0.751} \\
+        \cline{2-6}
+        & Inference & \textbf{9.158} & \textbf{0.685} & \textbf{0.696} & \textbf{0.689} \\
+        \hline
+    \end{tabular}
+\end{table}
 
 % figure 14
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure12.pdf}
+    \caption{Example of four fresh grape berry point cloud completion results: in each block, the left side shows the incomplete berry point cloud obtained from the segmentation of the bunch, and the right side shows the completion results using GrapeCPNet under the self-supervised training-based method.}
+    \label{fig:raw14}
+\end{figure}
 
@@
 % figure 16
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure13.pdf}
+    \caption{Example of visualization of the predicted complete berry point cloud fitted to the surface of an ellipsoid.}
+    \label{fig:raw16}
+\end{figure}
 
@@
 % figure 17
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure14.pdf}
+    \caption{Experimental results of axis length calculation for four species of fresh grape.
+From (a)-(d): Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape, and from (1)-(3): the calculation of the long, middle, and short axis, respectively.}
+    \label{fig:raw16}
+\end{figure}
 
@@
 % figure 18
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure15.pdf}
+    \caption{Experimental results of berry volume calculation.}
+    \label{fig:raw18}
+\end{figure}
 

### 2025-01-06 main.tex
update fig tbl eq citation

@@
 In this section, we first introduce the four experimental grape materials and the 3D reconstruction methods for obtaining 3D point cloud data. 
-We then provide a brief overview of the SoftGroup [32] deep learning network, which was trained on our previous point cloud dataset for instance segmentation of individual berries (Fig. 1a). 
-Next, we detail the proposed self-supervised completion deep learning module, GrapeCPNet, which predicts the complete berry point cloud from segmented partial berries (Fig. 1b). 
-Subsequently, we describe the module and method for calculating phenotypic traits (Fig. 1c). 
+We then provide a brief overview of the SoftGroup [32] deep learning network, which was trained on our previous point cloud dataset for instance segmentation of individual berries (Fig.~\ref{fig:raw1}a).
+Next, we detail the proposed self-supervised completion deep learning module, GrapeCPNet, which predicts the complete berry point cloud from segmented partial berries (Fig.~\ref{fig:raw1}b). 
+Subsequently, we describe the module and method for calculating phenotypic traits (Fig.~\ref{fig:raw1}c). 
 Finally, we introduced the evaluation method for model training and results validation.
@@
 To ensure the generality and applicability of the study, this paper considers the sparsity, shape, and color of the bunch, and chooses four common fresh grapes as the experimental materials, which are Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape.
-The characteristics of them are shown in Table 1 and the examples are shown in Figure 8.
+The characteristics of them are shown in Table~\ref{tlb:1} and the examples are shown in Figure~\ref{fig:raw86}.
 
@@
 In this paper, the multi-view images acquisition and 3D reconstruction by Agisoft Metashape (Agisoft LLC, St.
-Petersburg, Russia) was used to obtain the 3D point cloud of bunch (Fig.
-9a) and single complete berry (Fig.
-9b).
-Their correspondence of the same berry was also labelled as shown in Figure 9c
+Petersburg, Russia) was used to obtain the 3D point cloud of bunch (Fig.~\ref{fig:raw9}a) and single complete berry (Fig.~\ref{fig:raw9}b).
+Their correspondence of the same berry was also labelled as shown in Figure~\ref{fig:raw9}c
 
@@
 
-For whole bunch multi-view images acquisition, the device was built as shown in Figure 9a. 
-One grape bunch was hung on the hook which was attached to propellers driven by stepping motors (Fig. 9a1) that can achieve rotation at a certain speed. 
-The entire device was placed in front of a solid-colored backdrop (Fig. 9a2 ), and multiple cameras were set up to photograph the bunch from different height angles. 
+For whole bunch multi-view images acquisition, the device was built as shown in Figure~\ref{fig:raw9}a. 
+One grape bunch was hung on the hook which was attached to propellers driven by stepping motors (Fig.~\ref{fig:raw9}a1) that can achieve rotation at a certain speed. 
+The entire device was placed in front of a solid-colored backdrop (Fig.~\ref{fig:raw9}a2), and multiple cameras were set up to photograph the bunch from different height angles. 
 In addition, a ruler with markers were used for scale correction. 
-For single complete berry multi-view images acquisition in batch (Fig. 9b). 
-Nine berries were fixed floating by needle disk (Fig. 9b1) on a turntable device (Fig. 9b2). 
+For single complete berry multi-view images acquisition in batch (Fig.~\ref{fig:raw9}b). 
+Nine berries were fixed floating by needle disk (Fig.~\ref{fig:raw9}b1) on a turntable device (Fig.~\ref{fig:raw9}b2). 
 The background, cameras, and marker settings are similar to the previous bunch reconstruction. 
-The number of reconstructed images and the shooting parameters are selected, as shown in Table 2. 
-Examples of the point cloud of bunch, multiple berries, and single complete berries from multiple berries are shown in Figure 10.
+The number of reconstructed images and the shooting parameters are selected, as shown in Table~\ref{tlb:2}. 
+Examples of the point cloud of bunch, multiple berries, and single complete berries from multiple berries are shown in Figure~\ref{fig:raw10}.
 
@@
 
-As Figure 1a, the single-bunch shell point cloud was represented as $P_{bunch}=\{p_i \mid i=1, \cdots, m\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in 3D space and $m$ denotes the total number of points in the point cloud of the bunch.
+As Figure~\ref{fig:raw1}a, the single-bunch shell point cloud was represented as $P_{bunch}=\{p_i \mid i=1, \cdots, m\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in 3D space and $m$ denotes the total number of points in the point cloud of the bunch.
 The bunch point cloud segmentation task expects to segment $P_{bunch}$ into a combination of several individual subsets of the berries point cloud and a subset of the stem point cloud, as shown in Equation~(\ref{eq:1}).
@@
 The task of instance berry segmentation from a bunch is complex. 
-As shown in Figure 2, it involves distinct localization features and complex boundary morphology. 
+As shown in Figure~\ref{fig:raw2}, it involves distinct localization features and complex boundary morphology. 
 The distinct localization feature implies that individual berry has more geometrical and morphological details compared to the overall shape of the grape bunch, particularly when the object is a small-sized point cloud [31].
@@
 % todo
-Section 2.1.2 was labeled at the instance-level (Fig. 11). 
+Section 2.1.2 was labeled at the instance-level (Fig.~\ref{fig:raw11}). 
 This paper collected and labeled 8 bunches for each of the four species (total 32 bunches). 
@@
 This subsection introduced the self-supervised strategy to generating paired training data without manual annotation and the structure of grape completion network, GrapeCPNet. 
-The whole workflow of proposed GrapeCPNet is shown in Figure 3.
+The whole workflow of proposed GrapeCPNet is shown in Figure~\ref{fig:raw3}.
 
@@
 (Section 2.1.2) and were used as ground truth, while the incomplete grapes were cut from the complete grapes following characteristic of occlusion and were used as training inputs. 
-This data pair generation strategy saved huge amounts of data annotation. The common incomplete characteristics of the berry are shown in Figure 4.
+This data pair generation strategy saved huge amounts of data annotation. The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
 Based on the incomplete characteristics, we developed a cutting method for the complete berry point cloud to generate the incomplete berry point cloud.
@@
 
-This proposed algorithm is shown in Algorithm 1. 
+This proposed algorithm is shown in Algorithm \ref{alg:1}. 
 The inputs include a single complete berry point cloud and the maximum number of cutting area (5 in this paper). 
-The output is the cut incomplete berry point clouds. First, the single complete berry point cloud was normalized and centralized (Fig. 12a). 
+The output is the cut incomplete berry point clouds. First, the single complete berry point cloud was normalized and centralized (Fig.~\ref{fig:raw12}a). 
 Second, randomly pick the integer number of cuts lower than maximum number, in this paper ranging from 1 to 5. 
@@
 In this paper we set maximum 0.75 for center offsets and maximum 0.25 for radius. 
-Continue the previous cut looping until meet the cut limits. The cut incomplete berry of each loop was all saved as training data (Fig. 12b).
+Continue the previous cut looping until meet the cut limits. The cut incomplete berry of each loop was all saved as training data (Fig.~\ref{fig:raw12}b).
 
@@
 \begin{algorithm}
-    \caption{The cutting method for generating incomplete training data}
+    \caption{The cutting method for generating training data of incomplete berries}
     \label{alg:1}
-    \KwData{$P_C = \{p_i \mid i = 1, \cdots, t\}$ \tcp{One complete berry pointcloud}}
-    \KwData{$n$ \tcp{Number of incomplete berries to be generated}}
+    \KwData{$P_C$ \tcp{one complete berry point cloud}}
+    \KwData{$n$ \tcp{generate incomplete berries number}}
     \KwResult{$P_{\text{output}} = \{P_{o_i} \mid i = 1, \cdots, n\}$ \tcp{incomplete berry point cloud sets} }
@@
 For model training, 36 complete berry are collected for each of the four species of grape (in total 144). 
-To further expand the data quantity, based on the single complete berry point cloud obtained by reconstruction, this paper uses the PointFlow [40], a point cloud generation model to generate the simulated samples (Fig.
-12c).
+To further expand the data quantity, based on the single complete berry point cloud obtained by reconstruction, this paper uses the PointFlow [40], a point cloud generation model to generate the simulated samples (Fig.~\ref{fig:raw12}c).
 Then, 500 complete berry point clouds are generated from PointFlow method. 
@@
 By checking the labels of these berries, the corresponding single complete berry reconstruction results %todo
-(Section 2.1.2 \& Fig. 9c) were used as ground truth.
+(Section 2.1.2 \& Fig.~\ref{fig:raw9}c) were used as ground truth.
 
@@
 This paper combines the centroid-based sparse completion structure of PoinTr [35] with the diffusion-based dense completion structure of SnowFlakeNet [36]. 
-Based on the characteristics of the berry, it has two parts: contour completion and surface completion. The network structure is shown in Figure 5.
+Based on the characteristics of the berry, it has two parts: contour completion and surface completion. The network structure is shown in Figure~\ref{fig:raw5}.
 
@@
 
-Then, the 3D convolutional neural networks DGCNN [37] and MLP [38] are used to obtain the local structural features of each point $p_i$ in the center point set, as shown in Equation (\ref{eq:2}).
+Then, the 3D convolutional neural networks DGCNN [37] and MLP [38] are used to obtain the local structural features of each point $p_i$ in the center point set, as shown in Equation~(\ref{eq:2}).
 
@@
 Finally, since the $\varphi = \{ \varphi(p_i) \mid i=1, \cdots, M \}$ contains the relative position information of each point, it can be used as the position embedding and the serialized feature $F = \{F_i \mid i=1, \cdots, M \}$ was fed into the geometrically-aware Transformer [39] based encoder.
-The process is Equation (\ref{eq:3}).
+The process is Equation~(\ref{eq:3}).
 
@@
 {\raggedright where, $T_e$ denotes the encoder of the Transformer and $V=\{V_i |i=1, \cdots, M\}$ denotes the encoded feature. 
-Next, the predicted centroid point set of the missing part was output by the decoder, and the process as Equation (\ref{eq:4}).}
+Next, the predicted centroid point set of the missing part was output by the decoder, and the process as Equation~(\ref{eq:4}).}
 
@@
 On the other hand, the iteration of multiple point splitting steps delivers information from each one to the next one. 
-This approach effectively characterizes the curvature changes on the surface of the berry. The process is Equation (\ref{eq:5}).
+This approach effectively characterizes the curvature changes on the surface of the berry. The process is Equation~(\ref{eq:5}).
 
@@
 
-To describe the 3D morphology of berries, this paper used ellipsoidal surface fitting with three axes, for the completed berry point cloud (Fig. 7).
+To describe the 3D morphology of berries, this paper used ellipsoidal surface fitting with three axes, for the completed berry point cloud (Fig.~\ref{fig:raw7}).
 
@@
 Suppose the point cloud of the complete berry is denoted as $P_{complete}=\{P_i \mid i=1, \cdots,n\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in the 3D space, and $n$ denotes the number of points. 
-In this paper, it is fitted to an ellipsoid surface with three unequal long axes by the least squares method, and the function is shown in Equation (\ref{eq:6}).
+In this paper, it is fitted to an ellipsoid surface with three unequal long axes by the least squares method, and the function is shown in Equation~(\ref{eq:6}).
 
@@
 Thus, the values of $a$, $b$, $c$ can represent the berry radius parameters. 
-At the same time, the volume of the berry can be calculated as shown in Equation (\ref{eq:7}).
+At the same time, the volume of the berry can be calculated as shown in Equation~(\ref{eq:7}).
 
@@
 In this paper, we use the format of PoinTr [35] that is consistent with the PCN dataset [42] and use the chamfer distance (CD-distance) and F-Score to measure the effect of berry completion. 
-For each sample, the chamfer distance $d_CD$ between the predicted point set $P$ and the true point set $G$ is calculated as shown in Equation (\ref{eq:8})
+For each sample, the chamfer distance $d_CD$ between the predicted point set $P$ and the true point set $G$ is calculated as shown in Equation~(\ref{eq:8})
 
@@
 %todo
-Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table 3.
+Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table~\ref{tlb:3}.
 
@@
 
-As can be seen from Table 3, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.
-The visualization results of four fresh grapes for bunch point cloud segmentation using SoftGroup are shown in Figure 13.
+As can be seen from Table~\ref{tlb:3}, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.
+The visualization results of four fresh grapes for bunch point cloud segmentation using SoftGroup are shown in Figure~\ref{fig:raw13}.
 
@@
 Meanwhile, since the point cloud obtained after berry picking is used as the ground truth, the point cloud alignment is performed to calculate evaluation metrics of the predicted complete berry point cloud with the ground truth.
-The experimental results of comparing to other point cloud completion algorithms are shown in Table 4. 
+The experimental results of comparing to other point cloud completion algorithms are shown in Table~\ref{tlb:4}. 
 GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the other comparative algorithms. 
-The visualization of using GrapeCPNet to complement the incomplete berry segmented from the bunch in the application phase is shown in Figure 14.
+The visualization of using GrapeCPNet to complement the incomplete berry segmented from the bunch in the application phase is shown in Figure~\ref{fig:raw14}.
 
@@
 Section 2.5.3.
-The radius parameters are calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure 16.
+The radius parameters are calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure~\ref{fig:raw16}.
 
@@
 Section 2.1.2 can translate the scale of the point cloud space to the real world, so as to get the real radius length of the berry.
-Because of the large difference between the ratio of the long and short axis of different species, this paper conducted experiments on the calculation of the axis length of four species respectively, as shown in Figure 17.
+Because of the large difference between the ratio of the long and short axis of different species, this paper conducted experiments on the calculation of the axis length of four species respectively, as shown in Figure~\ref{fig:raw17}.
 
@@
 
-As shown in Figure 17, each point on the subplot block represents a berry sample, the horizontal coordinate indicates the true value of the axis length, the vertical coordinate indicates the prediction value, and the $R^2$ and MAE are displayed in the figure at the same time.
+As shown in Figure~\ref{fig:raw17}, each point on the subplot block represents a berry sample, the horizontal coordinate indicates the true value of the axis length, the vertical coordinate indicates the prediction value, and the $R^2$ and MAE are displayed in the figure at the same time.
 From the results, it can be seen that the proposed method achieves an average $R^2$ of 0.86 for the three axis lengths of the four species of grape. 
@@
 The experimental results show that the proposed method has achieved high accuracy in the calculation of the radius of different grape species. 
-In addition, based on the radius prediction results, the volume of all 108 berry samples is calculated in this paper, and the experimental results are shown in Figure 18.
+In addition, based on the radius prediction results, the volume of all 108 berry samples is calculated in this paper, and the experimental results are shown in Figure~\ref{fig:raw18}.
 

### 2025-01-06 main.tex
update reference

@@
 \AtBeginEnvironment{align}{\setstretch{1}\vspace{-\baselineskip}}
+% remove double space for references
+\AtBeginEnvironment{thebibliography}{\linespread{1}\selectfont}
 
@@
 To better guide planting strategy and monitoring growing status, several geometric parameters like counts, length, and volume at bunch level and berry level are commonly used in actual applications.
-[1-4].
-Among them, the number and the radius of the berries are the most important phenotypic parameters [5]. 
+\citep{luo_prediction_2024,raihen_prediction_2024,kamangir_largescale_2024,barbole_comparative_2023}.
+Among them, the number and the radius of the berries are the most important phenotypic parameters \citep{sneha_acrescale_2024}. 
 Traditional manual phenotyping of parameter measurements is labor-intensive and time-consuming, and often destructive. 
-To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic parameters based on computer vision has attracted extensive interest in recent years [6].
-Several simple geometry parameters can be acquired from 2D images by using computer vision algorithms like pattern recognition, machine learning, and deep learning [7]. 
+To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic parameters based on computer vision has attracted extensive interest in recent years \citep{li_review_2020}.
+Several simple geometry parameters can be acquired from 2D images by using computer vision algorithms like pattern recognition, machine learning, and deep learning \citep{zabawa_counting_2020}. 
 Projecting the 3D world onto a 2D image plane inevitably results in information loss. 
@@
 Additionally, clustered berries and their shadows naturally create complex structures even under controlled lightning conditions. 
-Leaving difficulties for obtaining reliable measurements of phenotypic parameters through 2D image analysis [8,9].
+Leaving difficulties for obtaining reliable measurements of phenotypic parameters through 2D image analysis \citep{fei_comprehensive_2022,xiang_multispace_2023}.
 
-Advances in 3D scanning and reconstruction techniques have made it possible to retain detailed spatial information about objects, enabling the acquisition of complex 3D morphological traits in grape bunches [10-11].
-Researchers have developed 3D phenotyping processes for grapes by combining feature-engineered point cloud processing algorithms[12,13]. 
+Advances in 3D scanning and reconstruction techniques have made it possible to retain detailed spatial information about objects, enabling the acquisition of complex 3D morphological traits in grape bunches \citep{jiang_3d_2019,ni_threedimensional_2021}.
+Researchers have developed 3D phenotyping processes for grapes by combining feature-engineered point cloud processing algorithms \citep{rose_automated_2016,rist_highprecision_2018}. 
 These methods primarily rely on point cloud segmentation techniques, such as edge-based segmentation, region-growing segmentation, and sphere-fitting algorithms. 
@@
 On the other hand, deep learning approach uses a data-driven approach to learn features from point cloud data automatically. 
-It recently shows promising adaptability and accuracy in plant 3D phenotyping [14-17]. Focusing on point cloud segmentation applications, 
-Li et al. [18] proposed MASPC\_Transform to segment the stems and leaves of rose bush point cloud data to obtain 3D phenotypic parameters. 
-Wang et al. [19] realized leaf instance segmentation by designing the PartNet for lettuce point cloud data. 
-Li et al. [20] proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. 
+It recently shows promising adaptability and accuracy in plant 3D phenotyping \citep{schneider_predicting_2020,scholer_automated_2015,rostami_survey_2019,du_pst_2023}.
+Focusing on point cloud segmentation applications,
+\citet{li_maspc_2022} proposed MASPC\_Transform to segment the stems and leaves of rose bush point cloud data to obtain 3D phenotypic parameters. 
+\citet{wang_3d_2022} realized leaf instance segmentation by designing the PartNet for lettuce point cloud data. 
+\citet{li_psegnet_2022} proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. 
 Unlike previous studies focused on canopy level or individual plant level analysis, instance segmentation alone is insufficient on berry level analysis. 
-The aggregated cluster growth [21] causes the berries to squeezed against each other, leading to interior occlusion and resulting in an incomplete point cloud of berry surfaces. 
+The aggregated cluster growth \citep{du_instance_2023} causes the berries to squeezed against each other, leading to interior occlusion and resulting in an incomplete point cloud of berry surfaces. 
 Therefore, point cloud instance segmentation can only capture partial information rather than that of whole berries.
 
-To address the partial point cloud problem, some researchers applied deep learning-based point cloud completion [22]. 
-Point cloud completion is the task of generating a complete 3D shape given partial point cloud input [23]. 
-Utilizing deep learning methods, researchers have designed point cloud completion networks[24-28]. 
-Park et al.
-[24] introduced DeepSDF to achieve the completion of object point cloud models.
+To address the partial point cloud problem, some researchers applied deep learning-based point cloud completion \citep{wang_unsupervised_2021}. 
+Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
+Utilizing deep learning methods, researchers have designed point cloud completion networks. 
+\citet{park_deepsdf_2019} introduced DeepSDF to achieve the completion of object point cloud models.
 It uses a learned continuous signed distance function to represent a class of shapes in latent space and is tolerant to noisy 3D input data.
-Magistri et al. [25] utilized a latent space of potential fruit appearances and propose an encoder-decoder network that converted a single RGB-D frame to a 3D shape of a complete fruit. 
-This network was extended and upgraded by Blok et al. [47] for high-throughput 3D shape completion of potato tubers on a commercial harvester.
-Tang et al [26] proposed a point cloud completion network Lake-net for furniture model point cloud datasets. 
+\citet{magistri_contrastive_2022} utilized a latent space of potential fruit appearances and propose an encoder-decoder network that converted a single RGB-D frame to a 3D shape of a complete fruit. 
+This network was extended and upgraded by \citet{blok_highthroughput_2025} for high-throughput 3D shape completion of potato tubers on a commercial harvester.
+\citet{tang_lakenet_2022} proposed a point cloud completion network Lake-net for furniture model point cloud datasets. 
 For grape berry application, the completion network is expected to infer a complete point cloud model based on a single partial berry point cloud after bunch segmentation. 
-However, existing models are mainly designed for feature extraction of objects consisting of simple geometric forms such as surfaces with fixed curvature, and absolute planes [29]. 
-The shape of the berry can roughly approach the deformation of a sphere or ellipsoid depending on the species [30], and its surface consists of multiple spherical surfaces of varying curvature, with a rich characterization of details.
+However, existing models are mainly designed for feature extraction of objects consisting of simple geometric forms such as surfaces with fixed curvature, and absolute planes \citep{fei_comprehensive_2022}.
+The shape of the berry can roughly approach the deformation of a sphere or ellipsoid depending on the species, and its surface consists of multiple spherical surfaces of varying curvature, with a rich characterization of details.
 This leads to difficulties in the direct application of existing networks. 
@@
 In this section, we first introduce the four experimental grape materials and the 3D reconstruction methods for obtaining 3D point cloud data. 
-We then provide a brief overview of the SoftGroup [32] deep learning network, which was trained on our previous point cloud dataset for instance segmentation of individual berries (Fig.~\ref{fig:raw1}a).
+We then provide a brief overview of the SoftGroup \citep{vu_softgroup_2022} deep learning network, which was trained on our previous point cloud dataset for instance segmentation of individual berries (Fig.~\ref{fig:raw1}a).
 Next, we detail the proposed self-supervised completion deep learning module, GrapeCPNet, which predicts the complete berry point cloud from segmented partial berries (Fig.~\ref{fig:raw1}b). 
@@
     \caption{Proposed pipeline for grape bunch 3D phenotyping.
-Taking the bunch point cloud data as input, it is realized through three steps: (1) berry instance segmentation by SoftGroup[32], (2) berry point cloud completion by proposed GrapeCPNet, and (3) phenotypic traits calculation.}
+Taking the bunch point cloud data as input, it is realized through three steps: (1) berry instance segmentation by SoftGroup \citep{vu_softgroup_2022}, (2) berry point cloud completion by proposed GrapeCPNet, and (3) phenotypic traits calculation.}
     \label{fig:raw1}
@@
 As shown in Figure~\ref{fig:raw2}, it involves distinct localization features and complex boundary morphology. 
-The distinct localization feature implies that individual berry has more geometrical and morphological details compared to the overall shape of the grape bunch, particularly when the object is a small-sized point cloud [31].
+The distinct localization feature implies that individual berry has more geometrical and morphological details compared to the overall shape of the grape bunch, particularly when the object is a small-sized point cloud \citep{luo_infield_2022}.
 The complex boundary morphology arises from berries pressing against each other, resulting in multiple curves with varying connecting depths. 
@@
 
-In this paper, SoftGroup [32] was selected for bunch point cloud segmentation by comparing different current deep learning-based point cloud instance segmentation models. 
+In this paper, SoftGroup \citep{vu_softgroup_2022} was selected for bunch point cloud segmentation by comparing different current deep learning-based point cloud instance segmentation models. 
 SoftGroup contains two aspects of design: 
@@
 The self-supervised training-based berry point cloud completion was used to predict their complete 3D model. 
-Self-supervised learning is a way of training a model without artificial annotations by using the data itself as truth value to supervise [33]. 
+Self-supervised learning is a way of training a model without artificial annotations by using the data itself as truth value to supervise \citep{fei_selfsupervised_2023}. 
 This subsection introduced the self-supervised strategy to generating paired training data without manual annotation and the structure of grape completion network, GrapeCPNet. 
@@
 For model training, 36 complete berry are collected for each of the four species of grape (in total 144). 
-To further expand the data quantity, based on the single complete berry point cloud obtained by reconstruction, this paper uses the PointFlow [40], a point cloud generation model to generate the simulated samples (Fig.~\ref{fig:raw12}c).
+To further expand the data quantity, based on the single complete berry point cloud obtained by reconstruction, this paper uses the PointFlow \citep{yang_pointflow_2019}, a point cloud generation model to generate the simulated samples (Fig.~\ref{fig:raw12}c).
 Then, 500 complete berry point clouds are generated from PointFlow method. 
@@
 Since the entire contour of the incomplete berry is missing, the model is required to have the ability to predict the incomplete part based on the visible part and make the prediction part fit the real berry surface and avoid detail distortion.
-This paper combines the centroid-based sparse completion structure of PoinTr [35] with the diffusion-based dense completion structure of SnowFlakeNet [36]. 
+This paper combines the centroid-based sparse completion structure of PoinTr \citep{yu_pointr_2021} with the diffusion-based dense completion structure of SnowFlakeNet \citep{xiang_snowflakenet_2021}.
 Based on the characteristics of the berry, it has two parts: contour completion and surface completion. The network structure is shown in Figure~\ref{fig:raw5}.
@@
 Based on the above analysis, this paper utilizes the centroid set of the visible part to infer the centroid set of the invisible part. 
-Specifically, GrapeCPNet uses centroid-based feature extraction in PoinTr [35] to accomplish berry point cloud contour completion. The process is described below:
+Specifically, GrapeCPNet uses centroid-based feature extraction in PoinTr \citep{yu_pointr_2021} to accomplish berry point cloud contour completion. The process is described below:
 
@@
 
-Then, the 3D convolutional neural networks DGCNN [37] and MLP [38] are used to obtain the local structural features of each point $p_i$ in the center point set, as shown in Equation~(\ref{eq:2}).
+Then, the 3D convolutional neural networks DGCNN \citep{wang_dynamic_2019} and MLP \citep{tolstikhin_mlpmixer_2021} are used to obtain the local structural features of each point $p_i$ in the center point set, as shown in Equation~(\ref{eq:2}).
 
@@
 
-Finally, since the $\varphi = \{ \varphi(p_i) \mid i=1, \cdots, M \}$ contains the relative position information of each point, it can be used as the position embedding and the serialized feature $F = \{F_i \mid i=1, \cdots, M \}$ was fed into the geometrically-aware Transformer [39] based encoder.
+Finally, since the $\varphi = \{ \varphi(p_i) \mid i=1, \cdots, M \}$ contains the relative position information of each point, it can be used as the position embedding and the serialized feature $F = \{F_i \mid i=1, \cdots, M \}$ was fed into the geometrically-aware Transformer \citep{vaswani_attention_2017} based encoder.
 The process is Equation~(\ref{eq:3}).
@@
 First, GrapeCPNet sets each point $p$ of the sparse complement $P_{pred-center}=\{p_i \mid i=1,\cdots,N\}$ as a ``seed point''. 
-Then, $P_{pred-center}$ was fed into multiple SPD [36] connected serially of SnowFlakeNet, which are used to realize point splitting and generation. 
+Then, $P_{pred-center}$ was fed into multiple SPD \citep{xiang_snowflakenet_2021} connected serially of SnowFlakeNet, which are used to realize point splitting and generation. 
 On the one hand, the SPD diffuses from the center point in a tree structure around, revealing the detailed geometric structure of the local region. 
@@
 
-In this paper, we use the format of SoftGroup [32] that is consistent with the S3DIS dataset [41] and use the average precision AP [32] as the evaluation metric for berry instance segmentation.
+In this paper, we use the format of SoftGroup \citep{vu_softgroup_2022} that is consistent with the S3DIS dataset \citep{armeni_3d_2016} and use the average precision AP \citep{vu_softgroup_2022} as the evaluation metric for berry instance segmentation.
 In the threshold setting, the average of the APs with selected the IoU (Intersection over Union) from 50\% to 95\% in steps of 5\% is noted as AP@50:5:95.
@@
 
-In this paper, we use the format of PoinTr [35] that is consistent with the PCN dataset [42] and use the chamfer distance (CD-distance) and F-Score to measure the effect of berry completion. 
+In this paper, we use the format of PoinTr \citep{yu_pointr_2021} that is consistent with the PCN dataset \citep{yuan_pcn_2018} and use the chamfer distance (CD-distance) and F-Score to measure the effect of berry completion.
 For each sample, the chamfer distance $d_CD$ between the predicted point set $P$ and the true point set $G$ is calculated as shown in Equation~(\ref{eq:8})
@@
 
-In addition, in order to verify the efficiency of GrapeCPNet, other classical point cloud completion networks, including PoinTr, SnowFlakeNet, TopNet [43], and GRNet [44] are selected as comparison algorithms.
+In addition, in order to verify the efficiency of GrapeCPNet, other classical point cloud completion networks, including PoinTr, SnowFlakeNet, TopNet \citep{tchapmi_topnet_2019}, and GRNet \citep{xie_grnet_2020} are selected as comparison algorithms.
 
@@
 At the same time, we found that GrapeCPNet is not effective in the case of complex berry appearance, such as drop-shaped. 
-We have found that some researchers [45,46] have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network. 
+We have found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
 We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion. 

### 2025-01-06 main.tex
correct tbl ref

@@
 To ensure the generality and applicability of the study, this paper considers the sparsity, shape, and color of the bunch, and chooses four common fresh grapes as the experimental materials, which are Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape.
-The characteristics of them are shown in Table~\ref{tlb:1} and the examples are shown in Figure~\ref{fig:raw86}.
+The characteristics of them are shown in Table~\ref{tbl:1} and the examples are shown in Figure~\ref{fig:raw86}.
 
@@
         \hline
-    \label{tlb:1}
+    \label{tbl:1}
     \end{tabular}
@@
 The background, cameras, and marker settings are similar to the previous bunch reconstruction. 
-The number of reconstructed images and the shooting parameters are selected, as shown in Table~\ref{tlb:2}. 
+The number of reconstructed images and the shooting parameters are selected, as shown in Table~\ref{tbl:2}. 
 Examples of the point cloud of bunch, multiple berries, and single complete berries from multiple berries are shown in Figure~\ref{fig:raw10}.
@@
         \hline
-    \label{tlb:2}
+    \label{tbl:2}
     \end{tabular}
@@
 %todo
-Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table~\ref{tlb:3}.
+Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table~\ref{tbl:3}.
 
@@
     \end{tabular}
+    \label{tbl:3}
 \end{table}
 
-As can be seen from Table~\ref{tlb:3}, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.
+As can be seen from Table~\ref{tbl:3}, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.
 The visualization results of four fresh grapes for bunch point cloud segmentation using SoftGroup are shown in Figure~\ref{fig:raw13}.
@@
 Meanwhile, since the point cloud obtained after berry picking is used as the ground truth, the point cloud alignment is performed to calculate evaluation metrics of the predicted complete berry point cloud with the ground truth.
-The experimental results of comparing to other point cloud completion algorithms are shown in Table~\ref{tlb:4}. 
+The experimental results of comparing to other point cloud completion algorithms are shown in Table~\ref{tbl:4}. 
 GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the other comparative algorithms. 
@@
     \end{tabular}
+    \label{tbl:4}
 \end{table}

### 2025-01-06 main.tex
update section cite

@@
 \subsubsection{3D reconstruction of grape}
+\label{sec:212}
 
@@
 \subsection{Berry Instance Segmentation}
+\label{sec:22}
 
@@
 
-In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in
-% todo
-Section 2.1.2 was labeled at the instance-level (Fig.~\ref{fig:raw11}). 
+In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was labeled at the instance-level (Fig.~\ref{fig:raw11}). 
 This paper collected and labeled 8 bunches for each of the four species (total 32 bunches). 
@@
 The point cloud completion network often requires the incomplete-complete data pairs of the same object to build a mapping relationship. 
-In this paper, the complete grapes were obtained by single berry reconstruction 
-%todo
-(Section 2.1.2) and were used as ground truth, while the incomplete grapes were cut from the complete grapes following characteristic of occlusion and were used as training inputs. 
+In this paper, the complete grapes were obtained by single berry reconstruction (Section~\ref{sec:212}) and were used as ground truth, while the incomplete grapes were cut from the complete grapes following characteristic of occlusion and were used as training inputs.
 This data pair generation strategy saved huge amounts of data annotation. The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
@@
 
-For the model inference validation, among 12 testing grape bunches of the berry instance segmentation model 
-%todo
-(Section 2.2), each grape species was randomly selected one bunch (total 4 bunches). 
+For the model inference validation, among 12 testing grape bunches of the berry instance segmentation model (Section~\ref{sec:22}), each grape species was randomly selected one bunch (total 4 bunches).
 For each bunch, 27 berries are randomly selected, and finally obtain a total of 108 incomplete berries as the input data for completion network inference validation. 
-By checking the labels of these berries, the corresponding single complete berry reconstruction results %todo
-(Section 2.1.2 \& Fig.~\ref{fig:raw9}c) were used as ground truth.
+By checking the labels of these berries, the corresponding single complete berry reconstruction results (Section~\ref{sec:212} \& Fig.~\ref{fig:raw9}c) were used as ground truth.
 
@@
 
-In order to validate the accuracy of extracted morphological traits, those 12 validation bunches in %todo
-Section 2.2 were continuously used after instance berry segmentation and berry completion. 
+In order to validate the accuracy of extracted morphological traits, those 12 validation bunches in Section~\ref{sec:22} were continuously used after instance berry segmentation and berry completion. 
 The radius and volume of the 108 samples are calculated. 
@@
 \subsubsection{Berry instance segmentation}
-
+\label{sec:251}
 In this paper, we use the format of SoftGroup \citep{vu_softgroup_2022} that is consistent with the S3DIS dataset \citep{armeni_3d_2016} and use the average precision AP \citep{vu_softgroup_2022} as the evaluation metric for berry instance segmentation.
@@
 \subsubsection{Phenotypic traits calculation}
-
+\label{sec:253}
 In order to evaluate the efficiency of the number of berry statistics and the calculation of berry radius and volume, the MAE (Mean Absolute Error) and the coefficient of determination $R^2$ (R-Square) are used to calculate the error between the prediction value and the true value of the sample.
@@
 Bunch point cloud segmentation is mainly realized based on SoftGroup, a point cloud segmentation network. 
-This paper calculates the segmentation results for the berry instances and stem instances using the dataset introduced in 
-%todo
-Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table~\ref{tbl:3}.
+This paper calculates the segmentation results for the berry instances and stem instances using the dataset introduced in Section~\ref{sec:22} and the evaluation metrics in Section~\ref{sec:251}, as shown in Table~\ref{tbl:3}.
 
@@
 Based on the method in this paper, the bunch point cloud is used as input, and the acquired 3D phenotypic parameters are the final output, which mainly contains two parts: the bunch-level phenotypic parameters and the berry-level phenotypic parameters.
-In this paper, experiments are conducted to calculate berry radius and volume with the dataset in the evaluation metrics in 
-%todo
-Section 2.5.3.
+In this paper, experiments are conducted to calculate berry radius and volume with the dataset in the evaluation metrics in Section~\ref{sec:253}.
 The radius parameters are calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure~\ref{fig:raw16}.
@@
 Three lengths of the radius of the berry can be obtained by fitting the predicted point cloud of the complete berry shell to the surface of an ellipsoid. 
-Meanwhile, the point cloud data acquisition method in 
-%todo
-Section 2.1.2 can translate the scale of the point cloud space to the real world, so as to get the real radius length of the berry.
+Meanwhile, the point cloud data acquisition method in Section~\ref{sec:212} can translate the scale of the point cloud space to the real world, so as to get the real radius length of the berry.
 Because of the large difference between the ratio of the long and short axis of different species, this paper conducted experiments on the calculation of the axis length of four species respectively, as shown in Figure~\ref{fig:raw17}.

### 2025-01-06 main.tex
update wei's comments

@@
 
-To address the partial point cloud problem, some researchers applied deep learning-based point cloud completion \citep{wang_unsupervised_2021}. 
+To address the issue of partial point clouds, point cloud shape completion is one of the most commonly employed solutions.
+\citet{ge_symmetrybased_2020} assume that strawberries are symmetrical, suggesting that their shape can be completed by mirroring the existing shape, provided an appropriate symmetrical plane can be identified.
+\citet{marangoz_fruit_2022} proposed an super-ellipsoids matching approach to map fruits on plants and estimate their shape.
+However, these methods are limited to specific fruit characteristics and require manual design of algorithms tailored to the features of the fruit, lacking the potential for generalized application.
+some researchers applied deep learning-based point cloud completion \citep{wang_unsupervised_2021}. 
 Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
@@
 \citet{tang_lakenet_2022} proposed a point cloud completion network Lake-net for furniture model point cloud datasets. 
-For grape berry application, the completion network is expected to infer a complete point cloud model based on a single partial berry point cloud after bunch segmentation. 
-However, existing models are mainly designed for feature extraction of objects consisting of simple geometric forms such as surfaces with fixed curvature, and absolute planes \citep{fei_comprehensive_2022}.
-The shape of the berry can roughly approach the deformation of a sphere or ellipsoid depending on the species, and its surface consists of multiple spherical surfaces of varying curvature, with a rich characterization of details.
-This leads to difficulties in the direct application of existing networks. 
-Therefore, there is an urgent demand to construct a network that can complete the detailed surface of an incomplete berry point cloud.
+For grape berry application, the shape of the berry can roughly approach the deformation of a sphere or ellipsoid depending on the species, and its surface consists of multiple spherical surfaces of varying curvature, with a rich characterization of details.
+The existing datasets from other fruits cannot be applied directly, and manually creating paired training datasets is time-consuming and labor-intensive \citep{blok_highthroughput_2025}.
+Therefore, there is a demand to develop a network and pipeline, capable of completing the detailed surface of an incomplete berry point cloud while requiring less labor-intensive training data preparation.
 
@@
 (1) individual berry segmentation module that segment each berry from 3D point cloud of whole bunch; 
-(2) point cloud completion module that complete the missing part of segmentated berry point cloud data; 
+(2) point cloud completion module that complete the missing part of segmented berry point cloud data; 
 (3) phenotyping module that extract berry phenotypic traits such as radius and volume. 
@@
 
+\section*{Declaration of generative AI and AI-assisted technologies in the writing process.}
+During the preparation of this work the author(s) used ChatGPT in order to check grammar, spelling, and improve fluency.
+After using this tool/service, the author(s) reviewed and edited the content as needed and take(s) full responsibility for the content of the published article.
+
 \section*{Declaration of competing interest}
@@
 \section*{Data availability}
-The dataset, model weight and code will be made available on request.
+The dataset and model weight will be available on request.
 
 \section*{Funding}
-This study is partially funded by the ...
+This study was partially supported by the National Natural Science Foundation of China (NSFC) Program 62276009 and the Japan Science and Technology Agency (JST) AIP Acceleration Research JPMJCR21U3.
 
 \section*{Acknowledgements}
-We would like to thank ... \citep{blok_highthroughput_2025}
+We would like to thank ...
 

### 2025-01-06 main.tex
pass spell check

@@
     \caption{Flowchart of the self-supervised berry point cloud completion, including model training and model inferencing (application) phases.
-In the training phase, the paired incomplete training data was generated from the complete single berry point cloud, then train GrapeCPNet self-supervisely without manual annotation.
+In the training phase, the paired incomplete training data was generated from the complete single berry point cloud, then train GrapeCPNet using self-supervised methods without manual annotation.
 In the application phase, the incomplete berry point cloud is input into the trained model to obtain a complete prediction berry.}
@@
 
-To describe the 3D morphology of berries, this paper used ellipsoidal surface fitting with three axes, for the completed berry point cloud (Fig.~\ref{fig:raw7}).
+To describe the 3D morphology of berries, this paper used ellipsoidal surface fitting with three axes, for the completed berry point cloud.
 
@@
 From (a)-(d): Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape, and from (1)-(3): the calculation of the long, middle, and short axis, respectively.}
-    \label{fig:raw16}
+    \label{fig:raw17}
 \end{figure}
@@
 \section*{CRediT authorship contribution statement}
-\textbf{Wenli Zhang}: conceptualisation, methodology, supervision, funding acquisition, project administration, writing - review; \textbf{Chao Zheng}: methodology, software, data curation, writing - original draft \& editing; \textbf{Chenhuizi Wang}: data curation, software; \textbf{Pieter M.
-Blok}: methodology, supervision, writing - review \& editing; \textbf{Haozhou Wang}: methodology, writing - review \& editing; \textbf{Wei Guo}: conceptualisation, methodology, funding acquisition, supervision, writing - review \& editing.
+\textbf{Wenli Zhang}: conceptualization, methodology, supervision, funding acquisition, project administration, writing - review; \textbf{Chao Zheng}: methodology, software, data curation, writing - original draft \& editing; \textbf{Chenhuizi Wang}: data curation, software; \textbf{Pieter M.
+Blok}: methodology, supervision, writing - review \& editing; \textbf{Haozhou Wang}: methodology, writing - review \& editing; \textbf{Wei Guo}: conceptualization, methodology, funding acquisition, supervision, writing - review \& editing.
 

### 2025-01-06 main.tex
recheck

@@
 To address the issue of partial point clouds, point cloud shape completion is one of the most commonly employed solutions.
-\citet{ge_symmetrybased_2020} assume that strawberries are symmetrical, suggesting that their shape can be completed by mirroring the existing shape, provided an appropriate symmetrical plane can be identified.
+Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
+For instance, \citet{ge_symmetrybased_2020} assume that strawberries are symmetrical, suggesting that their shape can be completed by mirroring the existing shape, provided an appropriate symmetrical plane can be identified.
 \citet{marangoz_fruit_2022} proposed an super-ellipsoids matching approach to map fruits on plants and estimate their shape.
-However, these methods are limited to specific fruit characteristics and require manual design of algorithms tailored to the features of the fruit, lacking the potential for generalized application.
+However, these methods are limited to specific fruit characteristics and require manual design of algorithms according to the features of the fruit, lacking the potential for generalized application.
 some researchers applied deep learning-based point cloud completion \citep{wang_unsupervised_2021}. 
-Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
 Utilizing deep learning methods, researchers have designed point cloud completion networks. 
@@
 For grape berry application, the shape of the berry can roughly approach the deformation of a sphere or ellipsoid depending on the species, and its surface consists of multiple spherical surfaces of varying curvature, with a rich characterization of details.
-The existing datasets from other fruits cannot be applied directly, and manually creating paired training datasets is time-consuming and labor-intensive \citep{blok_highthroughput_2025}.
+The existing datasets from other fruits cannot be applied directly, and manually creating paired training datasets is time-consuming and labor-intensive.
 Therefore, there is a demand to develop a network and pipeline, capable of completing the detailed surface of an incomplete berry point cloud while requiring less labor-intensive training data preparation.
@@
 The proposed pipeline includes: 
-(1) individual berry segmentation module that segment each berry from 3D point cloud of whole bunch; 
-(2) point cloud completion module that complete the missing part of segmented berry point cloud data; 
-(3) phenotyping module that extract berry phenotypic traits such as radius and volume. 
+(1) a individual berry segmentation module that segment each berry from 3D point cloud of whole bunch; 
+(2) a point cloud completion module that complete the missing part of segmented berry point cloud data through automatic training data generation; 
+(3) a phenotyping module that extract berry phenotypic traits such as radius and volume. 
 And at the end, the pipeline has been tested on four different fresh grape species (Red, Green, Kyoho, and Shine Muscat Grape).
@@
 {\raggedright where, $P_{berry_{i}}$ denotes the subset point cloud of the $i^{\text{th}}$ berry in the bunch, $n$ denotes the number of all the berries contained in the bunch, and $P_{stem}$ denotes the set of stem point cloud.
-Meanwhile, each subset $P_{berry_{i}}=\{p_j \mid j=1, \cdots, k\}$ consists of multiple points in 3D space, which can represent the location and morphology of the visible part of the berry within the bunch.}
+Meanwhile, each subset $P_{berry_{i}}=\{p_i \mid i=1, \cdots, k\}$ consists of multiple points in 3D space, which can represent the location and morphology of the visible part of the berry within the bunch.}
 
@@
 
-    $\hat{P_C} \gets Normalize(Translate(P_C))$ \tcp{center to $(0,0,0)$, range to $[-0.5, 0.5]$}
+    $\hat{P}_C \gets \text{Normalize}(\text{Translate}(P_C))$ \tcp{center to $(0,0,0)$, range to $[-0.5, 0.5]$}
     \For{$i = 0 \to n$}{
         set $m = \text{random}\{1,2,3,4,5\}$ \tcp{cut incomplete single berry $m$ times}
-        $P_{o_i} \gets copy(\hat{P_C})$ \tcp{initialize one output}
+        $P_{o_i} \gets copy(\hat{P}_C)$ \tcp{initialize one output}
         \For{$j = 0 \to m$}{
-            set $O = \{(x_o, y_o, z_o) \mid x, y, z \in \text{random}[-0.75, 0.75]\}$ \tcp{center variable} 
-            set $R = \text{random}[0.25, 0.75]$ \tcp{radius variable}
-            set $M_S \gets sphere(O, R)$ \tcp{genreate sphere cut model}
+            set $O = \{(x_o, y_o, z_o) \mid x, y, z \in \text{random}[-0.75, 0.75]\}$ \tcp{center} 
+            set $R = \text{random}[0.25, 0.75]$ \tcp{radius}
+            set $M_S \gets \text{sphere}(O, R)$ \tcp{genreate sphere cut model}
             $P_{o_i} = P_{o_i} - P_{o_i} \cap M_S$ \tcp{remove overlap with cut shpere model}
         }
-        $P_{o_i} \in P_{\text{output}}$ \tcp{add to output set}
+        $P_{\text{output}_i} \gets P_{o_i}$ \tcp{add to output set}
     }
@@
         \cline{2-6}
-        & Inference & 31.88 & 0.155 & 0.154 & 0.154 \\
+        & Inference & 31.880 & 0.155 & 0.154 & 0.154 \\
         \hline
-        \multirow{2}{*}{GRNet} & Test & 19.24 & 0.402 & 0.392 & 0.397 \\
+        \multirow{2}{*}{GRNet} & Test & 19.240 & 0.402 & 0.392 & 0.397 \\
         \cline{2-6}
-        & Inference & 21.25 & 0.365 & 0.363 & 0.364 \\
+        & Inference & 21.250 & 0.365 & 0.363 & 0.364 \\
         \hline
@@
 \section*{Declaration of generative AI and AI-assisted technologies in the writing process.}
-During the preparation of this work the author(s) used ChatGPT in order to check grammar, spelling, and improve fluency.
-After using this tool/service, the author(s) reviewed and edited the content as needed and take(s) full responsibility for the content of the published article.
+During the preparation of this work the authors used ChatGPT in order to check grammar, spelling, and improve fluency.
+After using this tool/service, the authors reviewed and edited the content as needed and take full responsibility for the content of the published article.
 

### 2025-01-14 main.tex
Editing by Blok

@@
     Haozhou Wang \textsuperscript{b},
-    Wei Guo \textsuperscript{b}
-    \blfootnote{Corresponding author: zhangwenli@bjut.edu.cn}
+    Wei Guo \textsuperscript{b,*}
+    \blfootnote{Corresponding author: zhangwenli@bjut.edu.cn; guowei@g.ecc.u-tokyo.ac.jp }
     \blfootnote{Email addresses: zhengchao97201@163.com (Chao Zheng), Wangchenhuizi@emails.bjut.edu.cn (Chenhuizi Wang), pieter.blok@fieldphenomics.com (Pieter M.
@@
 Currently, these measurements are done by humans, making it costly, labor-intensive, and often inaccurate. 
-Advances in 3D reconstruction and point cloud analysis allow extraction of detailed for grapes, yet current methods struggle with instance segmentation on incomplete point clouds due to occlusion. 
-This study presents a novel deep-learning-based phenotyping pipeline designed specifically for 3D grape point cloud data.                                                         
+Advances in 3D reconstruction and point cloud analysis allow extraction of detailed traits for grapes, yet current methods struggle incomplete point clouds due to occlusion. 
+This study presents a novel deep-learning-based phenotyping pipeline designed specifically for 3D point cloud data.                                                         
 First, individual berries are segmented from the grape bunch using the SoftGroup deep learning network. 
@@
 Finally, morphological analyses are applied to extract berry radius and volumes. 
-Validation on a dataset of four fresh grape varieties yielded  $R^2$ values of 85.53\% for berry radius and 96.89\% for berry volume, respectively. 
-These results demonstrate the potential of the proposed method for rapid, practical acquisition of grape 3D phenotypic information in grape cultivation.
+Validation on a dataset of four fresh grape varieties yielded  $R^2$ values of 85.5\% for berry radius and 96.9\% for berry volume, respectively. 
+These results demonstrate the potential of the proposed method for rapid and practical extraction of 3D phenotypic traits in grape cultivation.
 \end{abstract}
@@
 \section{Introduction}
-Fresh grape is one of the most important agricultural products and economic crops. 
-Its global production scale and consumption is increasing year by year. 
+Fresh grape is one of the most important agricultural products and economic crops \citep{alston_grapes_2019, venkitasamy_grapes_2019}. 
+Its global production and consumption is increasing year by year. 
 To better guide planting strategy and monitoring growing status, several geometric parameters like counts, length, and volume at bunch level and berry level are commonly used in actual applications.
@@
 Among them, the number and the radius of the berries are the most important phenotypic parameters \citep{sneha_acrescale_2024}. 
-Traditional manual phenotyping of parameter measurements is labor-intensive and time-consuming, and often destructive. 
-To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic parameters based on computer vision has attracted extensive interest in recent years \citep{li_review_2020}.
-Several simple geometry parameters can be acquired from 2D images by using computer vision algorithms like pattern recognition, machine learning, and deep learning \citep{zabawa_counting_2020}. 
-Projecting the 3D world onto a 2D image plane inevitably results in information loss. 
+Traditional manual phenotyping of traits is labor-intensive and time-consuming, and often destructive. 
+To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic traits based on computer vision has attracted extensive interest in recent years \citep{li_review_2020}.
+Several simple geometry traits can be acquired from 2D images by using computer vision algorithms that use pattern recognition, machine learning, and deep learning \citep{zabawa_counting_2020}. 
+Projecting the 2D image plane onto the 3D world inevitably results in information loss. 
 The occlusion of berries often lead to incomplete representations of grape bunches. 
-Additionally, clustered berries and their shadows naturally create complex structures even under controlled lightning conditions. 
-Leaving difficulties for obtaining reliable measurements of phenotypic parameters through 2D image analysis \citep{fei_comprehensive_2022,xiang_multispace_2023}.
+Additionally, clustered berries and their shadows  create challenges for obtaining reliable measurements of phenotypic parameters through 2D image analysis, even under controlled lightning conditions  \citep{fei_comprehensive_2022,xiang_multispace_2023}.
 
@@
 These methods primarily rely on point cloud segmentation techniques, such as edge-based segmentation, region-growing segmentation, and sphere-fitting algorithms. 
-However, traditional point cloud processing algorithms are heavily dependent on prior knowledge of the target object and require extensive manual feature design and parameter tuning to achieve optimal results in specific conditions, limiting their broader applicability.
+Unfortunately, traditional point cloud processing algorithms heavily rely on prior knowledge of the target object and require extensive manual feature engineering and parameter tuning to achieve optimal results in a wide range of conditions, thereby limiting their generalization performance.
 
-On the other hand, deep learning approach uses a data-driven approach to learn features from point cloud data automatically. 
+State-of-the-art deep learning approaches use a data-driven feature learning from the point cloud data automatically. 
 It recently shows promising adaptability and accuracy in plant 3D phenotyping \citep{schneider_predicting_2020,scholer_automated_2015,rostami_survey_2019,du_pst_2023}.
@@
 \citet{li_psegnet_2022} proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. 
-Unlike previous studies focused on canopy level or individual plant level analysis, instance segmentation alone is insufficient on berry level analysis. 
-The aggregated cluster growth \citep{du_instance_2023} causes the berries to squeezed against each other, leading to interior occlusion and resulting in an incomplete point cloud of berry surfaces. 
+The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on berry level analysis. 
+The aggregated cluster growth \citep{du_instance_2023} causes the berries to squeezed against each other, leading to self occlusion and resulting in an incomplete point cloud of berry surfaces. 
 Therefore, point cloud instance segmentation can only capture partial information rather than that of whole berries.
 
-To address the issue of partial point clouds, point cloud shape completion is one of the most commonly employed solutions.
+To address the issue of partial point clouds, and consequently an underestimation of the berry traits, point cloud shape completion is one of the most commonly used solutions.
 Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
@@
 However, these methods are limited to specific fruit characteristics and require manual design of algorithms according to the features of the fruit, lacking the potential for generalized application.
-some researchers applied deep learning-based point cloud completion \citep{wang_unsupervised_2021}. 
-Utilizing deep learning methods, researchers have designed point cloud completion networks. 
+Utilizing deep learning methods, researchers have designed point cloud completion networks \citep{wang_unsupervised_2021}. 
 \citet{park_deepsdf_2019} introduced DeepSDF to achieve the completion of object point cloud models.
 It uses a learned continuous signed distance function to represent a class of shapes in latent space and is tolerant to noisy 3D input data.
-\citet{magistri_contrastive_2022} utilized a latent space of potential fruit appearances and propose an encoder-decoder network that converted a single RGB-D frame to a 3D shape of a complete fruit. 
-This network was extended and upgraded by \citet{blok_highthroughput_2025} for high-throughput 3D shape completion of potato tubers on a commercial harvester.
-\citet{tang_lakenet_2022} proposed a point cloud completion network Lake-net for furniture model point cloud datasets. 
-For grape berry application, the shape of the berry can roughly approach the deformation of a sphere or ellipsoid depending on the species, and its surface consists of multiple spherical surfaces of varying curvature, with a rich characterization of details.
-The existing datasets from other fruits cannot be applied directly, and manually creating paired training datasets is time-consuming and labor-intensive.
-Therefore, there is a demand to develop a network and pipeline, capable of completing the detailed surface of an incomplete berry point cloud while requiring less labor-intensive training data preparation.
+\citet{magistri_contrastive_2022} utilized DeepSDF and its latent space in an encoder-decoder network that converted a single RGB-D frame to a 3D shape of a complete fruit. 
+This encoder-decoder network was extended and optimized by \citet{blok_highthroughput_2025} for high-throughput 3D shape completion of potato tubers on a commercial harvester.
+Outside the agricultural domain, \citet{tang_lakenet_2022} proposed a point cloud completion network (Lake-net) for furniture model point cloud datasets.
+For grape berry application, the shape of the berry can be roughly approached by the deformation of a sphere or ellipsoid depending on the species. 
+Existing datasets from other fruits cannot be applied directly, and manually creating paired training datasets is time-consuming and labor-intensive.
+Therefore, there is a demand to develop an analysis pipeline, capable of completing the detailed surface of an incomplete berry point cloud while requiring less labor-intensive training data preparation.
 
-In this study, we proposed a berry-level 3D grape phenotyping pipeline that will overcome the occlusion issue. 
+In this study, we proposed a novel berry-level 3D grape phenotyping pipeline that will overcome the occlusion issues. 
 The proposed pipeline includes: 
@@
 (2) a point cloud completion module that complete the missing part of segmented berry point cloud data through automatic training data generation; 
-(3) a phenotyping module that extract berry phenotypic traits such as radius and volume. 
-And at the end, the pipeline has been tested on four different fresh grape species (Red, Green, Kyoho, and Shine Muscat Grape).
+(3) a phenotyping module that extract berry phenotypic traits including radius and volume. 
+The novelty of our study is the research of this novel pipeline and its evaluation on four different fresh grape species (Red, Green, Kyoho, and Shine Muscat Grape).
 
@@
 
-In this section, we first introduce the four experimental grape materials and the 3D reconstruction methods for obtaining 3D point cloud data. 
-We then provide a brief overview of the SoftGroup \citep{vu_softgroup_2022} deep learning network, which was trained on our previous point cloud dataset for instance segmentation of individual berries (Fig.~\ref{fig:raw1}a).
+In this section, we first introduce the plant material for our grape analysis, followed by the 3D reconstruction methods for obtaining 3D point cloud data. 
+We then provide a brief overview of the SoftGroup \citep{vu_softgroup_2022} deep learning network, which was trained on our point cloud dataset for instance segmentation of individual berries (Fig.~\ref{fig:raw1}a).
 Next, we detail the proposed self-supervised completion deep learning module, GrapeCPNet, which predicts the complete berry point cloud from segmented partial berries (Fig.~\ref{fig:raw1}b). 
@@
 
-\subsubsection{Grape species selection}
+\subsubsection{Grape species}
 
-To ensure the generality and applicability of the study, this paper considers the sparsity, shape, and color of the bunch, and chooses four common fresh grapes as the experimental materials, which are Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape.
+To ensure the generalization and broad application of our study, this paper considers the sparsity, shape, and color of the bunch, and chooses four common fresh grapes as the experimental materials, which are Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape.
 The characteristics of them are shown in Table~\ref{tbl:1} and the examples are shown in Figure~\ref{fig:raw86}.
@@
 Petersburg, Russia) was used to obtain the 3D point cloud of bunch (Fig.~\ref{fig:raw9}a) and single complete berry (Fig.~\ref{fig:raw9}b).
-Their correspondence of the same berry was also labelled as shown in Figure~\ref{fig:raw9}c
+Their correspondence of the same berry was also labeled as shown in Figure~\ref{fig:raw9}c.
 
@@
 
-For whole bunch multi-view images acquisition, the device was built as shown in Figure~\ref{fig:raw9}a. 
+For whole bunch multi-view images acquisition, the device was built as shown in Fig.~\ref{fig:raw9}a. 
 One grape bunch was hung on the hook which was attached to propellers driven by stepping motors (Fig.~\ref{fig:raw9}a1) that can achieve rotation at a certain speed. 
-The entire device was placed in front of a solid-colored backdrop (Fig.~\ref{fig:raw9}a2), and multiple cameras were set up to photograph the bunch from different height angles. 
+The entire device was placed in front of a solid-colored backdrop (Fig.~\ref{fig:raw9}a2), and multiple cameras were set up to photograph the bunch from different heights and view angles. 
 In addition, a ruler with markers were used for scale correction. 
-For single complete berry multi-view images acquisition in batch (Fig.~\ref{fig:raw9}b). 
-Nine berries were fixed floating by needle disk (Fig.~\ref{fig:raw9}b1) on a turntable device (Fig.~\ref{fig:raw9}b2). 
+For single complete berry multi-view images acquisition in batch (Fig.~\ref{fig:raw9}b), 
+nine berries were fixed floating by needle disk (Fig.~\ref{fig:raw9}b1) on a turntable (Fig.~\ref{fig:raw9}b2). 
 The background, cameras, and marker settings are similar to the previous bunch reconstruction. 
-The number of reconstructed images and the shooting parameters are selected, as shown in Table~\ref{tbl:2}. 
+The number of reconstructed images and the image acquisition parameters are selected, as shown in Table~\ref{tbl:2}. 
 Examples of the point cloud of bunch, multiple berries, and single complete berries from multiple berries are shown in Figure~\ref{fig:raw10}.
@@
     \centering
-    \caption{Comparison of the characteristics of the four species of fresh grape}
-    \begin{tabular}{cccc}
+    \caption{Image acquisition details for grape bunches and single berries}
+    \begin{tabular}{ccccc}
         \hline
-        \textbf{Object} & \textbf{Shooting distance} & \textbf{Shooting angle} & \textbf{Number of images} \\
+        \textbf{Object} & \textbf{Distance} & \textbf{Camera view angles} & \textbf{Rotation angles} &  \textbf{Total image \#} \\
         \hline
-        Bunch        & 25-60cm & $0^{\circ}$, $\pm 25^{\circ}$, $\pm 45^{\circ}$ & $5 \times 50$ \\
-        Single berry & 20-40cm & $-15^{\circ}$, $0^{\circ}$, $25^{\circ}$, $45^{\circ}$ & $4 \times 50$ \\
+        Bunch        & 25-60cm & $0^{\circ}$, $\pm 25^{\circ}$, $\pm 45^{\circ}$ & $7.2^{\circ}$ (50 images) & $250$ \\
+        Single berry & 20-40cm & $-15^{\circ}$, $0^{\circ}$, $25^{\circ}$, $45^{\circ}$ & $7.2^{\circ}$ (50 images) & $200$ \\
         \hline
@@
 
-In this paper, SoftGroup \citep{vu_softgroup_2022} was selected for bunch point cloud segmentation by comparing different current deep learning-based point cloud instance segmentation models. 
-SoftGroup contains two aspects of design: 
+In this paper, SoftGroup \citep{vu_softgroup_2022} was selected for bunch point cloud segmentation after comparing different deep learning-based point cloud instance segmentation models. 
+SoftGroup used a two step approach: 
 (1) the point-by-point prediction U-Net was used to capture the detailed geometric characteristics between points. 
 (2) a threshold score was used to judge the boundary of the point to avoid point category misclassification. 
-Therefore, it is suitable for use in a bunch where there is a tight connection boundary among the berries.
+Therefore, it is suitable for use in a bunch where there is a tight connection between the berries.
 
 In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was labeled at the instance-level (Fig.~\ref{fig:raw11}). 
-This paper collected and labeled 8 bunches for each of the four species (total 32 bunches). 
-In the sample division, 5 grape bunches of each species (total 20) are randomly selected and used as training samples, the remaining 12 bunches are used for validation.
+This paper collected and labeled eight bunches for each of the four species (in total 32 bunches). 
+Five grape bunches per grape specie (in total 20) were randomly selected and used as training samples. The remaining three bunches were used for validation.
 
@@
 The self-supervised training-based berry point cloud completion was used to predict their complete 3D model. 
-Self-supervised learning is a way of training a model without artificial annotations by using the data itself as truth value to supervise \citep{fei_selfsupervised_2023}. 
-This subsection introduced the self-supervised strategy to generating paired training data without manual annotation and the structure of grape completion network, GrapeCPNet. 
-The whole workflow of proposed GrapeCPNet is shown in Figure~\ref{fig:raw3}.
+Self-supervised learning is a way of training a model without annotations by clustering the data in unsupervised manners\citep{fei_selfsupervised_2023}. 
+The following section summarizes the self-supervised strategy for the paired training data. It is followed by a description of the grape completion network, GrapeCPNet (Figure~\ref{fig:raw3}).
 
@@
     \caption{Flowchart of the self-supervised berry point cloud completion, including model training and model inferencing (application) phases.
-In the training phase, the paired incomplete training data was generated from the complete single berry point cloud, then train GrapeCPNet using self-supervised methods without manual annotation.
-In the application phase, the incomplete berry point cloud is input into the trained model to obtain a complete prediction berry.}
+In the training phase, the paired incomplete training data was generated from the complete single berry point cloud, then GrapeCPNet was trained using self-supervised methods without manual annotation.
+In the application phase, the incomplete berry point cloud is input to the trained model to obtain a complete prediction berry.}
     \label{fig:raw3}
@@
 
-The point cloud completion network often requires the incomplete-complete data pairs of the same object to build a mapping relationship. 
+Supervised point cloud completion training requires the incomplete-complete data pairs of the same object to build a mapping relationship. 
 In this paper, the complete grapes were obtained by single berry reconstruction (Section~\ref{sec:212}) and were used as ground truth, while the incomplete grapes were cut from the complete grapes following characteristic of occlusion and were used as training inputs.
-This data pair generation strategy saved huge amounts of data annotation. The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
-Based on the incomplete characteristics, we developed a cutting method for the complete berry point cloud to generate the incomplete berry point cloud.
+This data pair generation strategy alleviated the data annotation efforts. The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
+Based on the incomplete characteristics, we developed a selection method to generate the incomplete berry point cloud from the complete berry point cloud .
 
@@
 
-This proposed algorithm is shown in Algorithm \ref{alg:1}. 
-The inputs include a single complete berry point cloud and the maximum number of cutting area (5 in this paper). 
-The output is the cut incomplete berry point clouds. First, the single complete berry point cloud was normalized and centralized (Fig.~\ref{fig:raw12}a). 
-Second, randomly pick the integer number of cuts lower than maximum number, in this paper ranging from 1 to 5. 
-Then, for each loop of cutting, a 3D sphere model was generated in the space to collide with the berry point cloud, and the collision portion was removed to complete the cutting operation. 
-The maximum of center and radius parameters of 3D sphere model were manually set according to berry size. 
-In this paper we set maximum 0.75 for center offsets and maximum 0.25 for radius. 
-Continue the previous cut looping until meet the cut limits. The cut incomplete berry of each loop was all saved as training data (Fig.~\ref{fig:raw12}b).
+The pseudo-code of our proposed algorithm is shown in Algorithm \ref{alg:1}. 
+The inputs include a single complete berry point cloud and the maximum number of selection areas (5 in this paper). 
+The output is a selected incomplete berry point cloud. First, the single complete berry point cloud was normalized and centralized (Fig.~\ref{fig:raw12}a). 
+Second, randomly select the number of cuts, with a maximum of five cuts as specified in this paper. 
+Then, for each loop of selection, a 3D sphere model was generated in the space to collide with the berry point cloud, and the collision portion was removed to complete the operation. 
+The maximum center and radius parameters of the 3D sphere model were manually set according to the berry size. 
+In this paper we set a maximum of 0.75 for the center offsets and 0.25 for the radius offsets. 
+Continue the previous selection looping until the limits are met. The selected incomplete point cloud was saved from each loop as training data (Fig.~\ref{fig:raw12}b).
 
@@
 \begin{algorithm}
-    \caption{The cutting method for generating training data of incomplete berries}
+    \caption{The selection method for generating training data of incomplete berries}
     \label{alg:1}
@@
 
-    $\hat{P}_C \gets \text{Normalize}(\text{Translate}(P_C))$ \tcp{center to $(0,0,0)$, range to $[-0.5, 0.5]$}
+    $\hat{P}_C \gets \text{Normalize}(\text{Translate}(P_C))$ \tcp{center to $(0,0,0)$, range to $[-0.5m, 0.5m]$}
     \For{$i = 0 \to n$}{
-        set $m = \text{random}\{1,2,3,4,5\}$ \tcp{cut incomplete single berry $m$ times}
+        set $m = \text{random}\{1,2,3,4,5\}$ \tcp{select incomplete single berry $m$ times}
         $P_{o_i} \gets copy(\hat{P}_C)$ \tcp{initialize one output}
@@
             set $R = \text{random}[0.25, 0.75]$ \tcp{radius}
-            set $M_S \gets \text{sphere}(O, R)$ \tcp{genreate sphere cut model}
-            $P_{o_i} = P_{o_i} - P_{o_i} \cap M_S$ \tcp{remove overlap with cut shpere model}
+            set $M_S \gets \text{sphere}(O, R)$ \tcp{generate sphere model}
+            $P_{o_i} = P_{o_i} - P_{o_i} \cap M_S$ \tcp{remove overlap with sphere model}
         }
@@
 
-For model training, 36 complete berry are collected for each of the four species of grape (in total 144). 
+For model training, 36 complete berry were collected for each of the four species of grape (in total 144). 
 To further expand the data quantity, based on the single complete berry point cloud obtained by reconstruction, this paper uses the PointFlow \citep{yang_pointflow_2019}, a point cloud generation model to generate the simulated samples (Fig.~\ref{fig:raw12}c).
@@
 Each complete berry point cloud has 5 incomplete berry point clouds corresponding to it, and a total of 3220 training data pairs are obtained. 
-For the training and testing of the model, this paper divides the dataset according to a ratio close to 7:3, with a total of 450 complete berry point clouds (2250 training data pairs) to train the network and 194 complete berry point clouds (970 testing data pairs) to test.
+For the training and testing of the model, this paper divides the dataset according to a ratio close to 70-30\%, with a total of 450 complete berry point clouds (2250 training data pairs) to train the network and 194 complete berry point clouds (970 testing data pairs) to test.
 
-For the model inference validation, among 12 testing grape bunches of the berry instance segmentation model (Section~\ref{sec:22}), each grape species was randomly selected one bunch (total 4 bunches).
-For each bunch, 27 berries are randomly selected, and finally obtain a total of 108 incomplete berries as the input data for completion network inference validation. 
-By checking the labels of these berries, the corresponding single complete berry reconstruction results (Section~\ref{sec:212} \& Fig.~\ref{fig:raw9}c) were used as ground truth.
+For the model inference validation, from the 12 testing grape bunches of the berry instance,  one bunch was randomly selected per grape specie (in total 4 bunches), refer to (Section~\ref{sec:22}). 
+For each bunch, 27 berries were randomly selected, yielding a total of 108 incomplete berries for testing the completion network inference validation. 
+The labels of these berries (Section~\ref{sec:212} \& Fig.~\ref{fig:raw9}c), were used as ground truth.
 
-\subsubsection{GrapeCPNet structure}
+\subsubsection{GrapeCPNet}
 
@@
 
-{\raggedright\textbf{(1) Centroid-based berry contour completion}}
+{\raggedright\textbf{(a) Centroid-based berry contour completion}}
 
@@
 
-Finally, since the $\varphi = \{ \varphi(p_i) \mid i=1, \cdots, M \}$ contains the relative position information of each point, it can be used as the position embedding and the serialized feature $F = \{F_i \mid i=1, \cdots, M \}$ was fed into the geometrically-aware Transformer \citep{vaswani_attention_2017} based encoder.
+{\raggedright\textbf{(b) Transformer network}}
+
+Since the $\varphi = \{ \varphi(p_i) \mid i=1, \cdots, M \}$ contains the relative position information of each point, it can be used as the position embedding and the serialized feature $F = \{F_i \mid i=1, \cdots, M \}$ was fed into the geometrically-aware Transformer \citep{vaswani_attention_2017} based encoder.
 The process is Equation~(\ref{eq:3}).
@@
 
-{\raggedright\textbf{(2) Snowflake diffusion-based berry surface completion}}
+{\raggedright\textbf{(c) Snowflake diffusion-based berry surface completion}}
 
-The results of the contour completion can determine the overall 3D morphology, however, the density of this sparse point cloud requires the model can capture the detail surface geometry changes between points to avoid distortion.
-Therefore, this paper utilizes the snowflake diffusion-based generation idea to regard each point in the contour completion as the center point of the local region. 
-It diffuses based on the centroid points and generates further at the generated location, densification by point-to-point splitting. 
+The results of the contour completion can determine the overall 3D morphology, however, the density of this sparse point cloud requires the model to capture the detailed surface geometry changes between the points to prevent distortion.
+Therefore, this paper utilizes the snowflake diffusion-based generation method to regard each point in the contour completion as the center point of the local region. 
+Its diffusion is based on the centroid points and generates further at the generated location, densification by point-to-point splitting. 
 Specifically, as follows:
@@
 
-Through the above two steps, the complete 3D point cloud model of the berry can be obtained after contour completion and surface completion of GrapeCPNet.
+Through the above steps, the complete 3D point cloud model of the berry can be obtained after contour completion and surface completion of GrapeCPNet.
 
@@
 
-In order to validate the accuracy of extracted morphological traits, those 12 validation bunches in Section~\ref{sec:22} were continuously used after instance berry segmentation and berry completion. 
-The radius and volume of the 108 samples are calculated. 
-For ground truth measurement, instead of using manual measurement, which has multiple artificial errors in obtaining the true values of actual radius and volume. 
-This paper used the correspond individual complete berry as the ground truth and applied the same method for the radius and volume calculations.
+To validate the accuracy of extracted morphological traits, the 12 validation bunches  were used after instance berry segmentation and berry completion (refer to Section~\ref{sec:22}). 
+The radius and volume of the 108 samples were calculated. 
+For ground truth measurement, we used the values of the radius and volume of the individual complete berry from the completed point clouds.
 
@@
 
-In this paper, the evaluation metrics for the bunch segmentation, the berry completion, the effectiveness of the number of berries counting, and the calculation of radius and volume in the acquisition of 3D phenotypic parameters are as follows.
+In this paper, the metrics for the bunch segmentation, berry completion, berry counting, and the radius and volume calculation were used for evaluating the performance of our analysis pipeline.
 
@@
 \label{sec:251}
-In this paper, we use the format of SoftGroup \citep{vu_softgroup_2022} that is consistent with the S3DIS dataset \citep{armeni_3d_2016} and use the average precision AP \citep{vu_softgroup_2022} as the evaluation metric for berry instance segmentation.
-In the threshold setting, the average of the APs with selected the IoU (Intersection over Union) from 50\% to 95\% in steps of 5\% is noted as AP@50:5:95.
+In this paper, we used average precision AP as the evaluation metric for berry instance segmentation (similar to the original paper of \citep{vu_softgroup_2022}).
+The average APs with IoU (Intersection over Union) ranging from 50\% to 95\% in steps of 5\% were used and noted as AP@50:5:95.
 
@@
 
-In this paper, we use the format of PoinTr \citep{yu_pointr_2021} that is consistent with the PCN dataset \citep{yuan_pcn_2018} and use the chamfer distance (CD-distance) and F-Score to measure the effect of berry completion.
-For each sample, the chamfer distance $d_CD$ between the predicted point set $P$ and the true point set $G$ is calculated as shown in Equation~(\ref{eq:8})
+In this paper, we use the chamfer distance (CD-distance) and F-Score to measure the effect of berry completion (similar to the original paper of \citep{yu_pointr_2021}). 
+For each sample, the chamfer distance $d_{CD}$ between the predicted point set $P$ and the true point set $G$ was calculated as shown in Equation~(\ref{eq:8})
 
@@
 It can be seen that the chamfer distance represents the sum of the average closest distance from the point in $P$ to the point in $G$ and the average closest distance from the point in $G$ to the point in $P$.
-Where the L1 norm is used to calculate the closest distance between two points.}
+Where the L1 norm was used to calculate the closest distance between two points.}
 
-In addition, F-Score measures the similarity between $P$ and $G$ by the harmonic mean between Precision and Recall. 
-On the one hand, Precision counts the percentage of the number of points of the prediction within a certain distance from the truth point, which represents the accuracy of the prediction;
-on the other hand, Recall counts the percentage of the number of points of the truth point within a certain distance from the prediction point, which represents the completeness of the prediction.
-Specifically, as follows.
+The F-Score measured the similarity between $P$ and $G$ by the harmonic mean between Precision and Recall (Eq.~\ref{eq:9}). 
+Precision (Eq.~\ref{eq:10}) is the percentage of predicted points within a certain distance from the truth point, i.e.
+the accuracy of the prediction.
+Recall (Eq.~\ref{eq:11}) is the percentage of ground truth points within a certain distance from the predicted point, i.e.
+the completeness of the prediction.
 
-\begin{align}
-    \text{Precision}(d) &= \frac{1}{|P|} \sum_{p \in P} \left[ \min_{g \in G} \|p - g\| < d \right] \tag{9}\\
-    \text{Recall}(d) &= \frac{1}{|G|} \sum_{g \in G} \left[ \min_{p \in P} \|g - p\| < d \right] \tag{10}\\
-    F\text{-Score}(d) &= \frac{2 \times \text{Precision}(d) \times \text{Recall}(d)}{\text{Precision}(d) + \text{Recall}(d)} \tag{11}
-\end{align}
+\begin{equation}
+    F\text{-Score}(d) = \frac{2 \times \text{Precision}(d) \times \text{Recall}(d)}{\text{Precision}(d) + \text{Recall}(d)} 
+\label{eq:9}
+\end{equation}
 
-{\raggedright where, Precision$(d)$ and Recall$(d)$ in (11) denote the Precision and Recall computed under the distance threshold $d$, respectively, and $d$ is set to $0.01$ in the PCN data format. 
-From the above Equation, the higher the F-Score indicates that the two point sets are more similar.}
+\begin{equation}
+    \text{Precision}(d) = \frac{1}{|P|} \sum_{p \in P} \left[ \min_{g \in G} \|p - g\| < d \right]\\
+\label{eq:10}
+\end{equation}
 
-In addition, in order to verify the efficiency of GrapeCPNet, other classical point cloud completion networks, including PoinTr, SnowFlakeNet, TopNet \citep{tchapmi_topnet_2019}, and GRNet \citep{xie_grnet_2020} are selected as comparison algorithms.
+\begin{equation}
+    \text{Recall}(d) = \frac{1}{|G|} \sum_{g \in G} \left[ \min_{p \in P} \|g - p\| < d \right]
+\label{eq:11}
+\end{equation}
+
+{\raggedright The distance threshold $d$ was set to $0.01m$. Given that the point cloud was initially normalized to the range $[-0.5m, 0.5m]$. 
+From the above Equation, the higher the F-Score the better the match between the two point sets.}
+
+To verify the efficiency of GrapeCPNet, we compared it to other point cloud completion networks: PoinTr, SnowFlakeNet, TopNet \citep{tchapmi_topnet_2019}, and GRNet \citep{xie_grnet_2020}.
 
@@
 \label{sec:253}
-In order to evaluate the efficiency of the number of berry statistics and the calculation of berry radius and volume, the MAE (Mean Absolute Error) and the coefficient of determination $R^2$ (R-Square) are used to calculate the error between the prediction value and the true value of the sample.
+To evaluate the efficiency of the number of berry statistics and the calculation of berry radius and volume, the MAE (Mean Absolute Error) and the coefficient of determination $R^2$ (R-Square) are used to calculate the error between the prediction value and the true value of the sample.
 
@@
     \text{MAE} &= \frac{1}{m} \sum_{i=1}^{m} |y_i - \hat{y}_i| \tag{12}\\
-    R^2 &= 1 - \frac{\sum_{i} (\hat{y}_i - y_i)^2}{\sum_{i} (\bar{y}_i - y_i)^2} \tag{13}
+    R^2 &= 1 - \frac{\sum_{i=1}^{m} (\hat{y}_i - y_i)^2}{\sum_{i=1}^{m} (\bar{y}_i - y_i)^2} \tag{13}
 \end{align}
@@
 {\raggedright where, $m$ is the number of samples, $y_i$ is the true value of the $i^{\text{th}}$ sample, $\hat{y}_i$ is the prediction value, and $\bar{y}_i$ represents the mean of all true values. 
-It can be seen that the lower the MAE, the closer the prediction value is to the true value, and the value of $R^2$ ranges from 0 to 1, and the closer it is to 1 means that the prediction value is better fitted.}
+The lower the MAE, the closer the prediction value is to the true value. The values of $R^2$ range between 0 and 1, and the closer it is to 1 means the better the fit with the predicted values.}
 
@@
 
-In order to validate the efficiency of the method proposed in this paper, the experiments are conducted on each component separately, including the result of bunch point cloud segmentation, the result of berry point cloud completion based on self-supervised training, and the result of phenotypic parameters acquisition.
+To validate the efficiency of our method, the experiments were conducted on each component separately, including the result of bunch point cloud segmentation, the result of berry point cloud completion based on self-supervised training, and the result of obtaining the phenotypic traits.
 
@@
 
-Bunch point cloud segmentation is mainly realized based on SoftGroup, a point cloud segmentation network. 
-This paper calculates the segmentation results for the berry instances and stem instances using the dataset introduced in Section~\ref{sec:22} and the evaluation metrics in Section~\ref{sec:251}, as shown in Table~\ref{tbl:3}.
+The bunch point cloud segmentation results are summarized in Table~\ref{tbl:3}.
 
@@
 As can be seen from Table~\ref{tbl:3}, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.
-The visualization results of four fresh grapes for bunch point cloud segmentation using SoftGroup are shown in Figure~\ref{fig:raw13}.
+The results of four fresh grapes for bunch point cloud segmentation are visualized in Fig.~\ref{fig:raw13}.
 
@@
 
-The berry point cloud completion experiments are divided into two parts according to the different phases of the network: the results of the self-supervised training experiments and the results of the practical application experiments.
+The berry point cloud completion experiments are divided into two parts according to the different phases of the network: the results of the self-supervised training and the results of the practical application.
 
-(1) In the training phase, the incomplete-complete pair of the point cloud of berry is obtained by the cutting method to train the network. 
-The samples are divided into the training set and the testing set.
-Therefore, in order to verify the efficiency of berry point cloud completion in the training phase, experiments are conducted as ``Test''.
-
-(2) In the application phase, the incomplete berries segmented from the bunch are complemented based on the trained berry point cloud completion model. 
-Therefore, in order to verify the efficiency of berry point cloud completion in practical applications, experiments are conducted as ``Inference''.
-
-Meanwhile, since the point cloud obtained after berry picking is used as the ground truth, the point cloud alignment is performed to calculate evaluation metrics of the predicted complete berry point cloud with the ground truth.
-The experimental results of comparing to other point cloud completion algorithms are shown in Table~\ref{tbl:4}. 
-GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the other comparative algorithms. 
-The visualization of using GrapeCPNet to complement the incomplete berry segmented from the bunch in the application phase is shown in Figure~\ref{fig:raw14}.
+The experimental results of GrapeCPNet compared to other point cloud completion algorithms are shown in Table~\ref{tbl:4}. 
+GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the comparative algorithms.
+Fig.~\ref{fig:raw14} visualizes the shape completion result of GrapeCPNet on the incomplete berry segmented from the bunch in the application phase.
 
@@
     \centering
-    \caption{Experimental results of different completion networks based on self-supervised training for berry point cloud}
+    \caption{Experimental results of different completion networks based on self-supervised training for berry point cloud. Best performing results are visualized in bold.}
     \begin{tabular}{cccccc}
         \hline
-        \textbf{Model} & \textbf{DataSet} & \textbf{CD-distance $\downarrow$} & \textbf{Precision $\uparrow$} & \textbf{Recall $\uparrow$} & \textbf{F-score $\uparrow$} \\
+        \textbf{Model} & \textbf{DataSet} & \textbf{$d_{CD}$ $\downarrow$} & \textbf{Precision $\uparrow$} & \textbf{Recall $\uparrow$} & \textbf{F-score $\uparrow$} \\
         \hline
@@
         \hline
-        \multirow{2}{*}{GrapeCPNet (\textbf{Ours})} & Test & \textbf{8.315} & \textbf{0.729} & \textbf{0.772} & \textbf{0.751} \\
+        \multirow{2}{*}{GrapeCPNet (Ours)} & Test & \textbf{8.315} & \textbf{0.729} & \textbf{0.772} & \textbf{0.751} \\
         \cline{2-6}
@@
     \includegraphics[width=1\textwidth]{figures/Figure12.pdf}
-    \caption{Example of four fresh grape berry point cloud completion results: in each block, the left side shows the incomplete berry point cloud obtained from the segmentation of the bunch, and the right side shows the completion results using GrapeCPNet under the self-supervised training-based method.}
+    \caption{Example of four fresh grape berry point cloud completion results: in subfigures a-d, the left side shows the incomplete berry point cloud obtained from the segmentation of the bunch, and the right side shows the completion results using GrapeCPNet under the self-supervised training-based method.}
     \label{fig:raw14}
@@
 
-In addition, the results of the ``Inference'' experiments are worse than those of the ``Test'' experiments for two main reasons.
-First, there are differences between the dataset of the training phase and the application phase of self-supervised training, resulting in a loss of accuracy in the application of the model. 
-In addition, when evaluating the actual application efficiency of the model, the true value of the reconstructed complete point cloud of a single berry and the prediction value of the complemented point cloud suffer from the loss of accuracy when they are aligned.
-Through the above results, the experiments of berry point cloud completion based on self-supervised training reflected the efficacy of GrapeCPNet, meanwhile, this paper further validated the efficacy of the 3D phenotypic parameters acquisition of grape by the proposed method.
+The results of the ``Inference'' experiments are worse than those of the ``Test'' experiments for two main reasons.
+First, there are differences between the dataset of the training phase and the application phase of self-supervised training, resulting in a drop in the accuracy. 
+In addition, when evaluating the actual application efficiency of the model, the true value of the reconstructed complete point cloud of a single berry and the prediction value of the complemented point cloud suffer from the drop in the accuracy after aligning them.
+Through the above results, the experiments of berry point cloud completion based on self-supervised training reflected the efficacy of GrapeCPNet, meanwhile, this paper further validated the efficacy of the 3D phenotypic traits of grape by the proposed method.
 
@@
 
-Based on the method in this paper, the bunch point cloud is used as input, and the acquired 3D phenotypic parameters are the final output, which mainly contains two parts: the bunch-level phenotypic parameters and the berry-level phenotypic parameters.
-In this paper, experiments are conducted to calculate berry radius and volume with the dataset in the evaluation metrics in Section~\ref{sec:253}.
-The radius parameters are calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure~\ref{fig:raw16}.
+The radius parameters were calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure~\ref{fig:raw16}.
 
@@
 \end{figure}
-
-Three lengths of the radius of the berry can be obtained by fitting the predicted point cloud of the complete berry shell to the surface of an ellipsoid. 
-Meanwhile, the point cloud data acquisition method in Section~\ref{sec:212} can translate the scale of the point cloud space to the real world, so as to get the real radius length of the berry.
-Because of the large difference between the ratio of the long and short axis of different species, this paper conducted experiments on the calculation of the axis length of four species respectively, as shown in Figure~\ref{fig:raw17}.
 
@@
 
-As shown in Figure~\ref{fig:raw17}, each point on the subplot block represents a berry sample, the horizontal coordinate indicates the true value of the axis length, the vertical coordinate indicates the prediction value, and the $R^2$ and MAE are displayed in the figure at the same time.
-From the results, it can be seen that the proposed method achieves an average $R^2$ of 0.86 for the three axis lengths of the four species of grape. 
-The analysis based on different perspectives is as follows.
+From Fig.~\ref{fig:raw17}, it can be seen that the proposed method achieves an average $R^2$ of 0.86 for the three axis lengths of the four species of grape. 
+This result can be dissected as follows:
 
-(1) The different species: Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape axis lengths predicted to reach an average $R^2$ of 0.86, 0.84, 0.89, and 0.84, respectively. 
-Among them, Kyoho Grape achieves the best results due to its berries with spherical shapes that are not too densely clustered and the lower difficulty in berry completion and morphology fitting. 
+(1) The different species: Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape axis length prediction reached an average $R^2$ of 0.86, 0.84, 0.89, and 0.84, respectively. 
+Among them, Kyoho Grape achieved the best results due to its spherical berries that are not too densely clustered and the lower difficulty in berry completion and morphology fitting. 
 Secondly, Red Grape and Green Grape both present a typical ellipsoid shape, but the latter is less precise than the former due to its greater ratio of long axis to short axis, which provides a more complex presentation.
-In addition, Shine-Muscat Grape has the lowest precision, which is due to the fact that its berry grows tightly and squeeze each other heavily, and the completion and fitting suffer from a loss of precision.
+Shine-Muscat Grape had the lowest precision, which was due to the fact that its berry grows tightly and occlude each other heavily, making it harder to accurately complete its shape.
 
-(2) The different axis: the average $R^2$ of the four species of grape are 0.89, 0.83, and 0.84 for the long, middle, and short axis, respectively. 
-It can be seen that the prediction accuracy of the long axis is significantly higher than that of the others, in which the $R^2$ of Red Grape and Kyoho Grape reach 0.90 and 0.92, respectively, realizing a high accuracy.
-This is due to the fact that in berry completion and fitting, the long axis is the easiest to determine, with less fitting error compared to the other two axes.
+(2) The different axis: the average $R^2$ of the four species of grape were 0.89, 0.83, and 0.84 for the long, middle, and short axis, respectively. 
+It can be noted that the prediction accuracy of the long axis was significantly higher than that of the others, in which the $R^2$ of Red Grape and Kyoho Grape reached 0.90 and 0.92, respectively, achieving a high accuracy.
+This was due to the fact that in berry completion and fitting, the long axis is the easiest to determine, with less fitting errors compared to the other two axes.
 
-The experimental results show that the proposed method has achieved high accuracy in the calculation of the radius of different grape species. 
-In addition, based on the radius prediction results, the volume of all 108 berry samples is calculated in this paper, and the experimental results are shown in Figure~\ref{fig:raw18}.
+The experimental results showed that the proposed method achieved high accuracy in the calculation of the radius of different grape species. 
+In addition, based on the radius prediction results, the volume of all 108 berry samples was calculated in this paper, and the experimental results are shown in Figure~\ref{fig:raw18}.
 
@@
 
-From the experimental results, it can be seen that the proposed method in the four species of berry volume phenotypic parameter calculation, $R^2$ reached 0.97, MAE is 0.3842 $cm^3$, with high precision, fully guarantee the accuracy of the prediction of the volume of different species.
+For the berry volume calculation of the four species, the $R^2$ was 0.97, and the MAE was 0.3842 $cm^3$. Indicating a high precision for predicting the volume of the different species.
 
@@
 
-In this paper, a method for the automatic acquisition of 3D phenotypic parameters of grape is designed to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end in the current work.
-Based on the point cloud of a bunch, the combination of deep learning point cloud processing algorithms realizes the counting of the number of berries, the calculation of berry radius, and berry volume.
-Moreover, to address the problem of incomplete surface of berry point cloud caused by occlusion, GrapeCPNet, a berry point cloud completion model based on the self-supervised training method, is designed to provide effective analytical data for berry-level phenotypic analysis.
+In this paper, a method for the automatic acquisition of 3D phenotypic traits of grape was presented to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end analysis.
+Based on the point cloud of a grape bunch, a combination of deep learning point cloud processing algorithms realized the counting of the number of berries, the calculation of berry radius, and berry volume.
+Moreover, to address the problem of incomplete point clouds of berries due to occlusion, we introduced GrapeCPNet, a berry point cloud completion model based on the self-supervised training method.
 
-At the same time, we found that GrapeCPNet is not effective in the case of complex berry appearance, such as drop-shaped. 
+As discussion point, we found that GrapeCPNet was not effective in the case of complex berry appearance, such as drop-shaped. 
 We have found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
 We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion. 
-In addition, the noise of data is also related to the effectiveness of the method proposed in this paper. 
-How to implement the method in practical application scenarios, such as RGB-D collected point cloud data, is another issue to be considered in the future.
+In addition, the noise in the data is also related to the effectiveness of the method proposed in this paper. 
+How to implement the method in practical application scenarios, such as RGB-D collected point cloud data, is another issue to be considered in future research.
 
-Through the method proposed in this paper, the automated acquisition of 3D phenotypic parameters of grape can be realized, which is of great significance in the field of agricultural production and scientific research.
+Through the method proposed in this paper, the automated acquisition of 3D phenotypic traits of grape can be realized, which is of great significance in the field of agricultural production and scientific research.
 First, there are large differences in berry morphology among different species of grape, and accurate reconstruction and analysis at the berry-level can help researchers analyze character differences more accurately.
-This plays an important role in breed improvement, cultivation management, and yield prediction. 
-Secondly, the point cloud data analysis technology based on 3D reconstruction has a wide application prospect in the growth environment of field crops. 
+This plays an important role in plant breeding, cultivation management, and yield prediction. 
+Secondly, the point cloud data analysis technology based on 3D reconstruction has a wide application of field crop analysis. 
 Through the designed data acquisition method and related technologies, combined with the actual field crop growing environment, the growth process can be monitored and analyzed in real-time. 
-Further, it can understand the phenotypic change law of crops under a natural growing environment better, provide a scientific basis for agricultural production, and optimize the production process and quality control.
+Further, it can help understanding the phenotypic change of crops in natural growing environments, providing better and objective measures for crop production and quality control.
 
@@
 \section*{Funding}
-This study was partially supported by the National Natural Science Foundation of China (NSFC) Program 62276009 and the Japan Science and Technology Agency (JST) AIP Acceleration Research JPMJCR21U3.
+This study was partially supported by the National Natural Science Foundation of China (NSFC) Program 62276009 and the Japan Science and Technology Agency (JST) AIP Acceleration Research JPMJCR21U3, the Hokkaido Sarabetsu Village “Endowed Chair for Field Phenomics” project.
 
-\section*{Acknowledgements}
-We would like to thank ...
+% \section*{Acknowledgements}
+% We would like to thank ...
 

### 2025-02-13 main.tex
Updates from Overleaf
title, highlights, rm refs

@@
 \usepackage{natbib}
+
+% final or draft
+\usepackage[draft]{changes}
 
@@
 % Title
-\title{GrapeCPNet: A deep learning integration for grape completion and phenotyping in 3D}
+% \title{GrapeCPNet: A deep learning integration for grape completion and phenotyping in 3D}
+\title{\added{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}}
 \author{
@@
 
+\textbf{\added{Highlights}}
+
+\begin{itemize}
+%   \item Novel deep learning pipeline for automated 3D grape phenotyping.
+%   \item GrapeCPNet: Self-supervised network for berry points cloud completion.
+%   \item High accuracy in berry instance segmentation (99.5\% average precision).
+%   \item Robust performance across four grape varieties ($R^2$ of 0.855 for radius, 0.969 for 
+% volume).
+%   \item Nondestructive and highthroughput analysis for viticulture applications.
+  \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
+  \item \added{GrapeCPNet is trained using self-supervision, free of manual annotations.}
+  \item \added{Integrated into a deep learning pipeline for automated 3D grape bunch phenotyping.}
+  \item \added{Achieved over 0.85 $R^2$ and 99.5\% average precision on four grape varieties.}
+\end{itemize}
+
 \begin{abstract}
@@
 \section{Introduction}
-Fresh grape is one of the most important agricultural products and economic crops \citep{alston_grapes_2019, venkitasamy_grapes_2019}. 
+Fresh grape is one of the most important agricultural products and economic crops \citep{alston_grapes_2019}. 
 Its global production and consumption is increasing year by year. 
 To better guide planting strategy and monitoring growing status, several geometric parameters like counts, length, and volume at bunch level and berry level are commonly used in actual applications.
-\citep{luo_prediction_2024,raihen_prediction_2024,kamangir_largescale_2024,barbole_comparative_2023}.
+\citep{luo_prediction_2024,raihen_prediction_2024}.
 Among them, the number and the radius of the berries are the most important phenotypic parameters \citep{sneha_acrescale_2024}. 
 Traditional manual phenotyping of traits is labor-intensive and time-consuming, and often destructive. 
-To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic traits based on computer vision has attracted extensive interest in recent years \citep{li_review_2020}.
+To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic traits based on computer vision has attracted extensive interest in recent years. 
 Several simple geometry traits can be acquired from 2D images by using computer vision algorithms that use pattern recognition, machine learning, and deep learning \citep{zabawa_counting_2020}. 
@@
 Unfortunately, traditional point cloud processing algorithms heavily rely on prior knowledge of the target object and require extensive manual feature engineering and parameter tuning to achieve optimal results in a wide range of conditions, thereby limiting their generalization performance.
+\added{Implementing} state-of-the-art deep learning approaches\replaced{, which automatically learn features}{use a data-driven feature learning} from the point cloud data \replaced{, can  reduce the workload of designing robust algorithms for complex and diverse conditions}{ automatically}.
+\deleted{It recently shows promising adaptability and accuracy in plant 3D phenotyping (schneider\_predicting\_2020, scholer\_automated\_2015). }
+\deleted{Focusing on point cloud segmentation applications, }
+\deleted{li\_maspc\_2022 proposed MASPC\_Transform to segment the stems and leaves of rose bush point cloud data to obtain 3D phenotypic parameters. }
+\deleted{wang\_3d\_2022 realized leaf instance segmentation by designing the PartNet for lettuce point cloud data. }
+\deleted{li\_psegnet\_2022 proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. }
+\replaced{However, few studies have reported deep learning networks perform well in}{The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on} berry level analysis.
 
-State-of-the-art deep learning approaches use a data-driven feature learning from the point cloud data automatically. 
-It recently shows promising adaptability and accuracy in plant 3D phenotyping \citep{schneider_predicting_2020,scholer_automated_2015,rostami_survey_2019,du_pst_2023}.
-Focusing on point cloud segmentation applications,
-\citet{li_maspc_2022} proposed MASPC\_Transform to segment the stems and leaves of rose bush point cloud data to obtain 3D phenotypic parameters. 
-\citet{wang_3d_2022} realized leaf instance segmentation by designing the PartNet for lettuce point cloud data. 
-\citet{li_psegnet_2022} proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. 
-The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on berry level analysis. 
-The aggregated cluster growth \citep{du_instance_2023} causes the berries to squeezed against each other, leading to self occlusion and resulting in an incomplete point cloud of berry surfaces. 
+\added{Another challenge after the success of instance berry segmentation is the incomplete representation of berry surfaces.} 
+The aggregated cluster growth causes the berries to squeezed against each other, leading to self occlusion and resulting in an incomplete point cloud of berry surfaces \citep{du_instance_2023}. 
 Therefore, point cloud instance segmentation can only capture partial information rather than that of whole berries.
-
-To address the issue of partial point clouds, and consequently an underestimation of the berry traits, point cloud shape completion is one of the most commonly used solutions.
+To address \replaced{this issue}{the issue of partial point clouds,} and consequently an underestimation of the berry traits, point cloud shape completion is one of the most commonly used solutions.
 Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
@@
 (3) a phenotyping module that extract berry phenotypic traits including radius and volume. 
-The novelty of our study is the research of this novel pipeline and its evaluation on four different fresh grape species (Red, Green, Kyoho, and Shine Muscat Grape).
+\replaced{The proposed pipeline was evaluated}{The novelty of our study is the research of this novel pipeline and its evaluation} on four different fresh grape species (Red, Green, Kyoho, and Shine Muscat Grape).
 
@@
 
-\subsection{Berry Instance Segmentation}
+\subsection{Berry Instance Segmentation \added{Module}}
 \label{sec:22}
@@
 
-\subsection{Self-Supervised Point Cloud Completion}
+\subsection{Self-Supervised Point Cloud Completion \added{Module}}
 
 The self-supervised training-based berry point cloud completion was used to predict their complete 3D model. 
-Self-supervised learning is a way of training a model without annotations by clustering the data in unsupervised manners\citep{fei_selfsupervised_2023}. 
+Self-supervised learning is a way of training a model without annotations by clustering the data in unsupervised manners. 
 The following section summarizes the self-supervised strategy for the paired training data. It is followed by a description of the grape completion network, GrapeCPNet (Figure~\ref{fig:raw3}).
@@
 \label{sec:251}
-In this paper, we used average precision AP as the evaluation metric for berry instance segmentation (similar to the original paper of \citep{vu_softgroup_2022}).
+In this paper, we used average precision AP as the evaluation metric for berry instance segmentation, similar to the original paper of \citet{vu_softgroup_2022}.
 The average APs with IoU (Intersection over Union) ranging from 50\% to 95\% in steps of 5\% were used and noted as AP@50:5:95.
@@
 
-In this paper, we use the chamfer distance (CD-distance) and F-Score to measure the effect of berry completion (similar to the original paper of \citep{yu_pointr_2021}). 
+In this paper, we use the chamfer distance (CD-distance) and F-Score to measure the effect of berry completion,  similar to the original paper of \citet{yu_pointr_2021}. 
 For each sample, the chamfer distance $d_{CD}$ between the predicted point set $P$ and the true point set $G$ was calculated as shown in Equation~(\ref{eq:8})
@@
 
+\section{Conclusions}
+
+aaa
+
 \section*{CRediT authorship contribution statement}
@@
 \section*{Data availability}
-The dataset and model weight will be available on request.
+The dataset and model weight for the test usage is available here: https://github.com/I3-Laboratory/GrapeCPNet. The whole dataset used in this paper is available upon request.
 

### 2025-02-14 main.tex
Intro, con. & fig caps

@@
 % volume).
-%   \item Nondestructive and highthroughput analysis for viticulture applications.
+%   \item Non-destructive and high-throughput analysis for viticulture applications.
   \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
@@
 Its global production and consumption is increasing year by year. 
-To better guide planting strategy and monitoring growing status, several geometric parameters like counts, length, and volume at bunch level and berry level are commonly used in actual applications.
-\citep{luo_prediction_2024,raihen_prediction_2024}.
-Among them, the number and the radius of the berries are the most important phenotypic parameters \citep{sneha_acrescale_2024}. 
-Traditional manual phenotyping of traits is labor-intensive and time-consuming, and often destructive. 
+To \replaced{effectively}{better} guide planting strategies and monitoring growing status, several geometric parameters\replaced{, including}{like counts, length, and volume at bunch level and berry level are commonly used in actual applications raihen\_prediction\_2024.}
+\deleted{Among them,} the number \deleted{and the radius }of \deleted{the} berries \replaced{and their radius, are frequently measured}{are the most important phenotypic parameters (sneha\_acrescale\_2024) }.
+Traditional manual \replaced{measuring}{phenotyping of }traits is labor-intensive and time-consuming, and often destructive. 
 To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic traits based on computer vision has attracted extensive interest in recent years. 
-Several simple geometry traits can be acquired from 2D images by using computer vision algorithms that use pattern recognition, machine learning, and deep learning \citep{zabawa_counting_2020}. 
+Several simple geometry traits can be acquired from 2D images by using computer vision algorithms that use pattern recognition, machine learning, and deep learning \citep{chen_instance_2023, zabawa_counting_2020}.
 Projecting the 2D image plane onto the 3D world inevitably results in information loss. 
 The occlusion of berries often lead to incomplete representations of grape bunches. 
-Additionally, clustered berries and their shadows  create challenges for obtaining reliable measurements of phenotypic parameters through 2D image analysis, even under controlled lightning conditions  \citep{fei_comprehensive_2022,xiang_multispace_2023}.
+Additionally, clustered berries and their shadows create challenges for obtaining reliable measurements of phenotypic parameters through 2D image analysis, even under controlled lightning conditions.
 
-Advances in 3D scanning and reconstruction techniques have made it possible to retain detailed spatial information about objects, enabling the acquisition of complex 3D morphological traits in grape bunches \citep{jiang_3d_2019,ni_threedimensional_2021}.
-Researchers have developed 3D phenotyping processes for grapes by combining feature-engineered point cloud processing algorithms \citep{rose_automated_2016,rist_highprecision_2018}. 
+Advances in 3D scanning and reconstruction techniques have made it possible to retain detailed spatial information about objects, enabling the acquisition of complex 3D morphological traits in grape bunches \citep{ni_threedimensional_2021}.
+Researchers have developed 3D phenotyping processes for grapes by combining feature-engineered point cloud processing algorithms \citep{rose_automated_2016, rist_highprecision_2018}. 
 These methods primarily rely on point cloud segmentation techniques, such as edge-based segmentation, region-growing segmentation, and sphere-fitting algorithms. 
@@
 \deleted{li\_psegnet\_2022 proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. }
-\replaced{However, few studies have reported deep learning networks perform well in}{The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on} berry level analysis.
+\replaced{However, few studies have reported good performance deep learning networks in}{The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on} berry level analysis.
 
@@
 
-\subsection{Berry Instance Segmentation \added{Module}}
+\subsection{Berry Instance Segmentation}
 \label{sec:22}
@@
 
-\subsection{Self-Supervised Point Cloud Completion \added{Module}}
+\subsection{Self-Supervised Point Cloud Completion}
 
@@
 
-To validate the accuracy of extracted morphological traits, the 12 validation bunches  were used after instance berry segmentation and berry completion (refer to Section~\ref{sec:22}). 
-The radius and volume of the 108 samples were calculated. 
-For ground truth measurement, we used the values of the radius and volume of the individual complete berry from the completed point clouds.
+To validate the accuracy of extracted morphological traits, the 12 validation bunches \added{with 108 berry samples} were \replaced{selected.
+The berries were first scanned while still attached to bunch (Fig.~\ref{fig:raw9}a2).
+After instance segmentation, these scans of each berry are incomplete caused by occlusion.
+We then applied our proposed self-supervised completion method to get completion predictions.
+Finally get ellipsoidal surface fitting results as prediction values.
+}{ used after instance berry segmentation and berry completion (refer to Section~\ref{sec:22})}
+\deleted{The radius and volume of the 108 samples were calculated.} 
+For ground truth measurement, \replaced{we separated berries from the bunch to get complete scans of corresponding berry (Fig.~\ref{fig:raw9}b1).
+Then applied the ellipsoidal surface fitting to these completely scans.
+}{we used the values of the radius and volume of the individual complete berry from the completed point clouds.}
 
@@
 
-To verify the efficiency of GrapeCPNet, we compared it to other point cloud completion networks: PoinTr, SnowFlakeNet, TopNet \citep{tchapmi_topnet_2019}, and GRNet \citep{xie_grnet_2020}.
+To verify the efficiency of GrapeCPNet, we compared it to other point cloud completion networks: PoinTr \citep{yu_pointr_2021} SnowFlakeNet \citep{xiang_snowflakenet_2021}, TopNet \citep{tchapmi_topnet_2019}, and GRNet \citep{xie_grnet_2020}.
 
@@
     \caption{Experimental results of axis length calculation for four species of fresh grape.
-From (a)-(d): Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape, and from (1)-(3): the calculation of the long, middle, and short axis, respectively.}
+From (a)-(d): Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape, \deleted{and from (1)-(3): the calculation of the long, middle, and short axis, }respectively.
+\added{The ground truth values are obtained by completely scanning berries that were separated from the bunch (Fig.~\ref{fig:raw9}b1); The predicted values are obtained from our proposed self-supervised completion method, which addresses incomplete scans of berries that occur due to occlusion while they were still attached to the bunch (Fig.~\ref{fig:raw9}a2).}}
     \label{fig:raw17}
@@
     \includegraphics[width=1\textwidth]{figures/Figure15.pdf}
-    \caption{Experimental results of berry volume calculation.}
+    \caption{Experimental results of berry volume calculation.
+\added{The ground truth values are obtained by completely scanning berries that were separated from the bunch (Fig.~\ref{fig:raw9}b1); The predicted values are obtained from our proposed self-supervised completion method, which addresses incomplete scans of berries that occur due to occlusion while they were still attached to the bunch (Fig.~\ref{fig:raw9}a2).}}
     \label{fig:raw18}
@@
 
-\section{Discussion and Conclusion}
+\section{Discussion}
+
+\added{}
 
@@
 
-aaa
+\added{In this study, we proposed a deep-learning-based pipeline for processing 3D phenotyping grape bunches reconstructed by photogrammetry.}
+\added{The major contribution is the self-supervised completion network, named GrapeCPNet, designed to address the problem of missing parts in berries occluded within grape bunches with few manual annotations.}
+\added{Due to the dense and compact arrangement of berries within a grape bunch, the inner portions are often occluded and not visible.}
+\added{This often presents challenges in algorithm design for individual berry segmentation and accurate berry size estimation.}
+\added{We utilized state-of-the-art, data-driven deep learning approaches to address these challenges.}
+\added{First, the SoftGroup network, utilizing segmentation annotations from 8 grape bunches, was used to train a data-driven berry instance segmentation model.}
+\added{By randomly producing missing areas from complete berries, we automatically generated large number of training data for completion tasks.}
+\added{By combining the centroid-based sparsed completion and diffusion-based dense completion structure, the proposed GrapeCPNet achieved better performance than existing completion networks, with Precision of 0.729, Recall of 0.772 and F-score of 0.751.}
+\added{The ellipsoid surface fitting, used to calculate three axis lengths and volumes, achieved an average $R^2$ of 0.86 and 0.97 respectively, when comparing completed berries with their ground truth.}
+\added{This study clearly demonstrates the potential of using data-drive strategies with minimal annotation effort to address the 3D occlsuion challenge in agricultural applications.}
+\added{Although this network has only been tested on grape bunches collected in a controlled environment, the proposed deep learning pipelines and training data generation approach have broad potential applications for in-field vineyards and even other crops in the future.}
 

### 2025-02-16 main.tex
results compaired

@@
 \usepackage{lineno}
+\usepackage{makecell}
 
@@
 \deleted{li\_psegnet\_2022 proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. }
-\replaced{However, few studies have reported good performance deep learning networks in}{The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on} berry level analysis.
+\replaced{However, few studies have reported good performance deep learning networks and pipelines in}{The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on} berry level analysis.
 
@@
 
-To describe the 3D morphology of berries, this paper used ellipsoidal surface fitting with three axes, for the completed berry point cloud.
+To describe the 3D morphology of berries, this paper used ellipsoidal surface fitting with three axes, for the completed berry point cloud (Fig.~\ref{fig:raw16}).
+
+% figure 16
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure11.pdf}
+    \caption{Example of \deleted{visualization of the predicted complete }berry point cloud fitted to \replaced{its ellisoid surface}{the surface of an ellipsoid}.}
+    \label{fig:raw16}
+\end{figure}
 
@@
 
-Suppose the point cloud of the complete berry is denoted as $P_{complete}=\{P_i \mid i=1, \cdots,n\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in the 3D space, and $n$ denotes the number of points. 
+Suppose the point cloud of \replaced{a}{the} complete berry is denoted as $P_{complete}=\{P_i \mid i=1, \cdots,n\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in the 3D space, and $n$ denotes the number of points.
 In this paper, it is fitted to an ellipsoid surface with three unequal long axes by the least squares method, and the function is shown in Equation~(\ref{eq:6}).
@@
 \label{sec:251}
-In this paper, we used average precision AP as the evaluation metric for berry instance segmentation, similar to the original paper of \citet{vu_softgroup_2022}.
-The average APs with IoU (Intersection over Union) ranging from 50\% to 95\% in steps of 5\% were used and noted as AP@50:5:95.
+In this paper, we used average precision AP as the evaluation metric for berry instance segmentation, similar to the original paper of \added{SoftGroup} \citet{vu_softgroup_2022}.
+The average APs with IoU (Intersection over Union) ranging from 50\% to 95\% in steps of 5\% were used and noted as \replaced{mAP@[.5:.95]}{AP@50:5:95}.
 
@@
 
-The bunch point cloud segmentation results are summarized in Table~\ref{tbl:3}.
+\deleted{The bunch point cloud segmentation results are summarized in Table~\ref{tbl:3} }. 
+% table 3
+% \begin{table}[h]
+%     \centering
+%     \caption{Instance berry segmentation results from whole bunch}
+%     \begin{tabular}{ccc}
+%         \hline
+%         \textbf{Class} & \textbf{mAP@[.5:.95]} \\
+%         \hline
+%         Berry & 0.995 \\
+%         Stem & 0.941 \\
+%         \hline
+%     \end{tabular}
+%     \label{tbl:3}
+% \end{table}
+\deleted{As can be seen from Table~\ref{tbl:3}, The value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.}
 
-% table 3
-\begin{table}[h]
-    \centering
-    \caption{Instance berry segmentation results from whole bunch}
-    \begin{tabular}{ccc}
-        \hline
-        \textbf{Model} & \textbf{Class} & \textbf{AP@50:5:95} \\
-        \hline
-        \multirow{2}{*}{SoftGroup \citep{vu_softgroup_2022}} & Berry & 0.995 \\
-        \cline{2-3}
-        & Stem & 0.941 \\
-        \hline
-    \end{tabular}
-    \label{tbl:3}
-\end{table}
-
-As can be seen from Table~\ref{tbl:3}, the AP value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.
+\added{The mAP@[.5:.95] values of berry and stem class are 0.995 and 0.941, respectively, which }showed a high accuracy of the berry segmentation from the bunch.
+\added{Since mAP@[.5:.95] is a strict evaluation metric, it represents the mean values of Average Precision (AP) scores calculated from AP50 to AP95 at 5\% IoU intervals}.
+\added{Compared to other studies, \citet{ni_threedimensional_2021} reported that their proposed segmentation network achieved a mAP@[.5:.95] of 0.877 on their testing dataset, while \citet{du_instance_2023} achieved a mAP[.5:.95] of 0.657 and an AP50 of 0.952.}
+\added{In our study, the AP50 value exceeded 0.999, with both recall and precision values at this level also over 0.999.}
+\added{When compared to traidtional berry semgnetation algorithms, \citet{rose_automated_2016} reported a mean recall of 0.776 and precision of 0.978;}
 The results of four fresh grapes for bunch point cloud segmentation are visualized in Fig.~\ref{fig:raw13}.
+\added{According that figure, we can also see an almost perfect instance berry segmentation results.}
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{figures/Figure11.pdf}
+    \includegraphics[width=1\textwidth]{figures/Figure12.pdf}
     \caption{Segmentation results of the bunch of four species of fresh grape, the stems point cloud and the noise point cloud are set to black, and the different color point sets indicate the point clouds of different berry instances obtained.}
@@
 
-The berry point cloud completion experiments are divided into two parts according to the different phases of the network: the results of the self-supervised training and the results of the practical application.
-
-The experimental results of GrapeCPNet compared to other point cloud completion algorithms are shown in Table~\ref{tbl:4}. 
+The berry point cloud completion experiments are divided into two parts according to the different phases of the network: 
+the results of the self-supervised training \added{(Test)} and the results of the practical application \added{(Inference)}.
+\replaced{As}{The experimental results of GrapeCPNet compared to other point cloud completion algorithms are} shown in Table~\ref{tbl:4}, 
 GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the comparative algorithms.
@@
     \centering
-    \caption{Experimental results of different completion networks based on self-supervised training for berry point cloud. Best performing results are visualized in bold.}
+    \caption{\replaced{Comparing proposed method with}{Experimental results of} different completion networks \deleted{based on self-supervised training} for berry point cloud.
+Best performing results are visualized in bold.}
     \begin{tabular}{cccccc}
@@
         \hline
-        \multirow{2}{*}{PoinTr} & Test & 9.036 & 0.721 & 0.705 & 0.713 \\
+        \multirow{2}{*}{\makecell{PoinTr \\ \citep{yu_pointr_2021}}} & Test & 9.036 & 0.721 & 0.705 & 0.713 \\
         \cline{2-6}
@@
         \hline
-        \multirow{2}{*}{SnowFlakeNet} & Test & 11.235 & 0.512 & 0.534 & 0.521 \\
+        \multirow{2}{*}{\makecell{SnowFlakeNet \\ \citep{xiang_snowflakenet_2021}}} & Test & 11.235 & 0.512 & 0.534 & 0.521 \\
         \cline{2-6}
@@
         \hline
-        \multirow{2}{*}{TopNet} & Test & 23.019 & 0.201 & 0.200 & 0.201 \\
+        \multirow{2}{*}{\makecell{TopNet \\ \citep{tchapmi_topnet_2019}}} & Test & 23.019 & 0.201 & 0.200 & 0.201 \\
         \cline{2-6}
@@
         \hline
-        \multirow{2}{*}{GRNet} & Test & 19.240 & 0.402 & 0.392 & 0.397 \\
+        \multirow{2}{*}{\makecell{GRNet \\ \citep{xie_grnet_2020}}} & Test & 19.240 & 0.402 & 0.392 & 0.397 \\
         \cline{2-6}
@@
         \hline
-        \multirow{2}{*}{GrapeCPNet (Ours)} & Test & \textbf{8.315} & \textbf{0.729} & \textbf{0.772} & \textbf{0.751} \\
+        \multirow{2}{*}{\makecell{GrapeCPNet \\ (Ours)}} & Test & \textbf{8.315} & \textbf{0.729} & \textbf{0.772} & \textbf{0.751} \\
         \cline{2-6}
@@
     \centering
-    \includegraphics[width=1\textwidth]{figures/Figure12.pdf}
-    \caption{Example of four fresh grape berry point cloud completion results: in subfigures a-d, the left side shows the incomplete berry point cloud obtained from the segmentation of the bunch, and the right side shows the completion results using GrapeCPNet under the self-supervised training-based method.}
+    \includegraphics[width=1\textwidth]{figures/Figure13.pdf}
+    \caption{Example of four fresh grape berry point cloud completion results: in subfigures a-d, the left side shows \replaced{incomplete berry while}{the incomplete berry point cloud obtained from the segmentation of the bunch, and} the right side shows the completion results using \added{proposed} GrapeCPNet \deleted{under the self-supervised training-based method}.}
     \label{fig:raw14}
@@
 
-The radius parameters were calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure~\ref{fig:raw16}.
+The radius parameters were calculated by fitting the berry to the surface of an ellipsoid\deleted{, as shown in Figure~\ref{fig:raw16}}.
+From Figure~\ref{fig:raw17}, it can be seen that the proposed method achieves an average $R^2$ of 0.86 \added{and average MAE of 0.608 mm} for the three axis lengths of the four species of grape.
 
-% figure 16
-\begin{figure}[hbt!]
-    \centering
-    \includegraphics[width=1\textwidth]{figures/Figure13.pdf}
-    \caption{Example of visualization of the predicted complete berry point cloud fitted to the surface of an ellipsoid.}
-    \label{fig:raw16}
-\end{figure}
+This result can be dissected as follows:
 
@@
 
-From Fig.~\ref{fig:raw17}, it can be seen that the proposed method achieves an average $R^2$ of 0.86 for the three axis lengths of the four species of grape. 
-This result can be dissected as follows:
-
 (1) The different species: Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape axis length prediction reached an average $R^2$ of 0.86, 0.84, 0.89, and 0.84, respectively. 
 Among them, Kyoho Grape achieved the best results due to its spherical berries that are not too densely clustered and the lower difficulty in berry completion and morphology fitting. 
-Secondly, Red Grape and Green Grape both present a typical ellipsoid shape, but the latter is less precise than the former due to its greater ratio of long axis to short axis, which provides a more complex presentation.
+Secondly, Red Grape and Green Grape both present a typical ellipsoid shape, but the \replaced{Red}{latter} is less precise than the \replaced{Green}{former} due to its \replaced{larger}{greater} ratio of long axis to short axis, which provides a more complex presentation.
+\added{As reported by \citet{schneider_predicting_2020}, the mean length-to-width ratio of Green Grape is 21.18mm to 18.75mm, while for Red Grape, it is 24.11mm to 18.41mm.}
 Shine-Muscat Grape had the lowest precision, which was due to the fact that its berry grows tightly and occlude each other heavily, making it harder to accurately complete its shape.
@@
 
-The experimental results showed that the proposed method achieved high accuracy in the calculation of the radius of different grape species. 
 In addition, based on the radius prediction results, the volume of all 108 berry samples was calculated in this paper, and the experimental results are shown in Figure~\ref{fig:raw18}.
+For the berry volume calculation of the four species, the $R^2$ was 0.97, and the MAE was 0.3842 $cm^3$.
+\deleted{Indicating a high precision for predicting the volume of the different species.}
 
@@
 
-For the berry volume calculation of the four species, the $R^2$ was 0.97, and the MAE was 0.3842 $cm^3$. Indicating a high precision for predicting the volume of the different species.
+The experimental results showed that the proposed method achieved \added{both} high accuracy in the calculation of the radius \added{and volumes} of different grape species.
+\added{In out study, we achieved an average $R^2$ of 0.86 and an average MAE of 0.608 mm across the three axis of berry, as well as an $R^2$ of 0.9689 and an MAE of 0.3842 $cm^3$ for berry volumes.}
+\added{By comparision, \citet[Fig.~4]{rist_highprecision_2018} reported $R^2$ values of 0.54, 0.85, and 0.83 for berry width, length, and volume, respectively.}
+\added{\citet{botturi_stewie_2023} reported a best-case MAE of 21.7mm for berry ratio estimataion using deep learning network on 2D images.}
+\added{\citet{ni_threedimensional_2021} achieved a RMSE of 0.292 $cm^3$ for volume estimation.}
+\added{Although the method by \citet{ni_threedimensional_2021} achieved a lower errors for volume estimataion, it relies on sphere fitting that are primarily applicable to clustered, round fruits.}
+\added{In contrast, our proposed method not only accounts for occluded areas but is also adaptable to fruits of varying shapes, if appropriate paired training data is available.}
 
@@
 
-\added{}
+% achievement and contribution of ths study
+In this paper, \replaced{an automated deep learning pipeline for }{a method for the automatic }acquisition of 3D phenotypic traits of grape \added{bunch} was presented to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end analysis.
+Based on the \added{3D} point cloud of a grape bunch \added{obtained by close-range multi-view photogrammetry}, a combination of deep learning point cloud processing algorithms realized the counting of the number of berries, the calculation of berry radius, and berry volume.
+\replaced{As a major contribution}{Moreover}, to address the problem of incomplete point clouds of berries due to occlusion, we introduced GrapeCPNet, a berry point cloud completion model based on the self-supervised training method.
 
-In this paper, a method for the automatic acquisition of 3D phenotypic traits of grape was presented to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end analysis.
-Based on the point cloud of a grape bunch, a combination of deep learning point cloud processing algorithms realized the counting of the number of berries, the calculation of berry radius, and berry volume.
-Moreover, to address the problem of incomplete point clouds of berries due to occlusion, we introduced GrapeCPNet, a berry point cloud completion model based on the self-supervised training method.
+% revisiting background to reboot reader
 
+% revisit gap/aim/method
+
+% revisit results and explore their implecations
+
+% amap to literatures for comparison/support
+
+% ppotential limitations and suggestions for future works
+
+% the achievement / impact of study / potential applications.
 As discussion point, we found that GrapeCPNet was not effective in the case of complex berry appearance, such as drop-shaped. 
@@
 \added{First, the SoftGroup network, utilizing segmentation annotations from 8 grape bunches, was used to train a data-driven berry instance segmentation model.}
-\added{By randomly producing missing areas from complete berries, we automatically generated large number of training data for completion tasks.}
-\added{By combining the centroid-based sparsed completion and diffusion-based dense completion structure, the proposed GrapeCPNet achieved better performance than existing completion networks, with Precision of 0.729, Recall of 0.772 and F-score of 0.751.}
+% \added{By randomly producing missing areas from complete berries, we automatically generated large number of training data for completion tasks.}
+\added{The proposed GrapeCPNet also achieved better performance than existing completion networks, with Precision of 0.729, Recall of 0.772 and F-score of 0.751.}
 \added{The ellipsoid surface fitting, used to calculate three axis lengths and volumes, achieved an average $R^2$ of 0.86 and 0.97 respectively, when comparing completed berries with their ground truth.}
 \added{This study clearly demonstrates the potential of using data-drive strategies with minimal annotation effort to address the 3D occlsuion challenge in agricultural applications.}
-\added{Although this network has only been tested on grape bunches collected in a controlled environment, the proposed deep learning pipelines and training data generation approach have broad potential applications for in-field vineyards and even other crops in the future.}
+\added{Although this network has only been tested on grape bunches collected in a controlled indoor environment, the proposed deep learning pipelines and training data generation approach have broad potential applications for in-field vineyards and even other crops in the future.}
 

### 2025-02-16 main.tex
discussion part 1

@@
 This encoder-decoder network was extended and optimized by \citet{blok_highthroughput_2025} for high-throughput 3D shape completion of potato tubers on a commercial harvester. 
-Outside the agricultural domain, \citet{tang_lakenet_2022} proposed a point cloud completion network (Lake-net) for furniture model point cloud datasets.
+\deleted{Outside the agricultural domain, tang\_lakenet\_2022 proposed a point cloud completion network (Lake-net) for furniture model point cloud datasets.} 
 For grape berry application, the shape of the berry can be roughly approached by the deformation of a sphere or ellipsoid depending on the species. 
@@
 \label{sec:251}
-In this paper, we used average precision AP as the evaluation metric for berry instance segmentation, similar to the original paper of \added{SoftGroup} \citet{vu_softgroup_2022}.
+In this paper, we used average precision AP as the evaluation metric for berry instance segmentation, similar to the original paper of \added{SoftGroup} \citep{vu_softgroup_2022}.
 The average APs with IoU (Intersection over Union) ranging from 50\% to 95\% in steps of 5\% were used and noted as \replaced{mAP@[.5:.95]}{AP@50:5:95}.
@@
 \subsection{Berry Instance Segmentation Results}
+\label{sec: insegresults}
 
@@
         \hline
-        \textbf{Model} & \textbf{DataSet} & \textbf{$d_{CD}$ $\downarrow$} & \textbf{Precision $\uparrow$} & \textbf{Recall $\uparrow$} & \textbf{F-score $\uparrow$} \\
+        \textbf{Model} & \textbf{DataSet} & \textbf{$d_{CD}$ (mm) $\downarrow$} & \textbf{Precision $\uparrow$} & \textbf{Recall $\uparrow$} & \textbf{F-score $\uparrow$} \\
         \hline
@@
 From Figure~\ref{fig:raw17}, it can be seen that the proposed method achieves an average $R^2$ of 0.86 \added{and average MAE of 0.608 mm} for the three axis lengths of the four species of grape. 
-
 This result can be dissected as follows:
@@
 Secondly, Red Grape and Green Grape both present a typical ellipsoid shape, but the \replaced{Red}{latter} is less precise than the \replaced{Green}{former} due to its \replaced{larger}{greater} ratio of long axis to short axis, which provides a more complex presentation.
-\added{As reported by \citet{schneider_predicting_2020}, the mean length-to-width ratio of Green Grape is 21.18mm to 18.75mm, while for Red Grape, it is 24.11mm to 18.41mm.}
+\added{As also reported by \citet{schneider_predicting_2020}, the mean length-to-width ratio of Green Grape is 21.18mm to 18.75mm, while for Red Grape, it is 24.11mm to 18.41mm.}
 Shine-Muscat Grape had the lowest precision, which was due to the fact that its berry grows tightly and occlude each other heavily, making it harder to accurately complete its shape.
@@
 \added{\citet{botturi_stewie_2023} reported a best-case MAE of 21.7mm for berry ratio estimataion using deep learning network on 2D images.}
-\added{\citet{ni_threedimensional_2021} achieved a RMSE of 0.292 $cm^3$ for volume estimation.}
-\added{Although the method by \citet{ni_threedimensional_2021} achieved a lower errors for volume estimataion, it relies on sphere fitting that are primarily applicable to clustered, round fruits.}
+\added{Although the method by \citet{ni_threedimensional_2021} achieved a lower errors for volume estimataion (RMSE of 0.292 $cm^3$), it relies on sphere fitting that are primarily applicable to clustered, round fruits.}
 \added{In contrast, our proposed method not only accounts for occluded areas but is also adaptable to fruits of varying shapes, if appropriate paired training data is available.}
@@
 % achievement and contribution of ths study
-In this paper, \replaced{an automated deep learning pipeline for }{a method for the automatic }acquisition of 3D phenotypic traits of grape \added{bunch} was presented to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end analysis.
-Based on the \added{3D} point cloud of a grape bunch \added{obtained by close-range multi-view photogrammetry}, a combination of deep learning point cloud processing algorithms realized the counting of the number of berries, the calculation of berry radius, and berry volume.
+In this paper, \replaced{an automated deep learning pipeline for}{a method for the automatic} acquisition of 3D phenotypic traits of grape \added{bunch} was presented to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end analysis.
 \replaced{As a major contribution}{Moreover}, to address the problem of incomplete point clouds of berries due to occlusion, we introduced GrapeCPNet, a berry point cloud completion model based on the self-supervised training method.
+\deleted{Based on the point cloud of a grape bunch, a combination of deep learning point cloud processing algorithms realized the counting of the number of berries, the calculation of berry radius, and berry volume.
+}
 
 % revisiting background to reboot reader
+\added{Grape berry counting and size estimation plays a critical role in vineyard management and yield prediction.}
+\added{By using common digital cameras alongside deep learning networks, several studies have achieved automatic berry detection and instance segmentation \citep{jadhav_comparative_2021, chen_instance_2023}, and then forward the analyses of geometry traits and yield estimation \citep{quinones_gcnet_2025}.}
+\added{However, because of the dense and compact arrangement of berries within a grape bunch, some portions are often occluded and not visible when relying solely on single 2D images.}
+\added{To reduce the effects of occlusion, \citet{du_instance_2023} reported accurate berry counting estimations by correlating image-based detections with ground measurements.}
+\added{However, applying this method to other vineyards requires extensive, labor-intensive ground measurements}
+\added{Similarly, \citet{botturi_stewie_2023} attempted to extract feature maps, such as berry radii, directly from deep networks applied to 2D images}
+\added{Despite this approach, it still suffers from information loss and resulted in a high MAE of 21.7 mm.}
+\added{Applying multi-view images for 3D reconstruction can significantly reduce the extent of occlusion caused by viewpoint limitations.}
+\added{But unlike 2D images, which have well-structured data in the form of organized pixel matrices, the unordered nature of points in a 3D point cloud introduces significant challenges.}
+\added{Meanwhile, the inner portion of berry is still invisible, only the surface of exposed berry surfaces can be scanned or reconstructed.}
+\added{This complicates the algorithm design for individual berry segmentation and accurate berry size estimation.}
 
 % revisit gap/aim/method
+\added{For individual berry segmentation, early studies relied on the circular characteristics of the visible portions of berries for segmentation.}
+\added{Building on the work of \citet{schnabel_efficient_2007}, who introduced point cloud shape detection using RANSAC, researchers were able to cluster partial berries based on their rounded shapes \citep{scholer_automated_2015, rist_highprecision_2018, schneider_predicting_2020}.}
+\added{However, this feature-based approach performs well only in sparse grape arrangements and proves ineffective in more complex, dense conditions.}
+\added{The reliance on manually designed features for algorithm development has now reached its limitations.}
+\added{With advancements in machine learning, the focus has shifted to a data-driven era, where algorithms can learn complex feature patterns automatically.}
+\added{For instance, \citet{rose_automated_2016} applied machine learning to distinguish features between grape berry clusters and background leaves automatically.}
+\added{Similarly, \citet{ni_threedimensional_2021} implemented a two-step approach by first using mature 2D instance segmentation techniques on 2D images and then projecting the resulting segmentation masks onto reconstructed 3D models to complete the challenging task of 3D instance segmentation.}
+\added{In another approach, \citet{luo_3d_2023} Mask R-CNN for 2D image segmentation and projected the results onto RGB-D point clouds.}
+\added{The normal directions derived from the point clouds were then packed as an additional feature in the PointNet++ network for point cloud segmentation.}
+\added{In this study, we applied the state-of-the-art point cloud segmentation network, SoftGroup \citep{vu_softgroup_2022} directly to the problem.}
+\added{The primary time-consuming work of our approach was the annotation of 3D data for instance segmentation.}
+\added{Compared to similar studies on grape berries, our proposed method demonstrated superior performance, achieving the best results among the reviewed methods (Subsection~\ref{sec: insegresults}).}
 
-% revisit results and explore their implecations
-
-% amap to literatures for comparison/support
-
-% ppotential limitations and suggestions for future works
+\added{For berry completetion by deep learning, the most difficult and time-consuming work is preparing the paired training dataset with complete and incomplete point cloud.}
+\added{As our previous studies conducted for potato tuber completion networks \citep{blok_highthroughput_2025}, a distinguishable pin was used as reference point for pairing complete tubers by photogrammetry and incomplete tubers by RGBD camera.}
+\added{Then the pin-guided point cloud matching algorithm is applied to calculate transformation matrix between paired dataset.}
+\added{The potato tuber is single object with clear texture and shape variances, thus pairing through two different scans by two sensors is not too difficult.}
+\added{For the grape berry, it is super rounded with weak texture features and strong reflectance, making the paired data super challenging.}
+\added{Thus, the previous pin-guided point cloud paring methods for collection paired data does not work.}
 
 % the achievement / impact of study / potential applications.
-As discussion point, we found that GrapeCPNet was not effective in the case of complex berry appearance, such as drop-shaped. 
+\deleted{As discussion point, we found that GrapeCPNet was not effective in the case of complex berry appearance, such as drop-shaped.}
+
+% future works.
 We have found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
@@
 In addition, the noise in the data is also related to the effectiveness of the method proposed in this paper. 
-How to implement the method in practical application scenarios, such as RGB-D collected point cloud data, is another issue to be considered in future research.
+How to implement the method in practical application scenarios, such as RGB-D collected point cloud data, is another issue to be considered in future research. \citet{blok_highthroughput_2025}
 
@@
 
-\section{Conclusions}
+\section{Conclusion}
 
@@
 \added{The major contribution is the self-supervised completion network, named GrapeCPNet, designed to address the problem of missing parts in berries occluded within grape bunches with few manual annotations.}
-\added{Due to the dense and compact arrangement of berries within a grape bunch, the inner portions are often occluded and not visible.}
-\added{This often presents challenges in algorithm design for individual berry segmentation and accurate berry size estimation.}
 \added{We utilized state-of-the-art, data-driven deep learning approaches to address these challenges.}

### 2025-02-17 main.tex
finish discussion

@@
 \usepackage{makecell}
+\usepackage[T1]{fontenc}
 
@@
 \subsubsection{Self-supervised training data generation}
+\label{sec:berrycut}
 
@@
 \subsection{Berry Instance Segmentation Results}
-\label{sec: insegresults}
+\label{sec:insegresults}
 
@@
 \subsection{Berry Self-Supervised Completion Results}
+\label{sec:32}
 
@@
 \added{The primary time-consuming work of our approach was the annotation of 3D data for instance segmentation.}
-\added{Compared to similar studies on grape berries, our proposed method demonstrated superior performance, achieving the best results among the reviewed methods (Subsection~\ref{sec: insegresults}).}
+\added{Compared to similar studies on grape berries, our proposed method demonstrated superior performance, achieving the best results among the reviewed methods (Subsection~\ref{sec:insegresults}).}
 
-\added{For berry completetion by deep learning, the most difficult and time-consuming work is preparing the paired training dataset with complete and incomplete point cloud.}
-\added{As our previous studies conducted for potato tuber completion networks \citep{blok_highthroughput_2025}, a distinguishable pin was used as reference point for pairing complete tubers by photogrammetry and incomplete tubers by RGBD camera.}
-\added{Then the pin-guided point cloud matching algorithm is applied to calculate transformation matrix between paired dataset.}
-\added{The potato tuber is single object with clear texture and shape variances, thus pairing through two different scans by two sensors is not too difficult.}
-\added{For the grape berry, it is super rounded with weak texture features and strong reflectance, making the paired data super challenging.}
-\added{Thus, the previous pin-guided point cloud paring methods for collection paired data does not work.}
+\added{For berry completion using deep learning, the most challenging and time-consuming task is preparing the paired training datasets of complete and incomplete point clouds.}
+\added{In our previous work on potato tuber completion networks \citep{blok_highthroughput_2025}, a distinguishable pin was used as a reference point to align the complete tuber scans obtained via photogrammetry with the incomplete tuber scans captured using an RGB-D camera.}
+\added{A pin-guided point cloud matching algorithm was then applied to calculate the transformation matrix for pairing the datasets.}
+\added{Potato tubers, being single objects with clear textures and shape variation, presented fewer challenges when aligning data collected by two different types of sensors.}
+\added{However, grape berries pose a significantly more difficult problem due to their highly rounded shapes, weak texture features, and strong reflectance, which complicates the creation of paired data.}
+\added{As a result, the previous pin-guided point cloud pairing method used for potato tuber datasets is not effective for grape berries.}
+\added{Thus, we simulated random sphere cutting on the complete berry point clouds to generate thousands of paired incomplete point clouds, as described in Subsection~\ref{sec:berrycut}.}
+\added{As demonstrated in Subsection~\ref{sec:32}, these automatically generated paired training datasets were successfully used to train several completion models (Table~\ref{tbl:4}).}
+We have found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
+\added{Considering the agricultural plant completion task, our proposed GrapeCPNet, which combines centroid-based sparse completion with diffusion-based dense completion, outperformed other networks in terms of performance.}
+We found that GrapeCPNet \replaced{performed a little bit worse}{effective} in the case of \replaced{strange}{complex} berry \replaced{shapes}{appearance}, such as drop-shaped.
+We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion.
+
+% challenges, limitations and future works.
+\added{Another limitation of this study is that it focused on a single berry bunch in a controlled environment.}
+The noise in the data is also related to the effectiveness of the method proposed in this paper.
+\added{For practical applications in vineyards, collecting the same point cloud quality as that achieved in controlled indoor environments can be challenging, and multi-view data collection may not be as efficient.}
+How to \added{effectively} implement the method in practical application scenarios\deleted{, such as RGB-D collected point cloud data,} is another issue to be considered in future research.
+\added{To increasing data collection efficiency, devices such as RGB-D cameras \citep{blok_highthroughput_2025}, fisheye cameras \citep{tamura_unsupervised_2025}, or even 360 cameras can be used.}
+\added{Moreover, as in previous studies \citep{rose_automated_2016, luo_3d_2023}, investigating methods to segment individual grape bunches directly from vineyard scans using deep learning techniques should be an area of future exploration.}
+\added{Additionally, \citet[Fig.~9]{scholer_automated_2015} successfully demonstrated the construction of virtual 3D models of grape bunches, including the hidden branching architecture. }
+\added{By collecting time-series growth data, the branching structure could potentially be captured during early stages of thinning, as suggested by \citep{du_instance_2023}.}
+\added{Such data could enable studies on growth prediction for optimizing harvesting times and assessments of branching structure deviations within crowded berry bunches.}
+\added{Finally, applying the latest procedural computer graphics (CG) modeling techniques \citep{karoly_automated_2022} or functional-structural plant models \citep{helmrich_scalable_2024} represents another promising approach to advancing practical applications in this field.}
 
 % the achievement / impact of study / potential applications.
-\deleted{As discussion point, we found that GrapeCPNet was not effective in the case of complex berry appearance, such as drop-shaped.}
-
-% future works.
-We have found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
-We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion. 
-In addition, the noise in the data is also related to the effectiveness of the method proposed in this paper. 
-How to implement the method in practical application scenarios, such as RGB-D collected point cloud data, is another issue to be considered in future research. \citet{blok_highthroughput_2025}
-
 Through the method proposed in this paper, the automated acquisition of 3D phenotypic traits of grape can be realized, which is of great significance in the field of agricultural production and scientific research.

### 2025-02-17 main.tex
decrease references

@@
 \added{Such data could enable studies on growth prediction for optimizing harvesting times and assessments of branching structure deviations within crowded berry bunches.}
-\added{Finally, applying the latest procedural computer graphics (CG) modeling techniques \citep{karoly_automated_2022} or functional-structural plant models \citep{helmrich_scalable_2024} represents another promising approach to advancing practical applications in this field.}
+\added{Finally, applying the latest procedural computer graphics (CG) modeling techniques or functional-structural plant models represents another promising approach to advancing practical applications in this field.}
 

### 2025-04-30 main.v0.edits.tex
rm v0 changes

--- 2025-02-17 main.tex
@@
 
-\textbf{\added{Highlights}}
-
-\begin{itemize}
-%   \item Novel deep learning pipeline for automated 3D grape phenotyping.
-%   \item GrapeCPNet: Self-supervised network for berry points cloud completion.
-%   \item High accuracy in berry instance segmentation (99.5\% average precision).
-%   \item Robust performance across four grape varieties ($R^2$ of 0.855 for radius, 0.969 for 
-% volume).
-%   \item Non-destructive and high-throughput analysis for viticulture applications.
-  \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
-  \item \added{GrapeCPNet is trained using self-supervision, free of manual annotations.}
-  \item \added{Integrated into a deep learning pipeline for automated 3D grape bunch phenotyping.}
-  \item \added{Achieved over 0.85 $R^2$ and 99.5\% average precision on four grape varieties.}
-\end{itemize}
+% \textbf{\added{Highlights}}
+% \begin{itemize}
+% %   \item Novel deep learning pipeline for automated 3D grape phenotyping.
+% %   \item GrapeCPNet: Self-supervised network for berry points cloud completion.
+% %   \item High accuracy in berry instance segmentation (99.5\% average precision).
+% %   \item Robust performance across four grape varieties ($R^2$ of 0.855 for radius, 0.969 for 
+% % volume).
+% %   \item Non-destructive and high-throughput analysis for viticulture applications.
+%   \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
+%   \item \added{GrapeCPNet is trained using self-supervision, free of manual annotations.}
+%   \item \added{Integrated into a deep learning pipeline for automated 3D grape bunch phenotyping.}
+%   \item \added{Achieved over 0.85 $R^2$ and 99.5\% average precision on four grape varieties.}
+% \end{itemize}
 
@@
 Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
-For instance, \citet{ge_symmetrybased_2020} assume that strawberries are symmetrical, suggesting that their shape can be completed by mirroring the existing shape, provided an appropriate symmetrical plane can be identified.
+For instance, \citet{ge_symmetrybased_2020} assume that strawberries are symmetrical, suggesting that their shape can be completed by , provided an appropriate symmetrical plane can be identified.
 \citet{marangoz_fruit_2022} proposed an super-ellipsoids matching approach to map fruits on plants and estimate their shape.

### 2025-04-30 response2reviewer.tex
add reviewer's comments

\documentclass{ar2rc}
\usepackage{multicol}
\usepackage{tcolorbox}
\usepackage{booktabs}
\usepackage{array}
\usepackage{geometry}

\usepackage{natbib}

\newcommand{\papertitle}{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}
\newcommand{\journalname}{Computers and Electronics in Agriculture}

\rfoot{Page \thepage}
\lettertitle{The Response to Reviewers}
\journal{\journalname}
\doi{COMPAG-D-25-00311R1}

\title{\papertitle}
\author{
    Wenli Zhang \textsuperscript{a,*},
    Chao Zheng \textsuperscript{a},
    Chenhuizi Wang \textsuperscript{a},
    Pieter M. Blok \textsuperscript{b},
    Haozhou Wang \textsuperscript{b},
    Wei Guo \textsuperscript{b,*}
}

\corresponding{Corresponding author: zhangwenli@bjut.edu.cn; guowei@g.ecc.u-tokyo.ac.jp }
\email{
    \textsuperscript{a} Information Department, Beijing University of Technology, Beijing, China \\
    \textsuperscript{b} Graduate School of Agricultural and Life Sciences, The University of Tokyo, Tokyo, Japan
}

\begin{document}

\begin{center}
    \maketitle
\end{center}

\BT{To Editor and Reviewers}

\BL{Thank you for giving us the opportunity to submit a revised draft of the manuscript ``\papertitle'' for publication in the Journal of \journalname. We appreciate the time and effort that editors and the reviewers dedicated to providing feedback on our manuscript and are grateful for the insightful comments and valuable improvements to our paper. We have incorporated most of the suggestions made by the reviewers. Those changes are highlighted within the manuscript. Please see below, for a point-by-point response to the reviewers' comments and concerns. All page numbers refer to the revised manuscript file with tracked changes.}

\section{Reviewer \#1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#1}, fonttitle = \bfseries]
    Overall, the paper is well structured with a clear goal,  and the authors provide insight to justify their design choices. However, I believe the paper will benefit from  more experiments, particularly on the instance segmentation and  completion parts.
\end{tcolorbox}

\response{Thanks for your positive comments.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#2}, fonttitle = \bfseries]
    Regarding the instance segmentation, I understand that this is not the main contribution of the paper. Still, it would be nice to test different approaches here to evaluate the robustness of the completion network to varying levels of wrong predictions. Along a similar line, I would have liked to see the completion network working on ground truth segmentation labels as this will disentangle errors coming from the instance segmentation net and the completion net.
\end{tcolorbox}

\response{We have modified it in Sec. \uppercase\expandafter{\romannumeral1}, and highlighted it in yellow.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#3}, fonttitle = \bfseries]
    Regarding the completion net, I would have  liked to see ablation studies here as I believe this is the main  contribution of this work. For example, how does the number of cuts  influence the results of the completion metrics? How does the number of  output points in the centroid-based contour influence the snowflake net?
\end{tcolorbox}

\response{
    ...
}

\manuscript{
    ...
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#1}, fonttitle = \bfseries]
    Finally, is there a reason why the approach of Blok et al. 2025 is not being used as a  baseline? I would have liked to see a non-learning-based baseline as  well, like Marangoz et al. 2022
\end{tcolorbox}

\response{
    ...
}

\manuscript{
    ...
}

\section{Reviewer \#2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#1}, fonttitle = \bfseries]
    Line 159: What does "instance-level" mean? Which platform, software, or tool was used for labeling?
\end{tcolorbox}

\response{
    ...
}

\manuscript{
    ...
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#2}, fonttitle = \bfseries]
    Line 179: What is meant by "selection area"?
\end{tcolorbox}

\response{
    ...
}

\manuscript{
    ...
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#3}, fonttitle = \bfseries]
    Table 3 results: Was the same dataset used to assess the other algorithms, or were those metrics taken from their original studies?
\end{tcolorbox}

\response{
    ...
}

\manuscript{
    ...
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#4}, fonttitle = \bfseries]
    Occlusion  threshold: Is there a berry-occlusion threshold? For example, if less  than 50\% of a berry is visible, is it included? How are barely visible  berries handled?
\end{tcolorbox}

\response{
    ...
}

\manuscript{
    ...
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tcolorbox}[title = {Comment \#5}, fonttitle = \bfseries]
    Limitations \& future directions: How will the  model perform on wine grapes. Wine grapes accounts for ~60\% of US grape  production; clusters are denser, and berries are smaller than in table grapes.
\end{tcolorbox}

\response{
    ...
}

\manuscript{
    ...
}

\phantom{\cite{}} % 添加一个不可见的伪引用, 不会显示但能满足BibTeX要求避免无引用时报错
\bibliographystyle{elsarticle-harv}
\renewcommand{\bibsection}{} % 隐藏reference标题，如果需要则注释掉这一行
\bibliography{references}

\end{document}

% The copy-paste templates
\begin{verbatim}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{tcolorbox}[title = {Comment \#1}, fonttitle = \bfseries]
        ...
    \end{tcolorbox}

    \response{
        ...
    }

    \manuscript{
        ...
    }

\end{verbatim}

### 2025-05-01 response2reviewer.tex
auito comment counter

@@
 \section{Reviewer \#1}
+\setcounter{reviewercomment}{0}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#1}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Overall, the paper is well structured with a clear goal,  and the authors provide insight to justify their design choices.
 However, I believe the paper will benefit from  more experiments, particularly on the instance segmentation and  completion parts.
-\end{tcolorbox}
+\end{reviewercomment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#2}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Regarding the instance segmentation, I understand that this is not the main contribution of the paper.
@@
 Along a similar line, I would have liked to see the completion network working on ground truth segmentation labels as this will disentangle errors coming from the instance segmentation net and the completion net.
-\end{tcolorbox}
+\end{reviewercomment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#3}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Regarding the completion net, I would have  liked to see ablation studies here as I believe this is the main  contribution of this work.
@@
 How does the number of  output points in the centroid-based contour influence the snowflake net?
-\end{tcolorbox}
+\end{reviewercomment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#1}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Finally, is there a reason why the approach of Blok et al. 2025 is not being used as a  baseline? I would have liked to see a non-learning-based baseline as  well, like Marangoz et al. 2022
-\end{tcolorbox}
-
+\end{reviewercomment}
 \response{
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#1}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Line 159: What does "instance-level" mean? Which platform, software, or tool was used for labeling?
-\end{tcolorbox}
+\end{reviewercomment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#2}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Line 179: What is meant by "selection area"?
-\end{tcolorbox}
+\end{reviewercomment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#3}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Table 3 results: Was the same dataset used to assess the other algorithms, or were those metrics taken from their original studies?
-\end{tcolorbox}
+\end{reviewercomment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#4}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Occlusion  threshold: Is there a berry-occlusion threshold? For example, if less  than 50\% of a berry is visible, is it included? How are barely visible  berries handled?
-\end{tcolorbox}
+\end{reviewercomment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tcolorbox}[title = {Comment \#5}, fonttitle = \bfseries]
+\begin{reviewercomment}
     Limitations \& future directions: How will the  model perform on wine grapes.
 Wine grapes accounts for ~60\% of US grape  production; clusters are denser, and berries are smaller than in table grapes.
-\end{tcolorbox}
+\end{reviewercomment}
 
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{tcolorbox}[title = {Comment \#1}, fonttitle = \bfseries]
+    \begin{reviewercomment}
         ...
-    \end{tcolorbox}
+    \end{reviewercomment}
 

### 2025-05-01 main.tex
auito comment counter

--- 2025-02-16 main.tex
@@
 
-% Title
-% \title{GrapeCPNet: A deep learning integration for grape completion and phenotyping in 3D}
-\title{\added{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}}
+\title{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}
 \author{
@@
 \textsuperscript{b} Graduate School of Agricultural and Life Sciences, The University of Tokyo, Tokyo, Japan\\
-% \textsuperscript{*} \\
-
-\textbf{\added{Highlights}}
-
-\begin{itemize}
-%   \item Novel deep learning pipeline for automated 3D grape phenotyping.
-%   \item GrapeCPNet: Self-supervised network for berry points cloud completion.
-%   \item High accuracy in berry instance segmentation (99.5\% average precision).
-%   \item Robust performance across four grape varieties ($R^2$ of 0.855 for radius, 0.969 for 
-% volume).
-%   \item Non-destructive and high-throughput analysis for viticulture applications.
-  \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
-  \item \added{GrapeCPNet is trained using self-supervision, free of manual annotations.}
-  \item \added{Integrated into a deep learning pipeline for automated 3D grape bunch phenotyping.}
-  \item \added{Achieved over 0.85 $R^2$ and 99.5\% average precision on four grape varieties.}
-\end{itemize}
 
@@
 Its global production and consumption is increasing year by year. 
-To \replaced{effectively}{better} guide planting strategies and monitoring growing status, several geometric parameters\replaced{, including}{like counts, length, and volume at bunch level and berry level are commonly used in actual applications raihen\_prediction\_2024.}
-\deleted{Among them,} the number \deleted{and the radius }of \deleted{the} berries \replaced{and their radius, are frequently measured}{are the most important phenotypic parameters (sneha\_acrescale\_2024) }.
-Traditional manual \replaced{measuring}{phenotyping of }traits is labor-intensive and time-consuming, and often destructive. 
+To effectively guide planting strategies and monitoring growing status, several geometric parameters, including the number of berries and their radius, are frequently measured. 
+Traditional manual measuring traits is labor-intensive and time-consuming, and often destructive. 
 To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic traits based on computer vision has attracted extensive interest in recent years. 
@@
 Unfortunately, traditional point cloud processing algorithms heavily rely on prior knowledge of the target object and require extensive manual feature engineering and parameter tuning to achieve optimal results in a wide range of conditions, thereby limiting their generalization performance.
-\added{Implementing} state-of-the-art deep learning approaches\replaced{, which automatically learn features}{use a data-driven feature learning} from the point cloud data \replaced{, can  reduce the workload of designing robust algorithms for complex and diverse conditions}{ automatically}.
-\deleted{It recently shows promising adaptability and accuracy in plant 3D phenotyping (schneider\_predicting\_2020, scholer\_automated\_2015). }
-\deleted{Focusing on point cloud segmentation applications, }
-\deleted{li\_maspc\_2022 proposed MASPC\_Transform to segment the stems and leaves of rose bush point cloud data to obtain 3D phenotypic parameters. }
-\deleted{wang\_3d\_2022 realized leaf instance segmentation by designing the PartNet for lettuce point cloud data. }
-\deleted{li\_psegnet\_2022 proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. }
-\replaced{However, few studies have reported good performance deep learning networks and pipelines in}{The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on} berry level analysis.
+Implementing state-of-the-art deep learning approaches, which automatically learn features from the point cloud data, can reduce the workload of designing robust algorithms for complex and diverse conditions.
+However, few studies have reported good performance deep learning networks and pipelines in berry level analysis.
 
-\added{Another challenge after the success of instance berry segmentation is the incomplete representation of berry surfaces.} 
+Another challenge after the success of instance berry segmentation is the incomplete representation of berry surfaces. 
 The aggregated cluster growth causes the berries to squeezed against each other, leading to self occlusion and resulting in an incomplete point cloud of berry surfaces \citep{du_instance_2023}. 
 Therefore, point cloud instance segmentation can only capture partial information rather than that of whole berries.
-To address \replaced{this issue}{the issue of partial point clouds,} and consequently an underestimation of the berry traits, point cloud shape completion is one of the most commonly used solutions.
+To address this issue and consequently an underestimation of the berry traits, point cloud shape completion is one of the most commonly used solutions.
 Point cloud completion is the task of generating a complete 3D shape given partial point cloud input \citep{tesema_point_2024}. 
@@
 This encoder-decoder network was extended and optimized by \citet{blok_highthroughput_2025} for high-throughput 3D shape completion of potato tubers on a commercial harvester. 
-\deleted{Outside the agricultural domain, tang\_lakenet\_2022 proposed a point cloud completion network (Lake-net) for furniture model point cloud datasets.} 
 For grape berry application, the shape of the berry can be roughly approached by the deformation of a sphere or ellipsoid depending on the species. 
@@
 (3) a phenotyping module that extract berry phenotypic traits including radius and volume. 
-\replaced{The proposed pipeline was evaluated}{The novelty of our study is the research of this novel pipeline and its evaluation} on four different fresh grape species (Red, Green, Kyoho, and Shine Muscat Grape).
+The proposed pipeline was evaluated on four different fresh grape species (Red, Green, Kyoho, and Shine Muscat Grape).
 
@@
     \includegraphics[width=1\textwidth]{figures/Figure11.pdf}
-    \caption{Example of \deleted{visualization of the predicted complete }berry point cloud fitted to \replaced{its ellisoid surface}{the surface of an ellipsoid}.}
+    \caption{Example of berry point cloud fitted to its ellisoid surface.}
     \label{fig:raw16}
@@
 
-Suppose the point cloud of \replaced{a}{the} complete berry is denoted as $P_{complete}=\{P_i \mid i=1, \cdots,n\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in the 3D space, and $n$ denotes the number of points.
+Suppose the point cloud of a complete berry is denoted as $P_{complete}=\{P_i \mid i=1, \cdots,n\}$, where $p_i=(x_i,y_i,z_i)$ denotes a point in the 3D space, and $n$ denotes the number of points. 
 In this paper, it is fitted to an ellipsoid surface with three unequal long axes by the least squares method, and the function is shown in Equation~(\ref{eq:6}).
@@
 
-To validate the accuracy of extracted morphological traits, the 12 validation bunches \added{with 108 berry samples} were \replaced{selected.
+To validate the accuracy of extracted morphological traits, the 12 validation bunches with 108 berry samples were selected.
 The berries were first scanned while still attached to bunch (Fig.~\ref{fig:raw9}a2).
@@
 Finally get ellipsoidal surface fitting results as prediction values.
-}{ used after instance berry segmentation and berry completion (refer to Section~\ref{sec:22})}
-\deleted{The radius and volume of the 108 samples were calculated.} 
-For ground truth measurement, \replaced{we separated berries from the bunch to get complete scans of corresponding berry (Fig.~\ref{fig:raw9}b1).
+For ground truth measurement, we separated berries from the bunch to get complete scans of corresponding berry (Fig.~\ref{fig:raw9}b1).
 Then applied the ellipsoidal surface fitting to these completely scans.
-}{we used the values of the radius and volume of the individual complete berry from the completed point clouds.}
 
@@
 \label{sec:251}
-In this paper, we used average precision AP as the evaluation metric for berry instance segmentation, similar to the original paper of \added{SoftGroup} \citep{vu_softgroup_2022}.
-The average APs with IoU (Intersection over Union) ranging from 50\% to 95\% in steps of 5\% were used and noted as \replaced{mAP@[.5:.95]}{AP@50:5:95}.
+In this paper, we used average precision AP as the evaluation metric for berry instance segmentation, similar to the original paper of SoftGroup \citep{vu_softgroup_2022}.
+The average APs with IoU (Intersection over Union) ranging from 50\% to 95\% in steps of 5\% were used and noted as mAP@[.5:.95].
 
@@
 \subsection{Berry Instance Segmentation Results}
-\label{sec: insegresults}
+\label{sec:insegresults}
 
-\deleted{The bunch point cloud segmentation results are summarized in Table~\ref{tbl:3} }. 
-% table 3
-% \begin{table}[h]
-%     \centering
-%     \caption{Instance berry segmentation results from whole bunch}
-%     \begin{tabular}{ccc}
-%         \hline
-%         \textbf{Class} & \textbf{mAP@[.5:.95]} \\
-%         \hline
-%         Berry & 0.995 \\
-%         Stem & 0.941 \\
-%         \hline
-%     \end{tabular}
-%     \label{tbl:3}
-% \end{table}
-\deleted{As can be seen from Table~\ref{tbl:3}, The value of the point cloud instance segmentation for the berry category is over 99\%, which shows a high accuracy of the berry segmentation from the bunch.}
-
-\added{The mAP@[.5:.95] values of berry and stem class are 0.995 and 0.941, respectively, which }showed a high accuracy of the berry segmentation from the bunch.
-\added{Since mAP@[.5:.95] is a strict evaluation metric, it represents the mean values of Average Precision (AP) scores calculated from AP50 to AP95 at 5\% IoU intervals}.
-\added{Compared to other studies, \citet{ni_threedimensional_2021} reported that their proposed segmentation network achieved a mAP@[.5:.95] of 0.877 on their testing dataset, while \citet{du_instance_2023} achieved a mAP[.5:.95] of 0.657 and an AP50 of 0.952.}
-\added{In our study, the AP50 value exceeded 0.999, with both recall and precision values at this level also over 0.999.}
-\added{When compared to traidtional berry semgnetation algorithms, \citet{rose_automated_2016} reported a mean recall of 0.776 and precision of 0.978;}
+The mAP@[.5:.95] values of berry and stem class are 0.995 and 0.941, respectively, which showed a high accuracy of the berry segmentation from the bunch.
+Since mAP@[.5:.95] is a strict evaluation metric, it represents the mean values of Average Precision (AP) scores calculated from AP50 to AP95 at 5\% IoU intervals.
+Compared to other studies, \citet{ni_threedimensional_2021} reported that their proposed segmentation network achieved a mAP@[.5:.95] of 0.877 on their testing dataset, while \citet{du_instance_2023} achieved a mAP[.5:.95] of 0.657 and an AP50 of 0.952.
+In our study, the AP50 value exceeded 0.999, with both recall and precision values at this level also over 0.999.
+When compared to traidtional berry semgnetation algorithms, \citet{rose_automated_2016} reported a mean recall of 0.776 and precision of 0.978;
 The results of four fresh grapes for bunch point cloud segmentation are visualized in Fig.~\ref{fig:raw13}.
-\added{According that figure, we can also see an almost perfect instance berry segmentation results.}
+According that figure, we can also see an almost perfect instance berry segmentation results.
 
@@
 \subsection{Berry Self-Supervised Completion Results}
+\label{sec:32}
 
 The berry point cloud completion experiments are divided into two parts according to the different phases of the network: 
-the results of the self-supervised training \added{(Test)} and the results of the practical application \added{(Inference)}.
-\replaced{As}{The experimental results of GrapeCPNet compared to other point cloud completion algorithms are} shown in Table~\ref{tbl:4}, 
+the results of the self-supervised training (Test) and the results of the practical application (Inference).
+As shown in Table~\ref{tbl:4}, 
 GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the comparative algorithms.
@@
     \centering
-    \caption{\replaced{Comparing proposed method with}{Experimental results of} different completion networks \deleted{based on self-supervised training} for berry point cloud.
-Best performing results are visualized in bold.}
+    \caption{Comparing proposed method with different completion networks for berry point cloud. Best performing results are visualized in bold.}
     \begin{tabular}{cccccc}
@@
     \includegraphics[width=1\textwidth]{figures/Figure13.pdf}
-    \caption{Example of four fresh grape berry point cloud completion results: in subfigures a-d, the left side shows \replaced{incomplete berry while}{the incomplete berry point cloud obtained from the segmentation of the bunch, and} the right side shows the completion results using \added{proposed} GrapeCPNet \deleted{under the self-supervised training-based method}.}
+    \caption{Example of four fresh grape berry point cloud completion results: in subfigures a-d, the left side shows incomplete berry while the right side shows the completion results using proposed GrapeCPNet .}
     \label{fig:raw14}
@@
 
-The radius parameters were calculated by fitting the berry to the surface of an ellipsoid\deleted{, as shown in Figure~\ref{fig:raw16}}.
-From Figure~\ref{fig:raw17}, it can be seen that the proposed method achieves an average $R^2$ of 0.86 \added{and average MAE of 0.608 mm} for the three axis lengths of the four species of grape. 
+The radius parameters were calculated by fitting the berry to the surface of an ellipsoid.
+From Figure~\ref{fig:raw17}, it can be seen that the proposed method achieves an average $R^2$ of 0.86 and average MAE of 0.608 mm for the three axis lengths of the four species of grape. 
 This result can be dissected as follows:
@@
     \caption{Experimental results of axis length calculation for four species of fresh grape.
-From (a)-(d): Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape, \deleted{and from (1)-(3): the calculation of the long, middle, and short axis, }respectively.
-\added{The ground truth values are obtained by completely scanning berries that were separated from the bunch (Fig.~\ref{fig:raw9}b1); The predicted values are obtained from our proposed self-supervised completion method, which addresses incomplete scans of berries that occur due to occlusion while they were still attached to the bunch (Fig.~\ref{fig:raw9}a2).}}
+From (a)-(d): Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape, respectively.
+The ground truth values are obtained by completely scanning berries that were separated from the bunch (Fig.~\ref{fig:raw9}b1); The predicted values are obtained from our proposed self-supervised completion method, which addresses incomplete scans of berries that occur due to occlusion while they were still attached to the bunch (Fig.~\ref{fig:raw9}a2).}
     \label{fig:raw17}
@@
 Among them, Kyoho Grape achieved the best results due to its spherical berries that are not too densely clustered and the lower difficulty in berry completion and morphology fitting. 
-Secondly, Red Grape and Green Grape both present a typical ellipsoid shape, but the \replaced{Red}{latter} is less precise than the \replaced{Green}{former} due to its \replaced{larger}{greater} ratio of long axis to short axis, which provides a more complex presentation.
-\added{As also reported by \citet{schneider_predicting_2020}, the mean length-to-width ratio of Green Grape is 21.18mm to 18.75mm, while for Red Grape, it is 24.11mm to 18.41mm.}
+Secondly, Red Grape and Green Grape both present a typical ellipsoid shape, but the Red is less precise than the Green due to its larger ratio of long axis to short axis, which provides a more complex presentation.
+As also reported by \citet{schneider_predicting_2020}, the mean length-to-width ratio of Green Grape is 21.18mm to 18.75mm, while for Red Grape, it is 24.11mm to 18.41mm.
 Shine-Muscat Grape had the lowest precision, which was due to the fact that its berry grows tightly and occlude each other heavily, making it harder to accurately complete its shape.
@@
 For the berry volume calculation of the four species, the $R^2$ was 0.97, and the MAE was 0.3842 $cm^3$.
-\deleted{Indicating a high precision for predicting the volume of the different species.}
 
@@
     \caption{Experimental results of berry volume calculation.
-\added{The ground truth values are obtained by completely scanning berries that were separated from the bunch (Fig.~\ref{fig:raw9}b1); The predicted values are obtained from our proposed self-supervised completion method, which addresses incomplete scans of berries that occur due to occlusion while they were still attached to the bunch (Fig.~\ref{fig:raw9}a2).}}
+The ground truth values are obtained by completely scanning berries that were separated from the bunch (Fig.~\ref{fig:raw9}b1); The predicted values are obtained from our proposed self-supervised completion method, which addresses incomplete scans of berries that occur due to occlusion while they were still attached to the bunch (Fig.~\ref{fig:raw9}a2).}
     \label{fig:raw18}
@@
 
-The experimental results showed that the proposed method achieved \added{both} high accuracy in the calculation of the radius \added{and volumes} of different grape species.
-\added{In out study, we achieved an average $R^2$ of 0.86 and an average MAE of 0.608 mm across the three axis of berry, as well as an $R^2$ of 0.9689 and an MAE of 0.3842 $cm^3$ for berry volumes.}
-\added{By comparision, \citet[Fig.~4]{rist_highprecision_2018} reported $R^2$ values of 0.54, 0.85, and 0.83 for berry width, length, and volume, respectively.}
-\added{\citet{botturi_stewie_2023} reported a best-case MAE of 21.7mm for berry ratio estimataion using deep learning network on 2D images.}
-\added{Although the method by \citet{ni_threedimensional_2021} achieved a lower errors for volume estimataion (RMSE of 0.292 $cm^3$), it relies on sphere fitting that are primarily applicable to clustered, round fruits.}
-\added{In contrast, our proposed method not only accounts for occluded areas but is also adaptable to fruits of varying shapes, if appropriate paired training data is available.}
+The experimental results showed that the proposed method achieved both high accuracy in the calculation of the radius and volumes of different grape species.
+In out study, we achieved an average $R^2$ of 0.86 and an average MAE of 0.608 mm across the three axis of berry, as well as an $R^2$ of 0.9689 and an MAE of 0.3842 $cm^3$ for berry volumes.
+By comparision, \citet[Fig.~4]{rist_highprecision_2018} reported $R^2$ values of 0.54, 0.85, and 0.83 for berry width, length, and volume, respectively.
+\citet{botturi_stewie_2023} reported a best-case MAE of 21.7mm for berry ratio estimataion using deep learning network on 2D images.
+Although the method by \citet{ni_threedimensional_2021} achieved a lower errors for volume estimataion (RMSE of 0.292 $cm^3$), it relies on sphere fitting that are primarily applicable to clustered, round fruits.
+In contrast, our proposed method not only accounts for occluded areas but is also adaptable to fruits of varying shapes, if appropriate paired training data is available.
 
@@
 % achievement and contribution of ths study
-In this paper, \replaced{an automated deep learning pipeline for}{a method for the automatic} acquisition of 3D phenotypic traits of grape \added{bunch} was presented to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end analysis.
-\replaced{As a major contribution}{Moreover}, to address the problem of incomplete point clouds of berries due to occlusion, we introduced GrapeCPNet, a berry point cloud completion model based on the self-supervised training method.
-\deleted{Based on the point cloud of a grape bunch, a combination of deep learning point cloud processing algorithms realized the counting of the number of berries, the calculation of berry radius, and berry volume.
-}
+In this paper, an automated deep learning pipeline for acquisition of 3D phenotypic traits of grape bunch was presented to address the problems of high labor cost, poor accuracy, and inability to realize end-to-end analysis.
+As a major contribution, to address the problem of incomplete point clouds of berries due to occlusion, we introduced GrapeCPNet, a berry point cloud completion model based on the self-supervised training method.
 
 % revisiting background to reboot reader
-\added{Grape berry counting and size estimation plays a critical role in vineyard management and yield prediction.}
-\added{By using common digital cameras alongside deep learning networks, several studies have achieved automatic berry detection and instance segmentation \citep{jadhav_comparative_2021, chen_instance_2023}, and then forward the analyses of geometry traits and yield estimation \citep{quinones_gcnet_2025}.}
-\added{However, because of the dense and compact arrangement of berries within a grape bunch, some portions are often occluded and not visible when relying solely on single 2D images.}
-\added{To reduce the effects of occlusion, \citet{du_instance_2023} reported accurate berry counting estimations by correlating image-based detections with ground measurements.}
-\added{However, applying this method to other vineyards requires extensive, labor-intensive ground measurements}
-\added{Similarly, \citet{botturi_stewie_2023} attempted to extract feature maps, such as berry radii, directly from deep networks applied to 2D images}
-\added{Despite this approach, it still suffers from information loss and resulted in a high MAE of 21.7 mm.}
-\added{Applying multi-view images for 3D reconstruction can significantly reduce the extent of occlusion caused by viewpoint limitations.}
-\added{But unlike 2D images, which have well-structured data in the form of organized pixel matrices, the unordered nature of points in a 3D point cloud introduces significant challenges.}
-\added{Meanwhile, the inner portion of berry is still invisible, only the surface of exposed berry surfaces can be scanned or reconstructed.}
-\added{This complicates the algorithm design for individual berry segmentation and accurate berry size estimation.}
+Grape berry counting and size estimation plays a critical role in vineyard management and yield prediction.
+By using common digital cameras alongside deep learning networks, several studies have achieved automatic berry detection and instance segmentation \citep{jadhav_comparative_2021, chen_instance_2023}, and then forward the analyses of geometry traits and yield estimation \citep{quinones_gcnet_2025}.
+However, because of the dense and compact arrangement of berries within a grape bunch, some portions are often occluded and not visible when relying solely on single 2D images.
+To reduce the effects of occlusion, \citet{du_instance_2023} reported accurate berry counting estimations by correlating image-based detections with ground measurements.
+However, applying this method to other vineyards requires extensive, labor-intensive ground measurements
+Similarly, \citet{botturi_stewie_2023} attempted to extract feature maps, such as berry radii, directly from deep networks applied to 2D images
+Despite this approach, it still suffers from information loss and resulted in a high MAE of 21.7 mm.
+Applying multi-view images for 3D reconstruction can significantly reduce the extent of occlusion caused by viewpoint limitations.
+But unlike 2D images, which have well-structured data in the form of organized pixel matrices, the unordered nature of points in a 3D point cloud introduces significant challenges.
+Meanwhile, the inner portion of berry is still invisible, only the surface of exposed berry surfaces can be scanned or reconstructed.
+This complicates the algorithm design for individual berry segmentation and accurate berry size estimation.
 
 % revisit gap/aim/method
-\added{For individual berry segmentation, early studies relied on the circular characteristics of the visible portions of berries for segmentation.}
-\added{Building on the work of \citet{schnabel_efficient_2007}, who introduced point cloud shape detection using RANSAC, researchers were able to cluster partial berries based on their rounded shapes \citep{scholer_automated_2015, rist_highprecision_2018, schneider_predicting_2020}.}
-\added{However, this feature-based approach performs well only in sparse grape arrangements and proves ineffective in more complex, dense conditions.}
-\added{The reliance on manually designed features for algorithm development has now reached its limitations.}
-\added{With advancements in machine learning, the focus has shifted to a data-driven era, where algorithms can learn complex feature patterns automatically.}
-\added{For instance, \citet{rose_automated_2016} applied machine learning to distinguish features between grape berry clusters and background leaves automatically.}
-\added{Similarly, \citet{ni_threedimensional_2021} implemented a two-step approach by first using mature 2D instance segmentation techniques on 2D images and then projecting the resulting segmentation masks onto reconstructed 3D models to complete the challenging task of 3D instance segmentation.}
-\added{In another approach, \citet{luo_3d_2023} Mask R-CNN for 2D image segmentation and projected the results onto RGB-D point clouds.}
-\added{The normal directions derived from the point clouds were then packed as an additional feature in the PointNet++ network for point cloud segmentation.}
-\added{In this study, we applied the state-of-the-art point cloud segmentation network, SoftGroup \citep{vu_softgroup_2022} directly to the problem.}
-\added{The primary time-consuming work of our approach was the annotation of 3D data for instance segmentation.}
-\added{Compared to similar studies on grape berries, our proposed method demonstrated superior performance, achieving the best results among the reviewed methods (Subsection~\ref{sec: insegresults}).}
+For individual berry segmentation, early studies relied on the circular characteristics of the visible portions of berries for segmentation.
+Building on the work of \citet{schnabel_efficient_2007}, who introduced point cloud shape detection using RANSAC, researchers were able to cluster partial berries based on their rounded shapes \citep{scholer_automated_2015, rist_highprecision_2018, schneider_predicting_2020}.
+However, this feature-based approach performs well only in sparse grape arrangements and proves ineffective in more complex, dense conditions.
+The reliance on manually designed features for algorithm development has now reached its limitations.
+With advancements in machine learning, the focus has shifted to a data-driven era, where algorithms can learn complex feature patterns automatically.
+For instance, \citet{rose_automated_2016} applied machine learning to distinguish features between grape berry clusters and background leaves automatically.
+Similarly, \citet{ni_threedimensional_2021} implemented a two-step approach by first using mature 2D instance segmentation techniques on 2D images and then projecting the resulting segmentation masks onto reconstructed 3D models to complete the challenging task of 3D instance segmentation.
+In another approach, \citet{luo_3d_2023} Mask R-CNN for 2D image segmentation and projected the results onto RGB-D point clouds.
+The normal directions derived from the point clouds were then packed as an additional feature in the PointNet++ network for point cloud segmentation.
+In this study, we applied the state-of-the-art point cloud segmentation network, SoftGroup \citep{vu_softgroup_2022} directly to the problem.
+The primary time-consuming work of our approach was the annotation of 3D data for instance segmentation.
+Compared to similar studies on grape berries, our proposed method demonstrated superior performance, achieving the best results among the reviewed methods (Subsection~\ref{sec:insegresults}).
 
-\added{For berry completetion by deep learning, the most difficult and time-consuming work is preparing the paired training dataset with complete and incomplete point cloud.}
-\added{As our previous studies conducted for potato tuber completion networks \citep{blok_highthroughput_2025}, a distinguishable pin was used as reference point for pairing complete tubers by photogrammetry and incomplete tubers by RGBD camera.}
-\added{Then the pin-guided point cloud matching algorithm is applied to calculate transformation matrix between paired dataset.}
-\added{The potato tuber is single object with clear texture and shape variances, thus pairing through two different scans by two sensors is not too difficult.}
-\added{For the grape berry, it is super rounded with weak texture features and strong reflectance, making the paired data super challenging.}
-\added{Thus, the previous pin-guided point cloud paring methods for collection paired data does not work.}
+For berry completion using deep learning, the most challenging and time-consuming task is preparing the paired training datasets of complete and incomplete point clouds.
+In our previous work on potato tuber completion networks \citep{blok_highthroughput_2025}, a distinguishable pin was used as a reference point to align the complete tuber scans obtained via photogrammetry with the incomplete tuber scans captured using an RGB-D camera.
+A pin-guided point cloud matching algorithm was then applied to calculate the transformation matrix for pairing the datasets.
+Potato tubers, being single objects with clear textures and shape variation, presented fewer challenges when aligning data collected by two different types of sensors.
+However, grape berries pose a significantly more difficult problem due to their highly rounded shapes, weak texture features, and strong reflectance, which complicates the creation of paired data.
+As a result, the previous pin-guided point cloud pairing method used for potato tuber datasets is not effective for grape berries.
+Thus, we simulated random sphere cutting on the complete berry point clouds to generate thousands of paired incomplete point clouds, as described in Subsection~\ref{sec:berrycut}.
+As demonstrated in Subsection~\ref{sec:32}, these automatically generated paired training datasets were successfully used to train several completion models (Table~\ref{tbl:4}).
+We have found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
+Considering the agricultural plant completion task, our proposed GrapeCPNet, which combines centroid-based sparse completion with diffusion-based dense completion, outperformed other networks in terms of performance.
+We found that GrapeCPNet performed a little bit worse in the case of strange berry shapes, such as drop-shaped.
+We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion.
+
+% challenges, limitations and future works.
+Another limitation of this study is that it focused on a single berry bunch in a controlled environment.
+The noise in the data is also related to the effectiveness of the method proposed in this paper.
+For practical applications in vineyards, collecting the same point cloud quality as that achieved in controlled indoor environments can be challenging, and multi-view data collection may not be as efficient.
+How to effectively implement the method in practical application scenarios is another issue to be considered in future research.
+To increasing data collection efficiency, devices such as RGB-D cameras \citep{blok_highthroughput_2025}, fisheye cameras \citep{tamura_unsupervised_2025}, or even 360 cameras can be used.
+Moreover, as in previous studies \citep{rose_automated_2016, luo_3d_2023}, investigating methods to segment individual grape bunches directly from vineyard scans using deep learning techniques should be an area of future exploration.
+Additionally, \citet[Fig.~9]{scholer_automated_2015} successfully demonstrated the construction of virtual 3D models of grape bunches, including the hidden branching architecture. 
+By collecting time-series growth data, the branching structure could potentially be captured during early stages of thinning, as suggested by \citep{du_instance_2023}.
+Such data could enable studies on growth prediction for optimizing harvesting times and assessments of branching structure deviations within crowded berry bunches.
+Finally, applying the latest procedural computer graphics (CG) modeling techniques or functional-structural plant models represents another promising approach to advancing practical applications in this field.
 
 % the achievement / impact of study / potential applications.
-\deleted{As discussion point, we found that GrapeCPNet was not effective in the case of complex berry appearance, such as drop-shaped.}
-
-% future works.
-We have found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
-We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion. 
-In addition, the noise in the data is also related to the effectiveness of the method proposed in this paper. 
-How to implement the method in practical application scenarios, such as RGB-D collected point cloud data, is another issue to be considered in future research. \citet{blok_highthroughput_2025}
-
 Through the method proposed in this paper, the automated acquisition of 3D phenotypic traits of grape can be realized, which is of great significance in the field of agricultural production and scientific research.
@@
 
-\added{In this study, we proposed a deep-learning-based pipeline for processing 3D phenotyping grape bunches reconstructed by photogrammetry.}
-\added{The major contribution is the self-supervised completion network, named GrapeCPNet, designed to address the problem of missing parts in berries occluded within grape bunches with few manual annotations.}
-\added{We utilized state-of-the-art, data-driven deep learning approaches to address these challenges.}
-\added{First, the SoftGroup network, utilizing segmentation annotations from 8 grape bunches, was used to train a data-driven berry instance segmentation model.}
-% \added{By randomly producing missing areas from complete berries, we automatically generated large number of training data for completion tasks.}
-\added{The proposed GrapeCPNet also achieved better performance than existing completion networks, with Precision of 0.729, Recall of 0.772 and F-score of 0.751.}
-\added{The ellipsoid surface fitting, used to calculate three axis lengths and volumes, achieved an average $R^2$ of 0.86 and 0.97 respectively, when comparing completed berries with their ground truth.}
-\added{This study clearly demonstrates the potential of using data-drive strategies with minimal annotation effort to address the 3D occlsuion challenge in agricultural applications.}
-\added{Although this network has only been tested on grape bunches collected in a controlled indoor environment, the proposed deep learning pipelines and training data generation approach have broad potential applications for in-field vineyards and even other crops in the future.}
+In this study, we proposed a deep-learning-based pipeline for processing 3D phenotyping grape bunches reconstructed by photogrammetry.
+The major contribution is the self-supervised completion network, named GrapeCPNet, designed to address the problem of missing parts in berries occluded within grape bunches with few manual annotations.
+We utilized state-of-the-art, data-driven deep learning approaches to address these challenges.
+First, the SoftGroup network, utilizing segmentation annotations from 8 grape bunches, was used to train a data-driven berry instance segmentation model.
+The proposed GrapeCPNet also achieved better performance than existing completion networks, with Precision of 0.729, Recall of 0.772 and F-score of 0.751.
+The ellipsoid surface fitting, used to calculate three axis lengths and volumes, achieved an average $R^2$ of 0.86 and 0.97 respectively, when comparing completed berries with their ground truth.
+This study clearly demonstrates the potential of using data-drive strategies with minimal annotation effort to address the 3D occlsuion challenge in agricultural applications.
+Although this network has only been tested on grape bunches collected in a controlled indoor environment, the proposed deep learning pipelines and training data generation approach have broad potential applications for in-field vineyards and even other crops in the future.
 
@@
 \section*{Funding}
-This study was partially supported by the National Natural Science Foundation of China (NSFC) Program 62276009 and the Japan Science and Technology Agency (JST) AIP Acceleration Research JPMJCR21U3, the Hokkaido Sarabetsu Village “Endowed Chair for Field Phenomics” project.
-
-% \section*{Acknowledgements}
-% We would like to thank ...
+This study was partially supported by the National Natural Science Foundation of China (NSFC) Program 62276009 and the Japan Science and Technology Agency (JST) AIP Acceleration Research JPMJCR21U3, the Hokkaido Sarabetsu Village ``Endowed Chair for Field Phenomics'' project.
 

### 2025-05-01 response2reviewer.tex
allow changes in response to reviewers

@@
 \usepackage{natbib}
+
+\usepackage[draft,commandnameprefix=ifneeded]{changes}
+\definechangesauthor[color=red]{R1}
+\definechangesauthor[color=blue]{R2}
 
@@
 \begin{reviewercomment}
-    Line 159: What does "instance-level" mean? Which platform, software, or tool was used for labeling?
+    Line 159: What does "instance-level" mean?
+\end{reviewercomment}
+
+\response{
+    We appreciate the reviewer's comment.
+The term "instance-level" refers to the individual segmentation of each grape berry and stem in the point cloud, where each instance is distinctly labeled and separated from others.
+We have clarified this definition in the revised manuscript.
+}
+
+\manuscript{
+    In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) as shown in}{at the instance-level}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{reviewercomment}
+    Which platform, software, or tool was used for labeling?
 \end{reviewercomment}

### 2025-05-01 main.tex
allow changes in response to reviewers

@@
 \usepackage[draft]{changes}
+\definechangesauthor[color=red]{R1}
+\definechangesauthor[color=blue]{R2}
 
@@
 
-In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was labeled at the instance-level (Fig.~\ref{fig:raw11}). 
+In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) as shown in}{at the instance-level} Fig.~\ref{fig:raw11}.
 This paper collected and labeled eight bunches for each of the four species (in total 32 bunches). 

### 2025-05-02 response2reviewer.tex
update response template & review point 1

@@
 \usepackage{geometry}
+\usepackage{float}  % 强制后续文本不超过前面的图片，\begin{figure}[H]
+
+\usepackage[ruled]{algorithm2e}  % algorithm
 
 \usepackage{natbib}
+
+% 关联主文档用来索引引用
+\usepackage{xr}
+\externaldocument{main}
 
@@
 
-\section{Reviewer \#1}
-\setcounter{reviewercomment}{0}
+% Response to Editor
+\editor
 
+% Reviewer 1
+\reviewer
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Reviewer \#2}
-
+% Reviewer 2
+\reviewer
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \manuscript{
-    In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) as shown in}{at the instance-level}
+    In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) as shown in}{at the instance-level} Fig.~\ref{fig:raw11}.
 }
@@
 
+\todoblock{
+    Confirm with Guoqiang which tool for labeling
+}
+
 \manuscript{
-    ...
+
 }
@@
 \response{
-    ...
+    We appreciate the reviewer's question. 
+    The term "selection area" refers to the regions where portions are removed from the complete berry point cloud to simulate occlusion. 
+    To improve clarity, we have revised the terminology to "removal sphere regions" throughout the manuscript, as this more accurately describes the spherical regions where point cloud removal occurs during the incomplete data generation process.
 }
@@
 \manuscript{
-    ...
+    The inputs include a single complete berry point cloud and the maximum number of \replaced[id=R2]{removal sphere regions}{ selection areas (5 in this paper)}. 
 }
+
+\manuscript{
+    Supervised point cloud completion training requires the incomplete-complete data pairs of the same object to build a mapping relationship.
+    The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
+    In this paper, \added[id=R2]{to decrease the labor cost of such data pair generation,} the complete grapes were obtained by single berry reconstruction (Section~\ref{sec:212}) and were used as ground truth.
+    While the incomplete grapes were \replaced[id=R2]{generated by removing parts overlapped with randomly generated 3D sphere regions}{cut} from the complete grapes \deleted[id=R2]{following characteristic of occlusion and were used as training inputs.}
+    \deleted[id=R2]{This data pair generation strategy alleviated the data annotation efforts.}
+    \deleted[id=R2]{Based on the incomplete characteristics, we developed a selection method to generate the incomplete berry point cloud from the complete berry point cloud.}
+}
+
+\manuscript{
+    The pseudo-code of our proposed \added[id=R2]{removal} algorithm is shown in Algorithm \ref{alg:1}. 
+    The inputs include a single complete berry point cloud and the maximum number of \replaced[id=R2]{removal sphere regions}{selection areas (5 in this paper)}. 
+    The output is a selected incomplete berry point cloud. 
+    First, the single complete berry point cloud was normalized and centralized (Fig.~\ref{fig:raw12}a). 
+    Second, randomly \replaced[id=R2]{choose the number of removal sphere regions for current grape berry}{select the number of cuts}, with a maximum of five \replaced[id=R2]{removal sphere regions}{cuts as} specified in this paper.
+    Then, for each \replaced[id=R2]{removel sphere region,}{loop of selection, a 3D sphere model was generated in the space to collide with the berry point cloud, and} the collision portion \added[id=R2]{with the berry point cloud} was removed \deleted[id=R2]{to complete the operation}.
+    The \deleted[id=R2]{maximum} center and radius parameters of the 3D \replaced[id=R2]{removal sphere region}{sphere model} were \replaced[id=R2]{randomly}{manually} set according to the \added[id=R2]{normalized} berry size.
+    In this paper, we set \replaced[id=R2]{the sphere center positions within a random range of $\pm 0.75$ relative to the grape center, and the sphere radii within a random range of 0 to 0.25.}{a maximum of 0.75 for the center offsets and 0.25 for the radius offsets.}
+    \replaced[id=R2]{The incomplete berry point cloud was generated as training data by iteratively removing spherical regions.}{Continue the previous selection looping until the limits are met.
+The selected incomplete point cloud was saved from each loop as training data} (Fig.~\ref{fig:raw12}b).
+}
+
+\begin{algorithm}
+    \caption{The selection method for generating training data of incomplete berries}
+    \label{alg:1}
+    \KwData{$P_C$ \tcp{one complete berry point cloud}}
+    \KwData{$n$ \tcp{\added[id=R2]{number of incomplete berries to generate}}}
+    \KwResult{$P_{\text{output}} = \{P_{o_i} \mid i = 1, \cdots, n\}$ \tcp{incomplete berry point cloud sets} }
+
+    $\hat{P}_C \gets \text{Normalize}(\text{Translate}(P_C))$ \tcp{center to $(0,0,0)$, range to $[-0.5m, 0.5m]$}
+    \For{$i = 0 \to n$}{
+        set $m = \text{random}\{1,2,3,4,5\}$ \tcp{\added[id=R2]{number of removal sphere regions}}
+        $P_{o_i} \gets copy(\hat{P}_C)$ \tcp{initialize one output}
+        \For{$j = 0 \to m$}{
+            set $O = \{(x_o, y_o, z_o) \mid x, y, z \in \text{random}[-0.75, 0.75]\}$ \tcp{\added[id=R2]{removal sphere} center} 
+            set $R = \text{random}[0.25, 0.75]$ \tcp{\added[id=R2]{removal sphere} radius}
+            set $M_S \gets \text{sphere}(O, R)$ \tcp{generate \added[id=R2]{removal sphere region}}
+            $P_{o_i} = P_{o_i} - P_{o_i} \cap M_S$ \tcp{remove overlap \added[id=R2]{within sphere region}}
+        }
+        $P_{\text{output}_i} \gets P_{o_i}$ \tcp{add to output set}
+    }
+\end{algorithm}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/Figure9.pdf}
+    \caption{\replaced[id=R2]{Workflow of automatic paired training dataset generation}{Example of dataset composition} for the \deleted[id=R2]{self-supervised training-based method of the} berry point cloud completion network.}
+\end{figure}
 

### 2025-05-02 main.tex
update response template & review point 1

@@
 \usepackage{cite}
-\usepackage[ruled]{algorithm2e}
+\usepackage[ruled]{algorithm2e}  % algorithm
 \usepackage{amsmath,amssymb,amsfonts}
@@
 Supervised point cloud completion training requires the incomplete-complete data pairs of the same object to build a mapping relationship.
-In this paper, the complete grapes were obtained by single berry reconstruction (Section~\ref{sec:212}) and were used as ground truth, while the incomplete grapes were cut from the complete grapes following characteristic of occlusion and were used as training inputs.
-This data pair generation strategy alleviated the data annotation efforts. The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
-Based on the incomplete characteristics, we developed a selection method to generate the incomplete berry point cloud from the complete berry point cloud .
+The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
+In this paper, \added[id=R2]{to decrease the labor cost of such data pair generation,} the complete grapes were obtained by single berry reconstruction (Section~\ref{sec:212}) and were used as ground truth.
+While the incomplete grapes were \replaced[id=R2]{generated by removing parts overlapped with randomly generated 3D sphere regions}{cut} from the complete grapes \deleted[id=R2]{following characteristic of occlusion and were used as training inputs.}
+\deleted[id=R2]{This data pair generation strategy alleviated the data annotation efforts.}
+\deleted[id=R2]{Based on the incomplete characteristics, we developed a selection method to generate the incomplete berry point cloud from the complete berry point cloud.}
 
@@
 
-The pseudo-code of our proposed algorithm is shown in Algorithm \ref{alg:1}. 
-The inputs include a single complete berry point cloud and the maximum number of selection areas (5 in this paper). 
-The output is a selected incomplete berry point cloud. First, the single complete berry point cloud was normalized and centralized (Fig.~\ref{fig:raw12}a). 
-Second, randomly select the number of cuts, with a maximum of five cuts as specified in this paper. 
-Then, for each loop of selection, a 3D sphere model was generated in the space to collide with the berry point cloud, and the collision portion was removed to complete the operation. 
-The maximum center and radius parameters of the 3D sphere model were manually set according to the berry size. 
-In this paper we set a maximum of 0.75 for the center offsets and 0.25 for the radius offsets. 
-Continue the previous selection looping until the limits are met. The selected incomplete point cloud was saved from each loop as training data (Fig.~\ref{fig:raw12}b).
+The pseudo-code of our proposed \added[id=R2]{removal} algorithm is shown in Algorithm \ref{alg:1}. 
+The inputs include a single complete berry point cloud and the maximum number of \replaced[id=R2]{removal sphere regions}{ selection areas (5 in this paper)}. 
+The output is a selected incomplete berry point cloud. 
+First, the single complete berry point cloud was normalized and centralized (Fig.~\ref{fig:raw12}a). 
+Second, randomly \replaced[id=R2]{choose the number of removal sphere regions for current grape berry}{select the number of cuts}, with a maximum of five \replaced[id=R2]{removal sphere regions}{cuts as} specified in this paper.
+Then, for each \replaced[id=R2]{removel sphere region,}{loop of selection, a 3D sphere model was generated in the space to collide with the berry point cloud, and} the collision portion \added[id=R2]{with the berry point cloud} was removed \deleted[id=R2]{to complete the operation}.
+The \deleted[id=R2]{maximum} center and radius parameters of the 3D \replaced[id=R2]{removal sphere region}{sphere model} were \replaced[id=R2]{randomly}{manually} set according to the \added[id=R2]{normalized} berry size.
+In this paper, we set \replaced[id=R2]{the sphere center positions within a random range of $\pm 0.75$ relative to the grape center, and the sphere radii within a random range of 0 to 0.25.}{a maximum of 0.75 for the center offsets and 0.25 for the radius offsets.}
+\replaced[id=R2]{The incomplete berry point cloud was generated as training data by iteratively removing spherical regions.}{Continue the previous selection looping until the limits are met.
+The selected incomplete point cloud was saved from each loop as training data} (Fig.~\ref{fig:raw12}b).
 
@@
     \KwData{$P_C$ \tcp{one complete berry point cloud}}
-    \KwData{$n$ \tcp{generate incomplete berries number}}
+    \KwData{$n$ \tcp{\added[id=R2]{number of incomplete berries to generate}}}
     \KwResult{$P_{\text{output}} = \{P_{o_i} \mid i = 1, \cdots, n\}$ \tcp{incomplete berry point cloud sets} }
@@
     \For{$i = 0 \to n$}{
-        set $m = \text{random}\{1,2,3,4,5\}$ \tcp{select incomplete single berry $m$ times}
+        set $m = \text{random}\{1,2,3,4,5\}$ \tcp{\added[id=R2]{number of removal sphere regions}}
         $P_{o_i} \gets copy(\hat{P}_C)$ \tcp{initialize one output}
         \For{$j = 0 \to m$}{
-            set $O = \{(x_o, y_o, z_o) \mid x, y, z \in \text{random}[-0.75, 0.75]\}$ \tcp{center} 
-            set $R = \text{random}[0.25, 0.75]$ \tcp{radius}
-            set $M_S \gets \text{sphere}(O, R)$ \tcp{generate sphere model}
-            $P_{o_i} = P_{o_i} - P_{o_i} \cap M_S$ \tcp{remove overlap with sphere model}
+            set $O = \{(x_o, y_o, z_o) \mid x, y, z \in \text{random}[-0.75, 0.75]\}$ \tcp{\added[id=R2]{removal sphere} center} 
+            set $R = \text{random}[0.25, 0.75]$ \tcp{\added[id=R2]{removal sphere} radius}
+            set $M_S \gets \text{sphere}(O, R)$ \tcp{generate \added[id=R2]{removal sphere region}}
+            $P_{o_i} = P_{o_i} - P_{o_i} \cap M_S$ \tcp{remove overlap \added[id=R2]{within sphere region}}
         }
@@
     \includegraphics[width=1\textwidth]{figures/Figure9.pdf}
-    \caption{Example of dataset composition for the self-supervised training-based method of the berry point cloud completion network.}
+    \caption{\replaced[id=R2]{Workflow of automatic paired training dataset generation}{Example of dataset composition} for the \deleted[id=R2]{self-supervised training-based method of the} berry point cloud completion network.}
     \label{fig:raw12}

### 2025-05-02 response2reviewer.tex
add cover letter and format change

@@
 
-\newcommand{\papertitle}{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}
-\newcommand{\journalname}{Computers and Electronics in Agriculture}
+\rfoot{Page \thepage}
 
-\rfoot{Page \thepage}
 \lettertitle{The Response to Reviewers}
-\journal{\journalname}
-\doi{COMPAG-D-25-00311R1}
-
-\title{\papertitle}
+\title{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}
 \author{
@@
 }
+\journal{Computers and Electronics in Agriculture}
+\doi{COMPAG-D-25-00311R1}
 
@@
 
-\BT{To Editor and Reviewers}
+%%%%%%%%%%%%%%%%
+% cover letter %
+%%%%%%%%%%%%%%%%
+\thedate
 
-\BL{Thank you for giving us the opportunity to submit a revised draft of the manuscript ``\papertitle'' for publication in the Journal of \journalname.
+Dear Editor:
+
+Thank you for giving us the opportunity to submit a revised draft of the manuscript ``\thetitle'' for publication in the Journal of \thejournal.
 We appreciate the time and effort that editors and the reviewers dedicated to providing feedback on our manuscript and are grateful for the insightful comments and valuable improvements to our paper.
@@
 Please see below, for a point-by-point response to the reviewers' comments and concerns.
-All page numbers refer to the revised manuscript file with tracked changes.}
+All page numbers refer to the revised manuscript file with tracked changes.
 
+Thank your for your consideration. I am looking forward to hearing from you soon.
+
+Sincerely,
+
+Wei Guo\\
+Associate professor\\
+Graduate School of Agricultural and Life Science\\
+The University of Tokyo, Tokyo, Japan\\
+Email: guowei@g.ecc.u-tokyo.ac.jp
+
+\vfill
+\textbf{Note:} To enhance the legibility of this response letter, all the editor's and reviewers' comments are typeset in boxes.
+Rephrased or added sentences are typeset in color.
+The respective parts in the manuscript are highlighted to indicate changes.
+
+%====================
 % Response to Editor
+%====================
 \editor
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{reviewercomment}
+    Overall, the paper is well structured with a clear goal,  and the authors provide insight to justify their design choices.
+However, I believe the paper will benefit from  more experiments, particularly on the instance segmentation and  completion parts.
+\end{reviewercomment}
+
+\response{Thanks for your positive comments.}
+
+%============
 % Reviewer 1
+%============
 \reviewer
@@
 
+%============
 % Reviewer 2
+%============
+
 \reviewer

### 2025-05-02 response2reviewer.tex
response to R2

@@
 \begin{reviewercomment}
-    Overall, the paper is well structured with a clear goal,  and the authors provide insight to justify their design choices.
-However, I believe the paper will benefit from  more experiments, particularly on the instance segmentation and  completion parts.
+    Thank you for submitting your manuscript to Computers and Electronics in Agriculture. 
+    I have received comments from reviewers on your manuscript. 
+    Your paper should become acceptable for publication pending suitable moderate revision and modification of the article in light of the appended reviewer comments.
+
+    When resubmitting your manuscript, please carefully consider all issues mentioned in the reviewers' comments, outline every change made point by point, and provide suitable rebuttals for any comments not addressed.
 \end{reviewercomment}
 
-\response{Thanks for your positive comments.}
+\response{
+    We sincerely appreciate the positive feedback from the editor and reviewers regarding our manuscript. 
+    We are grateful for the opportunity to revise our work based on the valuable comments received.
+
+    In this revision, we have:
+
+    1. Carefully addressed all reviewer comments point-by-point;\\
+    2. Provided detailed responses explaining each modification;\\
+    3. Made all necessary revisions to improve manuscript clarity and technical accuracy;\\
+    4. Included tracked changes in the revised manuscript for transparent review.
+
+    We believe these revisions have significantly strengthened the paper, and we appreciate the editor's and reviewers' time and constructive suggestions. 
+    Please find our point-by-point responses to each reviewer comment in the following sections.
+}
 
@@
 
-\response{Thanks for your positive comments.}
+\response{
+    We sincerely appreciate the reviewer's positive assessment of our study and manuscript. 
+    Regarding the suggestion for additional experiments, we agree that further validation would strengthen the work.
+
+    In response, we have:
+}
+
+\todoblock{
+    Summary of added experiment.
+}
 
@@
 \response{
-    ...
+    We thank the reviewer for raising this important methodological detail. 
+    The 3D point clouds were labeled using CloudCompare (v2.12.4), an open-source software for 3D point cloud and mesh processing.
 }
@@
 \todoblock{
-    Confirm with Guoqiang which tool for labeling
+    Confirm which tool for labeling
 }
@@
 \response{
-    ...
+    We appreciate the reviewer's attention to experimental rigor. 
+    To ensure fair comparison, all the comparing methods were conducted on our grape dataset under the same conditions.
+    We have added this clarification to the results part.
 }
@@
 \manuscript{
-    ...
+    GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the comparative algorithms \added[id=R2]{under the same condition of our grape dataset}.
 }
@@
 \begin{reviewercomment}
-    Occlusion  threshold: Is there a berry-occlusion threshold? For example, if less  than 50\% of a berry is visible, is it included? How are barely visible  berries handled?
+    Occlusion threshold: Is there a berry-occlusion threshold? 
+    For example, if less than 50\% of a berry is visible, is it included? How are barely visible berries handled?
 \end{reviewercomment}
@@
 \response{
-    ...
+    We thank the reviewer for this insightful question regarding occlusion handling. 
+    Our approach was designed specifically to address challenging occlusion scenarios.
+
+    We intentionally avoided setting visibility thresholds (e.g., 50\% cutoff) to maintain the applicable of proposed method.
+    As shown in Fig.~\ref{fig:raw12}b, after removing 4 sphere regions, the incomplete berry for network training can achieved nearly around 75\% occlusion. 
+    Thus, the GrapeCPNet is able to learn serever occlusions for barely visible berries.
+
+    However, we must also admit that when severely obscured, only partial information can be seen. 
+    The more obscured it is, the less information it provides. 
+    Therefore, errors inevitably increase when the berry is not in a regular shape.
+    As stated in the discussion part, we planed to taking prior knowledge of berry geometry to further improve the quality of completion.
 }
@@
 \manuscript{
-    ...
+    We found that GrapeCPNet performed a little bit worse in the case of strange berry shapes, such as drop-shaped \added[id=R2]{berries, particularly when berries were sereverly occluded}.
+    We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion. 
 }
@@
 \response{
-    ...
+    We appreciate the reviewer's insightful comment regarding wine grapes, which indeed represent a major segment of grape production. 
+    In our current study, we just focused on table grape varieties commonly found in Chinese markets.
+    Although they covered a wide range of cluster densities (from sparse to very dense) and berry sizes (20-35 cm axis length, as shown in Table~\ref{tbl:1} and Figure~\ref{fig:raw17}), 
+    we acknowledge that wine grapes typically have smaller berry sizes lower than 13-15 mm \citep{manso_wine_2021,melo_berry_2015}, these small sizes were not included in our dataset.
+
+    From a deep learning perspective, our model architecture should be capable of handling smaller wine grapes if provided with appropriate training data, as the fundamental detection principles remain similar regardless of grape variety.
+    Nevertheless, we agree that future work should specifically address wine grape detection through collaboration with U.S. researchers to: 
+    (1) collect wine grape datasets, and 
+    (2) evaluate whether models trained on table grapes can generalize well to the smaller wine grape berries without additional training.
+
+    We have added the previous points to the discussion parts.
 }
@@
 \manuscript{
-    ...
+    \added[id=R2]{
+        This study has another limitation: it focuses only on four table grapes, which are currently common and available in Chinese markets.
+        Although we examined a wide range of cluster densities (from sparse to very dense) and berry sizes (20-35 mm axis length, as shown in Table~\ref{tbl:1} and Figure~\ref{fig:raw17}),
+        the study did not include wine grapes, which account for over 60\% of U.S. grape production and typically have smaller berries and denser clusters.
+        As \citet{manso_wine_2021,melo_berry_2015} report, wine grape berries are often smaller than 13-15 mm, a size range not covered in our dataset.
+        From a deep learning perspective, our model architecture should be able to detect smaller wine grapes with appropriate training data, as the basic detection principles are similar across grape varieties.
+        Future work should involve collaboration with U.S.
+researchers to collect wine grape datasets and assess whether models trained on table grapes can generalize well to smaller wine grape berries without additional training.
     }
 
-\phantom{\cite{}} % 添加一个不可见的伪引用, 不会显示但能满足BibTeX要求避免无引用时报错
+    \replaced[id=R2]{Additionally, this study only}{Another limitation of this study is that it} focused on a single berry bunch in a controlled environment.
+}
+
+% \phantom{\cite{}} % 添加一个不可见的伪引用, 不会显示但能满足BibTeX要求避免无引用时报错
 \bibliographystyle{elsarticle-harv}
-\renewcommand{\bibsection}{} % 隐藏reference标题，如果需要则注释掉这一行
+% \renewcommand{\bibsection}{} % 隐藏reference标题，如果需要则注释掉这一行
 \bibliography{references}

### 2025-05-02 main.tex
response to R2

@@
 As shown in Table~\ref{tbl:4}, 
-GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the comparative algorithms.
+GrapeCPNet achieves the best results under the self-supervised training method in both the training phase and the application phase, better than the comparative algorithms \added[id=R2]{under the same condition of our grape dataset}.
 Fig.~\ref{fig:raw14} visualizes the shape completion result of GrapeCPNet on the incomplete berry segmented from the bunch in the application phase.
@@
 Considering the agricultural plant completion task, our proposed GrapeCPNet, which combines centroid-based sparse completion with diffusion-based dense completion, outperformed other networks in terms of performance.
-We found that GrapeCPNet performed a little bit worse in the case of strange berry shapes, such as drop-shaped.
+We found that GrapeCPNet performed a little bit worse in the case of strange berry shapes, such as drop-shaped \added[id=R2]{berries, particularly when berries were sereverly occluded}.
 We subsequently consider utilizing the prior knowledge of berry geometry to achieve more detailed morphological feature extraction and representation to improve the quality of completion.
@@
 % challenges, limitations and future works.
-Another limitation of this study is that it focused on a single berry bunch in a controlled environment.
+\added[id=R2]{
+    This study has another limitation: it focuses only on four table grapes, which are currently common and available in Chinese markets.
+    Although we examined a wide range of cluster densities (from sparse to very dense) and berry sizes (20-35 mm axis length, as shown in Table~\ref{tbl:1} and Figure~\ref{fig:raw17}),
+    the study did not include wine grapes, which account for over 60\% of U.S. grape production and typically have smaller berries and denser clusters.
+    As \citet{manso_wine_2021,melo_berry_2015} report, wine grape berries are often smaller than 13-15 mm, a size range not covered in our dataset.
+    From a deep learning perspective, our model architecture should be able to detect smaller wine grapes with appropriate training data, as the basic detection principles are similar across grape varieties.
+    Future work should involve collaboration with U.S.
+researchers to collect wine grape datasets and assess whether models trained on table grapes can generalize well to smaller wine grape berries without additional training.
+}
+
+\replaced[id=R2]{Additionally, this study only}{Another limitation of this study is that it} focused on a single berry bunch in a controlled environment.
 The noise in the data is also related to the effectiveness of the method proposed in this paper.

### 2025-05-02 response2reviewer.tex
finish R1 response framework

@@
     1. Carefully addressed all reviewer comments point-by-point;\\
-    2. Provided detailed responses explaining each modification;\\
-    3. Made all necessary revisions to improve manuscript clarity and technical accuracy;\\
-    4. Included tracked changes in the revised manuscript for transparent review.
+    2. ...
+    % 2. Provided detailed responses explaining each modification;\\
+    % 3. Made all necessary revisions to improve manuscript clarity and technical accuracy;\\
+    % 4. Included tracked changes in the revised manuscript for transparent review.
 
@@
     In response, we have:
+
+    ...
 }
@@
 
-\response{We have modified it in Sec. \uppercase\expandafter{\romannumeral1}, and highlighted it in yellow.}
+\response{
+    We sincerely appreciate the reviewer's valuable suggestions regarding the instance segmentation evaluation. 
+    In response, we have conducted additional comparative experiments by applying our completion network to both manually annotated ground truth labels and SoftGroup segmentation results, with quantitative comparisons shown in the new results figure and table below.
+
+    A t-test analysis revealed no statistically significant differences between the two approaches (p > xxx), demonstrating that our high-accuracy segmentation network (achieving mAP@[.5:.95] of 0.995 represents an AP50 of 0.999 for our results) provides sufficiently reliable inputs for the completion network.
+
+    We maintain our design of having specialized networks focus on their respective tasks: the segmentation network achieves reliable segmentation accuracy, while the completion network specializes in partial point cloud completion.
+    Rather than increasing the completion network's robustness to handle poor segmentation results.
+    It would require generating artificial training data with various error patterns that might negatively impact training.
+    We believe it is more principled to improve the segmentation performance directly. 
+    This modular approach ensures clear responsibility separation between network components.
+}
+
+\todoblock{
+    Execute the following experiment on manual annotation bunches:
+
+    1. Apply completion networks directly on ground truth (separated 3D reconstruction)
+
+    2. Run SoftGroup segmentation on ground truth, and then apply completion networks on these results
+
+    3. Compare two results to draw comparison tables and runing t-test to show no significant differences.
+}
+
+\manuscript{
+    ...
+}
 
@@
 \response{
+    We thank the reviewer for these insightful suggestions regarding ablation studies for our completion network. 
+    For current manuscript, we already have part ablation studies. 
+    The GrapeCPNet is combined the modification of PoinTr and SnowFlakeNet.
+    As shown in the original Table 3, we compared the performance of:
+    (1) Standalone PoinTr; (2) Standalone SnowFlakeNet; (3) Our modified GrapeCPNet (combined architecture).
+    The results demonstrated the superiority of our integrated approach.
+
+    We have also expanded our ablation studies to provide more comprehensive analysis as you suggested:
+
+    1. \textbf{Impact of Cut Numbers}: We conducted new experiments evaluating how different occlusion levels (number of cuts) affect completion performance:
+
     ...
+
+    The results showed that mixed occlusion training significantly improves generalization
+
+    2. \textbf{Point Number Analysis}: We investigated how output point count affects SnowFlakeNet performance:
+
+    ...
+
+    The result showed higher point counts yield better completion quality.
+}
+
+\todoblock{
+    To add the experiement:
+
+    1.
+split training data to 1 cuts, 2cuts, 3cuts, 4 cuts and 5 cuts, train 5 individual networks and validate on val dataset and compare with 1-5 full training data?
+(expected -> less cuts in training data, worse performance on server overlapped.)
+
+    2. Decrease the feature M (current=2048) of networks, 2048, 1024, 512, 256, to see if any affects of completion results.
 }
@@
 \end{reviewercomment}
+
 \response{
-    ...
+    We appreciate the reviewer's suggestion regarding additional baselines.
+
+    The work of \citet{marangoz_fruit_2022} generates cube-like point clouds for peppers, which may not be suitable for our sphere-like grape berries.
+    Additionally, re-implementation their algorithm is time-consuming and unlikely to benefit our current grape project.
+    Our ellipsoid surface fitting is a similar non-learning-based approach, serving for berry traits analysis in this study. 
+    Therefore, it may not be appropriate as a baseline comparison.
+
+    The comparison with \citet{blok_highthroughput_2025} was not included initially because these were independent parallel research projects during our manuscript preparation phase. 
+    Following editorial recommendations during the submission process, we subsequently added discussions of comparable works in the revised manuscript, including it into the discussion part after its acceptance.
+
+    In this revision, we have now included CoRe++ from \citet{blok_highthroughput_2025} performance on our grape dataset in Table 3. 
+    However, we observe that the network architectures target substantially different objectives.
+    Our grape dataset involves partial completion from the same sensor type, while the potato network focuses on fusing different sensors 
+    (with incomplete point clouds from RGB-D and complete ones from SfM, exhibiting significant shape and texture differences). 
+    Our approach emphasizes better completion performance while the \citet{blok_highthroughput_2025} more on processing speed and real-time processing, and consequently, CoRe++ does not demonstrate significant advantages in our grape dataset scenario.
+}
+
+\todoblock{
+    Add CoRe++ results to Table 3 (collaboration with pieter)
 }
@@
 \todoblock{
-    Confirm which tool for labeling
+    Confirm which tool for labeling, or SoftGroup can automatically annotation?
 }

### 2025-05-08 response2reviewer.tex
R1 point 2

@@
 \response{
-    We sincerely appreciate the reviewer's positive assessment of our study and manuscript. 
-    Regarding the suggestion for additional experiments, we agree that further validation would strengthen the work.
-
-    In response, we have:
-
-    ...
-}
-
-\todoblock{
-    Summary of added experiment.
+    We sincerely appreciate the reviewer's valuable feedback and constructive suggestions for improving our paper. 
+    Regarding the request for additional experiments on instance segmentation and completion,
+    We have enhanced the manuscript to better explain these design choices in the Methods, Results and  Discussion sections.
+    Please find our detailed responses to each specific comment below.
 }
@@
 \response{
-    We sincerely appreciate the reviewer's valuable suggestions regarding the instance segmentation evaluation. 
-    In response, we have conducted additional comparative experiments by applying our completion network to both manually annotated ground truth labels and SoftGroup segmentation results, with quantitative comparisons shown in the new results figure and table below.
+    We sincerely appreciate the reviewer's insightful comments regarding the evaluation of instance segmentation and its impact on the completion network. 
+    We agree that analyzing the robustness of the completion network to segmentation errors is an interesting direction, and we already have conducted a similar preliminary experiments during the early stage of our studies.
 
-    A t-test analysis revealed no statistically significant differences between the two approaches (p > xxx), demonstrating that our high-accuracy segmentation network (achieving mAP@[.5:.95] of 0.995 represents an AP50 of 0.999 for our results) provides sufficiently reliable inputs for the completion network.
+    In our preliminary tests on a small subset of data, we visually compared the outputs of completion network on using ground truth segmentation versus SoftGroup segmentation outputs. 
+    The differences were negligible to the human eye thus not mentioned in the manuscript.
+    This is because our high-quality grape point clouds (captured in a controlled indoor environment with high-overlap scanning) exhibit clear boundaries and minimal noise. 
+    Also, since our segmentation network (trained on manually annotated data using SoftGroup) achieves near-perfect performance (mAP@[.5:.95] of 0.995, representing AP50 of 0.999), making its outputs virtually almost indistinguishable from ground truth for our application.
+    Moreover, we note that manual annotation of 3D data on 2D displays inevitably contains some human error, meaning even ``ground truth'' segmentations are not perfectly accurate.
 
-    We maintain our design of having specialized networks focus on their respective tasks: the segmentation network achieves reliable segmentation accuracy, while the completion network specializes in partial point cloud completion.
-    Rather than increasing the completion network's robustness to handle poor segmentation results.
-    It would require generating artificial training data with various error patterns that might negatively impact training.
-    We believe it is more principled to improve the segmentation performance directly. 
-    This modular approach ensures clear responsibility separation between network components.
-}
+    Given these observations, we believe our current design - where each specialized network focuses on its respective task - represents the most efficient approach. 
+    The segmentation network reliably handles instance separation, while the completion network specializes in partial point cloud completion.
+    While artificially generating poor segmentation outputs to test completion robustness could be interesting, 
+    it would require additional design to generating extra training data to cover various error patterns that might negatively impact network training.
 
-\todoblock{
-    Execute the following experiment on manual annotation bunches:
-
-    1. Apply completion networks directly on ground truth (separated 3D reconstruction)
-
-    2. Run SoftGroup segmentation on ground truth, and then apply completion networks on these results
-
-    3. Compare two results to draw comparison tables and runing t-test to show no significant differences.
+    Instead, we believe it's more principled to:
+    1) Improve data collection quality, as poor-quality inputs lead to poor-quality outputs; and
+    2) Enhance segmentation accuracy to ensure high-quality inputs for the completion network.
 }
@@
 \manuscript{
-    ...
+    and the result of obtaining the phenotypic traits.
+
+    \textbf{3.1 Berry Instance Segmentation Results}
+
+    \added[id=R1]{
+    Our controlled indoor environment (Fig.~\ref{fig:raw9}) with high-overlap scanning enabled high-quality grape point cloud reconstruction, featuring clear boundaries and minimal noise.
+    Some reconstructed results are shown in Figs.~\ref{fig:raw10}, \ref{fig:raw2}, \ref{fig:raw11}, and \ref{fig:raw13}.
+    These high-quality input data reduced the challenges in annotating instance berry segmentation training data.
+    They also simplified the segmentation model training by minimizing concerns about noise and unclear boundaries.
+}
+
+    \added[id=R1]{The segmentation task divides the grape bunch into two parts: berries and stems.} 
+    The mAP@[.5:.95] values of berry and stem class are 0.995 and 0.941, respectively, which showed a high accuracy of the berry segmentation from the bunch.
+}
+
+\manuscript{
+    The primary time-consuming work of our approach was the annotation of 3D data for instance segmentation.
+    \added[id=R1]{
+        We acknowledge that manual annotation of 3D data on 2D displays may introduce some human errors, meaning even the ground truth segmentation annotations are not perfectly accurate.
+        However, due to the high-quality 3D reconstruction with clear berry boundaries and minimal noise effects,
+        we could train a highly accurate SoftGroup segmentation network, achieving an mAP@[.5:.95] of 0.995 and AP50 of 0.999.
+    }
+    Compared to similar studies on grape berries, our proposed method demonstrated superior performance, achieving the best results among the reviewed methods (Subsection~\ref{sec:insegresults}).
+    \added[id=R1]{Instead of developing complex algorithms to handle low-quality inputs, improving input quality simplifies the problem and produces better outputs.}
+
+    For berry completion using deep learning, the most challenging and time-consuming task is
+}
+
+\manuscript{
+    \added[id=R2]{
+        and assess whether models trained on table grapes can generalize well to smaller wine grape berries without additional training.
+    }
+
+    \added[id=R1]{
+        The design philosophy focuses on ensuring input quality and assigning specialized networks to their respective tasks, which provides the most efficient approach. 
+        Rather than developing complex algorithms to process low-quality inputs with unclear berry boundaries and noisy 3D models, improving input quality simplifies the problem and enhances the results.
+        Similarly, assigning each specialized network to its specific task is essential. 
+        In this study, the segmentation network reliably performs instance separation, while the completion network specializes in partial point cloud completion. 
+        Although the automatic training data generation strategy can be adjusted to produce poor segmentation outputs—for example, by adding noise or partially cutting neighboring berries—it remains difficult to cover all potential error patterns to improve robustness.
+        Additionally, training with too many low-quality samples may negatively affect network performance. 
+        However, this design philosophy also faces challenges in practical applications.
+    }
+    \replaced[id=R1]{For example, this study}{Another limitation of this study is that it} focused on a single berry bunch in a controlled environment.
+}
+
+\manuscript{
+    the branching structure could potentially be captured during early stages of thinning, as suggested by \citep{du_instance_2023}.
+    \added[id=R1]{Lastly, with the development of lidar scanning techniques, some companies also provide low-cost products to improve 3D scanning results in the field, such as XGrids (XGRIDS LIMITED, \url{https://www.xgrids.com}).}
+    Such data could enable studies on growth prediction for optimizing harvesting times and assessments of branching structure deviations within crowded berry bunches.
 }

### 2025-05-08 main.tex
R1 point 2

@@
 
+\added[id=R1]{
+    Our controlled indoor environment (Fig.~\ref{fig:raw9}) with high-overlap scanning enabled high-quality grape point cloud reconstruction, featuring clear boundaries and minimal noise.
+    Some reconstructed results are shown in Figs.~\ref{fig:raw10}, \ref{fig:raw2}, \ref{fig:raw11}, and \ref{fig:raw13}.
+    These high-quality input data reduced the challenges in annotating instance berry segmentation training data.
+    They also simplified the segmentation model training by minimizing concerns about noise and unclear boundaries.
+}
+
+\added[id=R1]{The segmentation task divides the grape bunch into two parts: berries and stems.} 
 The mAP@[.5:.95] values of berry and stem class are 0.995 and 0.941, respectively, which showed a high accuracy of the berry segmentation from the bunch.
@@
 In our study, the AP50 value exceeded 0.999, with both recall and precision values at this level also over 0.999.
-When compared to traidtional berry semgnetation algorithms, \citet{rose_automated_2016} reported a mean recall of 0.776 and precision of 0.978;
+When compared to traditional berry segmentation algorithms, \citet{rose_automated_2016} reported a mean recall of 0.776 and precision of 0.978;
 The results of four fresh grapes for bunch point cloud segmentation are visualized in Fig.~\ref{fig:raw13}.
@@
 The primary time-consuming work of our approach was the annotation of 3D data for instance segmentation.
+\added[id=R1]{
+    We acknowledge that manual annotation of 3D data on 2D displays may introduce some human errors, meaning even the ground truth segmentation annotations are not perfectly accurate.
+    However, due to the high-quality 3D reconstruction with clear berry boundaries and minimal noise effects,
+    we could train a highly accurate SoftGroup segmentation network, achieving an mAP@[.5:.95] of 0.995 and AP50 of 0.999.
+}
 Compared to similar studies on grape berries, our proposed method demonstrated superior performance, achieving the best results among the reviewed methods (Subsection~\ref{sec:insegresults}).
@@
 
-\replaced[id=R2]{Additionally, this study only}{Another limitation of this study is that it} focused on a single berry bunch in a controlled environment.
+\added[id=R1]{
+    The design philosophy focuses on ensuring input quality and assigning specialized networks to their respective tasks, which provides the most efficient approach. 
+    Rather than developing complex algorithms to process low-quality inputs with unclear berry boundaries and noisy 3D models, improving input quality simplifies the problem and enhances the results. 
+    Similarly, assigning each specialized network to its specific task is essential. 
+    In this study, the segmentation network reliably performs instance separation, while the completion network specializes in partial point cloud completion. 
+    Although the automatic training data generation strategy can be adjusted to produce poor segmentation outputs—for example, by adding noise or partially cutting neighboring berries—it remains difficult to cover all potential error patterns to improve robustness.
+    Additionally, training with too many low-quality samples may negatively affect network performance. 
+    However, this design philosophy also faces challenges in practical applications.
+}
+\replaced[id=R1]{For example, this study}{Another limitation of this study is that it} focused on a single berry bunch in a controlled environment.
 The noise in the data is also related to the effectiveness of the method proposed in this paper.
@@
 By collecting time-series growth data, the branching structure could potentially be captured during early stages of thinning, as suggested by \citep{du_instance_2023}.
+\added[id=R1]{Lastly, with the development of lidar scanning techniques, some companies also provide low-cost products to improve 3D scanning results in the field, such as XGrids (XGRIDS LIMITED, \url{https://www.xgrids.com}).}
 Such data could enable studies on growth prediction for optimizing harvesting times and assessments of branching structure deviations within crowded berry bunches.

### 2025-05-08 response2reviewer.tex
R1 finish

@@
 \response{
-    We thank the reviewer for these insightful suggestions regarding ablation studies for our completion network. 
-    For current manuscript, we already have part ablation studies. 
-    The GrapeCPNet is combined the modification of PoinTr and SnowFlakeNet.
-    As shown in the original Table 3, we compared the performance of:
-    (1) Standalone PoinTr; (2) Standalone SnowFlakeNet; (3) Our modified GrapeCPNet (combined architecture).
-    The results demonstrated the superiority of our integrated approach.
+    We thank the reviewer for the insightful suggestions regarding ablation studies for our completion network. 
+    We would like to clarify that GrapeCPNet is not an entirely new network architecture, but rather a combination of features from two existing models (PoinTr and SnowFlakeNet). 
+    This approach differs from traditional network design methodologies. 
+    Therefore, performing the suggested ablation studies may not be practical or aligned with our main research objectives.
 
-    We have also expanded our ablation studies to provide more comprehensive analysis as you suggested:
+    However, when treating each network component as an independent module, our results already include comparative experiments between individual networks and the combined architecture. 
+    As shown in Table 3, we compared the performance of: (1) PoinTr alone; (2) SnowFlakeNet alone; (3) Our combined GrapeCPNet. 
+    The results demonstrate that the combined architecture outperforms either individual network.
 
-    1. \textbf{Impact of Cut Numbers}: We conducted new experiments evaluating how different occlusion levels (number of cuts) affect completion performance:
+    To support future research in this area, we will make our source code and training data publicly available. 
+    This will allow other researchers to examine how preprocessing parameters may affect the network's performance.
 
-    ...
-
-    The results showed that mixed occlusion training significantly improves generalization
-
-    2. \textbf{Point Number Analysis}: We investigated how output point count affects SnowFlakeNet performance:
-
-    ...
-
-    The result showed higher point counts yield better completion quality.
-}
-
-\todoblock{
-    To add the experiement:
-
-    1.
-split training data to 1 cuts, 2cuts, 3cuts, 4 cuts and 5 cuts, train 5 individual networks and validate on val dataset and compare with 1-5 full training data?
-(expected -> less cuts in training data, worse performance on server overlapped.)
-
-    2. Decrease the feature M (current=2048) of networks, 2048, 1024, 512, 256, to see if any affects of completion results.
+    We have also added the above discussion in the results section.
 }
@@
 \manuscript{
-    ...
+    this paper further validated the efficacy of the 3D phenotypic traits of grape by the proposed method.
+
+    \added[id=R1]{
+        Since GrapeCPNet combines features from two existing models (PoinTr and SnowFlakeNet) rather than introducing a completely new architecture,
+        ablation studies may not align with our research focus.
+        However, we conducted comparative experiments by treating each network as an independent module.
+        As shown in Table~\ref{tbl:4}, we evaluated three approaches: (1) PoinTr alone, (2) SnowFlakeNet alone, and (3) our combined GrapeCPNet.
+        The results show that GrapeCPNet achieves better performance than either individual network.
+        To facilitate future research, we will release our source code and training data at \url{https://github.com/I3-Laboratory/GrapeCPNet}.
+        This will enable interested researchers to examine how preprocessing parameters influence the network's performance.
+    }
+
+    \textbf{3.3 Phenotypic Traits Calculation Results}
+}
+
+\manuscript{
+    \textbf{Data availability}
+
+    The \added[id=R1]{demo dataset, source codes} and model weight for the \replaced[id=R1]{academic}{test} usage is available \replaced[id=R1]{at}{here:} \url{https://github.com/I3-Laboratory/GrapeCPNet}.
+    The whole dataset \added[id=R1]{and codes} used in this paper is available upon request.
 }
@@
 
-    The work of \citet{marangoz_fruit_2022} generates cube-like point clouds for peppers, which may not be suitable for our sphere-like grape berries.
+    The comparison with \citet{blok_highthroughput_2025} was not included initially because these were independent parallel research projects during our manuscript preparation phase. 
+    Following editorial recommendations during the submission process, we subsequently added discussions of comparable works in the revised manuscript, including it into the discussion part after \citet{blok_highthroughput_2025} been accepted.
+
+    Additionally, the network architectures target substantially different objectives. 
+    This grape completion involves partial completion using the same sensor type, while the potato network focuses on fusing different sensors with an emphasis on processing speed and real-time performance.
+    Specifically, \citet{blok_highthroughput_2025} works with incomplete point clouds from RGB-D sensors and complete point clouds from SfM, which exhibit significant differences in shape and texture.
+    Our approach aims for better completion performance on ellipsoid berry shapes with smooth surfaces, whereas \citet{blok_highthroughput_2025} focuses on irregular and elongated potato tuber shapes.
+    Although both networks perform completion tasks, their purposes and input data differ. 
+    For the future work, it may be interesting to do a comparation of two networks on inverted crops.
+
+    It is also the similar reason why we not comparing with \citet{marangoz_fruit_2022}.
+    The work of \citet{marangoz_fruit_2022} generates cube-like point clouds for peppers, which would may not be suitable for ellipsoid grape berries with smooth surfaces.
     Additionally, re-implementation their algorithm is time-consuming and unlikely to benefit our current grape project.
-    Our ellipsoid surface fitting is a similar non-learning-based approach, serving for berry traits analysis in this study. 
-    Therefore, it may not be appropriate as a baseline comparison.
+    Our ellipsoid surface fitting is a similar non-learning-based approach, serving for berry traits analysis in this study (section~\ref{sec:ellipsoid}). 
+    Therefore, non-learning-based approach may not be appropriate as a baseline comparison
 
-    The comparison with \citet{blok_highthroughput_2025} was not included initially because these were independent parallel research projects during our manuscript preparation phase. 
-    Following editorial recommendations during the submission process, we subsequently added discussions of comparable works in the revised manuscript, including it into the discussion part after its acceptance.
-
-    In this revision, we have now included CoRe++ from \citet{blok_highthroughput_2025} performance on our grape dataset in Table 3. 
-    However, we observe that the network architectures target substantially different objectives.
-    Our grape dataset involves partial completion from the same sensor type, while the potato network focuses on fusing different sensors 
-    (with incomplete point clouds from RGB-D and complete ones from SfM, exhibiting significant shape and texture differences). 
-    Our approach emphasizes better completion performance while the \citet{blok_highthroughput_2025} more on processing speed and real-time processing, and consequently, CoRe++ does not demonstrate significant advantages in our grape dataset scenario.
-}
-
-\todoblock{
-    Add CoRe++ results to Table 3 (collaboration with pieter)
+    We have also added the above discussion in the introduction and discussion section.
 }
@@
 \manuscript{
-    ...
+    provided an appropriate symmetrical plane can be identified.
+    \citet{marangoz_fruit_2022} proposed an super-ellipsoids matching approach to \replaced[id=R1]{generate cube-like point clouds for peppers}{ map fruits on plants} and estimate their shape.
+    However, these methods are limited to specific fruit characteristics and require manual design of algorithms according to the features of the fruit
+}
+
+\manuscript{
+    training datasets of complete and incomplete point clouds.
+    In our \replaced[id=R1]{recent}{previous} work on potato tuber completion networks \citep{blok_highthroughput_2025}, a distinguishable pin was 
+}
+
+\manuscript{
+    these automatically generated paired training datasets were successfully used to train several completion models (Table~\ref{tbl:4}).
+
+    \added[id=R1]{
+        Although our recent work proposed a completion network for partial potato tubers \citep{blok_highthroughput_2025}, the purposes and input data types differ. 
+        This grape completion study uses the same sensor type, whereas the potato network focuses on fusing different sensors with an emphasis on processing speed and real-time performance on fast-moving conveyors.
+        Specifically, the tuber completion study processes incomplete point clouds from RGB-D sensors and complete point clouds from SfM, which show significant differences in shape and texture. 
+        Additionally, the grape completion targets smooth ellipsoid berry surfaces, while potato tubers have more irregular and elongated shapes. 
+        For future work, it may be interesting to compare the two networks on inverted crops.
+    }
+    We \replaced[id=R1]{also}{have} found that some researchers
 }

### 2025-05-08 main.tex
R1 finish

@@
 For instance, \citet{ge_symmetrybased_2020} assume that strawberries are symmetrical, suggesting that their shape can be completed by mirroring the existing shape, provided an appropriate symmetrical plane can be identified.
-\citet{marangoz_fruit_2022} proposed an super-ellipsoids matching approach to map fruits on plants and estimate their shape.
+\citet{marangoz_fruit_2022} proposed an super-ellipsoids matching approach to \replaced[id=R1]{generate cube-like point clouds for peppers}{ map fruits on plants} and estimate their shape.
 However, these methods are limited to specific fruit characteristics and require manual design of algorithms according to the features of the fruit, lacking the potential for generalized application.
@@
 \subsection{Phenotypic Traits Calculation and Validation}
+\label{sec:ellipsoid}
 
@@
 
+\added[id=R1]{
+    Since GrapeCPNet combines features from two existing models (PoinTr and SnowFlakeNet) rather than introducing a completely new architecture,
+    ablation studies may not align with our research focus.
+    However, we conducted comparative experiments by treating each network as an independent module.
+    As shown in Table~\ref{tbl:4}, we evaluated three approaches: (1) PoinTr alone, (2) SnowFlakeNet alone, and (3) our combined GrapeCPNet.
+    The results show that GrapeCPNet achieves better performance than either individual network.
+    To facilitate future research, we will release our source code and training data at \url{https://github.com/I3-Laboratory/GrapeCPNet}.
+    This will enable interested researchers to examine how preprocessing parameters influence the network's performance.
+}
+
 \subsection{Phenotypic Traits Calculation Results}
@@
 For berry completion using deep learning, the most challenging and time-consuming task is preparing the paired training datasets of complete and incomplete point clouds.
-In our previous work on potato tuber completion networks \citep{blok_highthroughput_2025}, a distinguishable pin was used as a reference point to align the complete tuber scans obtained via photogrammetry with the incomplete tuber scans captured using an RGB-D camera.
+In our \replaced[id=R1]{recent}{previous} work on potato tuber completion networks \citep{blok_highthroughput_2025}, a distinguishable pin was used as a reference point to align the complete tuber scans obtained via photogrammetry with the incomplete tuber scans captured using an RGB-D camera.
 A pin-guided point cloud matching algorithm was then applied to calculate the transformation matrix for pairing the datasets.
@@
 As demonstrated in Subsection~\ref{sec:32}, these automatically generated paired training datasets were successfully used to train several completion models (Table~\ref{tbl:4}).
-We have found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
+
+\added[id=R1]{
+    Although our recent work proposed a completion network for partial potato tubers \citep{blok_highthroughput_2025}, the purposes and input data types differ. 
+    This grape completion study uses the same sensor type, whereas the potato network focuses on fusing different sensors with an emphasis on processing speed and real-time performance on fast-moving conveyors.
+    Specifically, the tuber completion study processes incomplete point clouds from RGB-D sensors and complete point clouds from SfM, which show significant differences in shape and texture. 
+    Additionally, the grape completion targets smooth ellipsoid berry surfaces, while potato tubers have more irregular and elongated shapes. 
+    For future work, it may be interesting to compare the two networks on inverted crops.
+}
+We \replaced[id=R1]{also}{have} found that some researchers \citep{pan_panoptic_2023,magistri_efficient_2024} have improved the completion effect by encoding a prior knowledge of the geometry of the object into the weights of the neural network.
 Considering the agricultural plant completion task, our proposed GrapeCPNet, which combines centroid-based sparse completion with diffusion-based dense completion, outperformed other networks in terms of performance.
@@
 \section*{Data availability}
-The dataset and model weight for the test usage is available here: https://github.com/I3-Laboratory/GrapeCPNet. The whole dataset used in this paper is available upon request.
+The \added[id=R1]{demo dataset, source codes} and model weight for the \replaced[id=R1]{academic}{test} usage is available \replaced[id=R1]{at}{here:} \url{https://github.com/I3-Laboratory/GrapeCPNet}.
+The whole dataset \added[id=R1]{and codes} used in this paper is available upon request.
 

### 2025-05-08 response2reviewer.tex
update compile notice

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%% IMPORTANT NOTICE %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% The `main.tex` can be compiled directly on Overleaf, 
+% but the `response2reviewers.tex` needs to be locally compiled, 
+% which requires the `out/main.aux` and `out/main.pdf` file to get correct compiling.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%% IMPORTANT NOTICE %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \documentclass{ar2rc}
@@
 \externaldocument{main}
+
+% 将main.pdf添加到末尾
+\usepackage{pdfpages}
 
@@
 \textbf{Note:} To enhance the legibility of this response letter, all the editor's and reviewers' comments are typeset in boxes.
-Rephrased or added sentences are typeset in color.
+Rephrased or added sentences are typeset in color with suffix \added[id=R1]{} and \added[id=R2]{}.
 The respective parts in the manuscript are highlighted to indicate changes.
@@
 
-    \replaced[id=R2]{Additionally, this study only}{Another limitation of this study is that it} focused on a single berry bunch in a controlled environment.
+    \added[id=R1]{
+        The design philosophy focuses on ensuring input quality and assigning specialized networks to their respective tasks, which provides the most efficient approach. 
+    }
 }
@@
 \bibliography{references}
+
+\includepdf[pages=-]{out/main.pdf} % 添加整个 PDF
 

### 2025-05-08 response2reviewer.tex
finish reviewer

@@
 \manuscript{
-    In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) as shown in}{at the instance-level} Fig.~\ref{fig:raw11}.
+    In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) by CloudCompare (\url{https://www.cloudcompare.org/}) as shown in}{at the instance-level} Fig.~\ref{fig:raw11}.
 }
@@
     We thank the reviewer for raising this important methodological detail. 
-    The 3D point clouds were labeled using CloudCompare (v2.12.4), an open-source software for 3D point cloud and mesh processing.
-}
-
-\todoblock{
-    Confirm which tool for labeling, or SoftGroup can automatically annotation?
+    The 3D point clouds were labeled using CloudCompare, an open-source software for 3D point cloud and mesh processing.
 }
@@
 \manuscript{
-
+    In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) by CloudCompare (\url{https://www.cloudcompare.org/}) as shown in}{at the instance-level} Fig.~\ref{fig:raw11}.
 }

### 2025-05-08 main.tex
finish reviewer

@@
 
-In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) as shown in}{at the instance-level} Fig.~\ref{fig:raw11}.
+In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was \added[id=R2]{individually} labeled \replaced[id=R2]{(instance-level segmentation) by CloudCompare (\url{https://www.cloudcompare.org/}) as shown in}{at the instance-level} Fig.~\ref{fig:raw11}.
 This paper collected and labeled eight bunches for each of the four species (in total 32 bunches). 

### 2025-05-15 response2reviewer.tex
wei's updates

@@
 We appreciate the time and effort that editors and the reviewers dedicated to providing feedback on our manuscript and are grateful for the insightful comments and valuable improvements to our paper.
-We have incorporated most of the suggestions made by the reviewers.
+We have incorporated the suggestions made by the reviewers.
 Those changes are highlighted within the manuscript.
-Please see below, for a point-by-point response to the reviewers' comments and concerns.
+Please see below for a point-by-point response to the reviewers' comments and concerns.
 All page numbers refer to the revised manuscript file with tracked changes.
 
-Thank your for your consideration. I am looking forward to hearing from you soon.
+Thank you for your consideration. I am looking forward to hearing from you soon.
 
@@
     1. Carefully addressed all reviewer comments point-by-point;\\
-    2. ...
+    2. Especially, ...
     % 2. Provided detailed responses explaining each modification;\\
@@
 
-    We believe these revisions have significantly strengthened the paper, and we appreciate the editor's and reviewers' time and constructive suggestions. 
-    Please find our point-by-point responses to each reviewer comment in the following sections.
+    These revisions have significantly strengthened the paper, and we appreciate the editors' and reviewers' time and constructive suggestions. 
+    Please find our point-by-point responses to each reviewer's comment in the following sections.
 }
@@
 
-    In our preliminary tests on a small subset of data, we visually compared the outputs of completion network on using ground truth segmentation versus SoftGroup segmentation outputs. 
-    The differences were negligible to the human eye thus not mentioned in the manuscript.
+    In our preliminary tests on a small subset of data, we visually compared the outputs of the completion network on using ground truth segmentation versus SoftGroup segmentation outputs. 
+    The differences were negligible to the human eye and thus not mentioned in the manuscript.
     This is because our high-quality grape point clouds (captured in a controlled indoor environment with high-overlap scanning) exhibit clear boundaries and minimal noise. 
-    Also, since our segmentation network (trained on manually annotated data using SoftGroup) achieves near-perfect performance (mAP@[.5:.95] of 0.995, representing AP50 of 0.999), making its outputs virtually almost indistinguishable from ground truth for our application.
+    Also, since our segmentation network (trained on manually annotated data using SoftGroup) achieves near-perfect performance (mAP@[.5:.95] of 0.995, representing AP50 of 0.999), making its outputs virtually indistinguishable from ground truth for our application.
     Moreover, we note that manual annotation of 3D data on 2D displays inevitably contains some human error, meaning even ``ground truth'' segmentations are not perfectly accurate.
 
-    Given these observations, we believe our current design - where each specialized network focuses on its respective task - represents the most efficient approach. 
+    Given these observations, our current design - where each specialized network focuses on its respective task - represents the most efficient approach. 
     The segmentation network reliably handles instance separation, while the completion network specializes in partial point cloud completion.
     While artificially generating poor segmentation outputs to test completion robustness could be interesting, 
-    it would require additional design to generating extra training data to cover various error patterns that might negatively impact network training.
+    It would require additional design to generate extra training data to cover various error patterns that might negatively impact network training.
 
@@
 
-    To support future research in this area, we will make our source code and training data publicly available. 
-    This will allow other researchers to examine how preprocessing parameters may affect the network's performance.
+    To support future research in this area, we also made our source code and training data of completion net publicly available. 
+    This will allow other researchers to examine how preprocessing parameters affect the completion network's performance.
 
-    We have also added the above discussion in the results section.
+    We have also added the above discussion to the results section.
 }
@@
     \added[id=R1]{
-        Since GrapeCPNet combines features from two existing models (PoinTr and SnowFlakeNet) rather than introducing a completely new architecture,
-        ablation studies may not align with our research focus.
+        Since GrapeCPNet combines features from two existing models (PoinTr and SnowFlakeNet) rather than introducing a completely new architecture, ablation studies may not align with our research focus.
         However, we conducted comparative experiments by treating each network as an independent module.
@@
         The results show that GrapeCPNet achieves better performance than either individual network.
-        To facilitate future research, we will release our source code and training data at \url{https://github.com/I3-Laboratory/GrapeCPNet}.
+        The source code and training data are publicly available at \url{https://github.com/I3-Laboratory/GrapeCPNet}.
         This will enable interested researchers to examine how preprocessing parameters influence the network's performance.
@@
 
-    The \added[id=R1]{demo dataset, source codes} and model weight for the \replaced[id=R1]{academic}{test} usage is available \replaced[id=R1]{at}{here:} \url{https://github.com/I3-Laboratory/GrapeCPNet}.
-    The whole dataset \added[id=R1]{and codes} used in this paper is available upon request.
+    The \added[id=R1]{demo dataset, source codes} and model weight \added[id=R1]{of GrapeCPNet (completion network)} for the \replaced[id=R1]{academic}{test} usage is available \replaced[id=R1]{at}{here:} \url{https://github.com/I3-Laboratory/GrapeCPNet}.
 }

### 2025-05-15 main.tex
wei's updates

@@
 \section*{Data availability}
-The \added[id=R1]{demo dataset, source codes} and model weight for the \replaced[id=R1]{academic}{test} usage is available \replaced[id=R1]{at}{here:} \url{https://github.com/I3-Laboratory/GrapeCPNet}.
-The whole dataset \added[id=R1]{and codes} used in this paper is available upon request.
+The \added[id=R1]{demo dataset, source codes} and model weight \added[id=R1]{of GrapeCPNet (completion network)} for the \replaced[id=R1]{academic}{test} usage is available \replaced[id=R1]{at}{here:} \url{https://github.com/I3-Laboratory/GrapeCPNet}.
 
